### 2016-08-06 paper/main.tex
manuscript draft

\documentclass[iop,numberedappendix,apj,]{emulateapj}

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color,xcolor}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
\allowdisplaybreaks[1]
\bibliographystyle{apj}
\renewcommand{\bibname}{References}

\def\plotonesc#1{\centering \leavevmode
\includegraphics[clip=, width=1.70\columnwidth]{#1}}
\def\plotoneh#1{\centering \leavevmode
\includegraphics[clip=, width=.95\columnwidth]{#1}}
\def\plotone#1{\centering \leavevmode
\includegraphics[clip=, width=.85\columnwidth]{#1}}
\def\plotoneShrinkSmall#1{\centering \leavevmode
\includegraphics[clip=, width=.49\columnwidth]{#1}}
\def\plotoneShrinkMed#1{\centering \leavevmode
\includegraphics[clip=, width=.55\columnwidth]{#1}}
\def\plotoneShrinkBig#1{\centering \leavevmode
\includegraphics[clip=, width=.65\columnwidth]{#1}}
\def\plottwo#1#2{\centering \leavevmode
\includegraphics[width=.45\columnwidth]{#1} \hfil
\includegraphics[width=.45\columnwidth]{#2}}
\def\plottwob#1#2{\centering \leavevmode
\includegraphics[width=.49\columnwidth]{#1} \hfil
\includegraphics[width=.49\columnwidth]{#2}}
\def\plottwor#1#2{\centering \leavevmode
\includegraphics[width=.55\columnwidth,angle=90]{#1} \hfil
\includegraphics[width=.55\columnwidth,angle=90]{#2}}
\def\plotthree#1#2#3{\centering \leavevmode
\includegraphics[width=.3\columnwidth]{#1} \hfil
\includegraphics[width=.3\columnwidth]{#2} \hfil
\includegraphics[width=.3\columnwidth]{#3}}

\def\gsim{\;\rlap{\lower 2.5pt
 \hbox{$\sim$}}\raise 1.5pt\hbox{$>$}\;}
\def\lsim{\;\rlap{\lower 2.5pt
   \hbox{$\sim$}}\raise 1.5pt\hbox{$<$}\;}

% set formatting properties
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.8in}
\setlength{\hoffset}{0.0in}
\setlength{\voffset}{-0.4in}
\parindent 0.2in
\parskip 0.1in

\def\memoYF#1{\color{red}{\bf [#1]}\color{black}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE DOCUMENT BEGINS HERE                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\slugcomment{Submitted to ApJ, XX September 2015}

\begin{document}

\title{(tentative) Rotational Spectral Unmixing of Exoplanets}

\author{
%
Yuka Fujii\altaffilmark{1,2} 
%
Jacob Lustig-Yaeger\altaffilmark{3} 
%
Nicolas Cowan ?\altaffilmark{4} 
%
}

\affil{$^1$NASA Goddard Institute for Space Studies, 
  New York, NY 10025, USA}

\affil{$^2$Earth-Life Science Institute, Tokyo Institute of Technology, 
  Tokyo, 152-8550, JAPAN}

\affil{$^3$University of Washington, 
  }

\affil{$^4$McGill University, 
  }

\vspace{0.5\baselineskip}

\email{
yuka.fujii.ebihara@gmail.com
}

\begin{abstract}

\end{abstract}

\keywords{planets and satellites: Jupiter --- Sun: evolution ---
  planetary systems --- stars: evolution ---
  stars: AGB and post-AGB --- radio continuum: planetary systems}

%]%%% End front material

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Future direct imaging observations of terrestrial exoplanets is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
A substantial number of work have seeked detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
It has been pointed out that not only some of atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{desmarais2002} but also surface reflectance spectra affect the continuum of the spectra, which could be measured through low-resolution spectra, or multi-band photometry (color) \citep[e.g.,][]{ford2001}.

However, interpretation of disk-integrated colors is not trivial. 
This is particularly true for Earth-like planets which may harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possible biological surfaces, e.g. vegetation. 
Disentangling specific features from mixed disk-integrated color can be very challenging.

A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to planetary spin rotation and orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.  
\citet{cowan2009, cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components (with a difference of 1) and that the variation pattern is indicative of the surface properties. 
\citet{fujii2010, fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, where they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered. 
Moreover, by coupling the time variation due to spin rotation and that due to orbital revolution, 2-dimensional information of the surface may be retrieved with sufficient quality of data \citep{kawahara2010, kawahara2011, fujii2012}.

\citet{cowan2013} took another approach to the same inverse problem. 
Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters and letting them to fit the data. 
The result appeared successful to the extent that the obtained reflectance spectra roughly match the typical spectra of clouds, ocean, and continents. 
However, the longitudinal map of these components do not match the reality sufficiently well.

We were motivated by this unsatisfactory result and decided to revisit their analysis with some updates. 
Specifically, the updates include:
\begin{itemize}
\item Revisiting the formulation and point out the inherit degeneracy. 
\item Introducing regularization terms
\item Influence of the unknown radius
\end{itemize}

The organization of this paper is as follows. 
Section \ref{s:frame} revisits the problem, ....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Framing the problem}
\label{s:frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algebraic Model}
\label{ss:model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Assuming that the planetary surface is Lambertian scatterer everywhere, with a certain number $K$ of mutually distinct surface types, 
the disk-integrated spectra can be written as a weighted summation of the reflectance spectra of different surface types, e.g., 
%%%
\begin{equation}
d_{ij} = R_p^2 \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
\end{equation}
%%%
where $R_p$ is the planetary radius, $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively. 
The symbols represent as follows:
$d_{ij}$ is the observed apparent albedo (``$d$'' for data) at $i$-th epoch and $j$-th band, 
$f_{lk}^{\ast }$ is the contribution factor of the $k$-th surface type at $i$-th observational epoch, and 
$s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band.

The contribution factor $f^{\ast }$ is the weighted summation of the area fraction of $k$-th surface type, e.g., 
%%%
\begin{equation}
f^{\ast }_{ik} = \sum _{l} W_{il} f_{lk}
\end{equation}
%%%
where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type at $l$-th longitudinal slice, and 
$W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
As a result,
%%%
\begin{equation}
d_{ij} = R_p^2 \sum _{l,k} W_{il} \, f_{lk} \, s_{kj}
\end{equation}
%%%

Because $f$ is area fraction and $s$ is reflectance spectra, they are subject to the following constraints:
%%%
\begin{eqnarray}
\begin{cases}
\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
\;\; 0 < f_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \\
\;\; \sum_k f_{lk} = 1 & \mbox{for any $l$} 
\end{cases}
\label{eq:constraints}
\end{eqnarray}
%%%

Now, in the case that the planetary radius and observational geometry (latitude and longitude of the sub-stellar point and the sub-observer point) is fully known, the relevant problem is, given $d_{ij}$, estimate both $f_{lk}$ and $s_{kj}$ subject to the constraints of equation (\ref{eq:constraints}). 
---This is pioneered by trial by \citet{cowan2013}.

We argue that estimating $f$ and $s$ is no superior to estimating $f^*$ and $s$ subject to the following similar constraint:
%%%
\begin{eqnarray}
\begin{cases}
\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
\;\; 0 < f^{\ast }_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \\
\;\; \sum_k f_{lk}^{\ast } = 1 & \mbox{for any $l$} 
\end{cases}
\label{eq:constraints_ast}
\end{eqnarray}
%%%
\memoYF{write here}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Degeneracy}
\label{ss:degeneracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Baysean Formulation and Regularization}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\# of Surface Types}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Testing with mock data}
\label{s:mockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to 4 EPOXI observation of the Earth}
\label{ss:epoxi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{s:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Uncertainty in Radius}
\label{ss:radius}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity to Initial Condition}
\label{ss:initialcondition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{s:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments

\bibliography{ref}

\end{document}

### 2016-08-08 paper/main.tex
A figure of 4 EPOXI observations is added. A figure of retrieved result from EPOXI June observation is added for a test. Text updated.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Algebraic Model}
+\subsection{Algebraic Formulation}
 \label{ss:model}
@@
 $s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
+The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below.
 
@@
 $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
+The maximum number of $l$ is denoted by $L$. 
 As a result,
@@
 
+%%%
+\begin{equation}
+\tilde d_{ij} = \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
+\end{equation}
+%%%
+where $\tilde d_{ij} = d_{ij}/R_p^2$. 
+Without any constraints on $f^{\ast }$ and $s$, it is trivial to notice the degeneracy in the solutions. 
+Using an arbitrary regular matrix $X$ with rank $K$, a particular set of solution $\{ f^{\ast },\,s\}$ implies another set of solution $\{ f^{\ast }X^{-1},\,Xs\}$.
+
+Now that they are subject to the constraints (equation (\ref{eq:constraints_ast})), the range of acceptable solution is limited. 
+However, the constraints cannot be sufficient to reduce them to a unique solution. 
+One can create a infinite number of candidates for $f_{ik}^{\ast }$ which satisfies both of the two constraints for $f$, then $s$ may be obtained by $s = f^{+} \tilde d$, where $f^+$ is the pseudo-inverse matrix (note that $K < I$ to be able to find the solution) and among these solutions there should be many that satisfy the constraint for $s$ as well.
+\memoYF{Need to brush up. Possibly need to consider SVD of $f$. }
+
+To see this, we demonstrate the application to the mock data with known solution in Section \ref{s:mockdata}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Baysean Formulation and Regularization}
+\subsection{Bayesian Formulation}
 \label{ss:regularization}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%
+\begin{eqnarray}
+Posterior = \prod\limits_{i,j} \frac{1}{\sqrt{2\pi }\sigma_{ij}} &&  \exp \left[ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right] \notag \\
+&& \times \; \mathcal{P} (\{f_{l,k}\}) \cdot \mathcal{P}(\{s_{l,k}\}) 
+\end{eqnarray}
+%%%
+where $\mathcal{P} (X) $ is a prior for $X$.
+
+In order to take account of constraints (equation (\ref{eq:constraints})), we adopt the following transformation of variables: 
+%%%
+\begin{eqnarray}
+\begin{cases}
+t_{kj} = \displaystyle \ln \left[ \frac{ s_{kj} }{1 - s_{kj} } \right]  \;\;\; & \mbox{for any $k$, $j$} \\
+g_{lk} = \displaystyle \ln \left[ \frac{ f_{lk} }{1 - \sum _{m=0}^{k} f_{lm} } \right] \;\;\; & \mbox{for $k=1, ..., K-1$, any $j$} 
+\end{cases}
+\end{eqnarray}
+%%%
+Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$ and $f$ satisfy our constraints.
 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to 4 EPOXI observation of the Earth}
+\section{Application to 4 EPOXI observations of the Earth}
 \label{ss:epoxi}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bt]
+    \begin{center}
+\includegraphics[width=\hsize]{EPOXI_vislightcurve_4obs.pdf}
+    \end{center}
+    \caption{4 light curves of the Earth obtained with EPOXI mission.}
+\label{fig:EPOXIlc}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bt]
+    \begin{center}
+    \includegraphics[width=\hsize]{June_xmed_std_GPReg.pdf}
+    \end{center}
+    \caption{Result of inversion of EPOXI June data. \memoYF{to be revised}}
+\label{fig:mcmc_June_tmp}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-08-16 paper/main.tex
description about EPOXI data

@@
 A substantial number of work have seeked detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
-It has been pointed out that not only some of atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{desmarais2002} but also surface reflectance spectra affect the continuum of the spectra, which could be measured through low-resolution spectra, or multi-band photometry (color) \citep[e.g.,][]{ford2001}.
+It has been pointed out that not only some of atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but also surface reflectance spectra affect the continuum of the spectra, which could be measured through low-resolution spectra, or multi-band photometry (color) \citep[e.g.,][]{Ford2001}.
 
@@
 A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to planetary spin rotation and orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
-\citet{cowan2009, cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components (with a difference of 1) and that the variation pattern is indicative of the surface properties.
-\citet{fujii2010, fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, where they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
-Moreover, by coupling the time variation due to spin rotation and that due to orbital revolution, 2-dimensional information of the surface may be retrieved with sufficient quality of data \citep{kawahara2010, kawahara2011, fujii2012}.
+\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components (with a difference of 1) and that the variation pattern is indicative of the surface properties.
+\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, where they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
+Moreover, by coupling the time variation due to spin rotation and that due to orbital revolution, 2-dimensional information of the surface may be retrieved with sufficient quality of data \citep{Kawahara2010, Kawahara2011, Fujii2012}.
 
-\citet{cowan2013} took another approach to the same inverse problem. 
+\citet{Cowan2013} took another approach to the same inverse problem. 
 Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters and letting them to fit the data.
@@
 %%%
-where $R_p$ is the planetary radius, $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively. 
+where $R_p$ is the planetary radius, $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively \citep[see][]{Fujii2010} . 
 The symbols represent as follows:
@@
 $s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
-The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below.
+The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
 
-The contribution factor $f^{\ast }$ is the weighted summation of the area fraction of $k$-th surface type, e.g., 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[bh]
+\caption{Indexes}
+\begin{center}
+\begin{tabular}{ccc} \hline \hline
+Name & Symbol & Maximum \\ \hline
+Observation Time & $i$ & I \\
+Band & $j$ & J  \\
+Surface Type & $k$ & K  \\
+Longitudinal Slice  & $l$ & L \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:index}
+\end{table}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The contribution factor $f^{\ast }$ is the weighted summation of the area fraction of $k$-th surface type, i. e.,
 %%%
@@
 Now, in the case that the planetary radius and observational geometry (latitude and longitude of the sub-stellar point and the sub-observer point) is fully known, the relevant problem is, given $d_{ij}$, estimate both $f_{lk}$ and $s_{kj}$ subject to the constraints of equation (\ref{eq:constraints}).
----This is pioneered by trial by \citet{cowan2013}.
+---This is pioneered by trial by \citet{Cowan2013}.
 
@@
 %%%
-Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$ and $f$ satisfy our constraints.
+Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$ and $f$ always satisfy our constraints.
 
@@
 \section{Application to 4 EPOXI observations of the Earth}
-\label{ss:epoxi}
+\label{s:epoxi}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{EPOXI data}
+\label{ss:epoxidata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bt]
+\begin{figure*}[!tb]
     \begin{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now apply our framework to the observed multi-band reflected light curves of the Earth obtained with EPOXI \citep{Livengood2011, Cowan2011}. 
+There are 7 photometric filters from about 300 nm to 1000 nm, each of which has roughly 100-nm band width. 
+In total, 5 series of observations were conducted, each of which spans $\sim $24 hours with 1-hour intervals. 
+Since one of them includes lunar transit in front of the Earth and the interpretation is not straightforward, we just remove it from our data and consider only 4 series of observations, which were conducted on March 2008, June 2008, March 2009, and October 2009.
+The data are presented in Figure \ref{fig:EPOXIlc} in terms of {\it apparent albedo}, the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}.
+
+The geometrical configuration among the star, the target (the Earth), and the detector varies from observation to observation. 
+The information is summarized in \citet{Cowan2011}, but we also outline in Table \ref{tab:EPOXI} just for reference.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}[htp]
+\caption{EPOXI Observations}
+\begin{center}
+\begin{tabular}{cccccc} \hline \hline
+\multicolumn{2}{c}{Date} & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\
+\multicolumn{2}{c}{Phase} & & & & \\ \hline
+\multirow{2}{*}{initial sub-solar} & latitude & & & & \\
+& longitude  & & & & \\ \hline 
+\multirow{2}{*}{initial sub-observer} & latitude & & & & \\
+& longitude & & & & \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:EPOXI}
+\end{table*}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Retrieval using equation (\ref{eq:}) }
+\label{ss:retrieval}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+First, each series of data is analyzed separately. 
+Without regularization and with regularization
 

### 2016-08-16 main_fitlc_mcmc_EPOXI_NEW.py

@@ -11,7 +11,10 @@ import os
 import pdb
 
 from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
-    FLAG_REG_AREA, FLAG_REG_ALBD, N_TYPE, deg2rad, N_SIDE, INFILE, calculate_walkers
+    REGULARIZATION, N_TYPE, deg2rad, N_SIDE, INFILE, calculate_walkers
+
+import prior
+import reparameterize
 
 NCPU = multiprocessing.cpu_count()
 
@@ -27,119 +30,16 @@ NCPU = multiprocessing.cpu_count()
 # basic functions
 #=============================================== ====
 
-#---------------------------------------------------
-def latlon2cart(lat, lon):
-    x = np.sin((90.-lat)*deg2rad)*np.cos(lon*deg2rad)
-    y = np.sin((90.-lat)*deg2rad)*np.sin(lon*deg2rad)
-    z = np.cos((90.-lat)*deg2rad)
-    return np.array([x,y,z])
-
-
-#---------------------------------------------------
-def weight(time):
-    """
-    Weight of pixel at (lat_r, lon_r) assuming Lambertian surface
-    """
-    EO_vec = latlon2cart(LAT_O, LON_O-OMEGA*time/deg2rad)
-    ES_vec = latlon2cart(LAT_S, LON_S-OMEGA*time/deg2rad)
-    ER_vec_array = np.array(hp.pix2vec(N_SIDE, np.arange(hp.nside2npix(N_SIDE))))
-    cosTH0_array = np.dot(ES_vec, ER_vec_array)
-    cosTH1_array = np.dot(EO_vec, ER_vec_array)
-    return np.clip(cosTH0_array, 0., 1.)*np.clip(cosTH1_array, 0., 1.)
-
-
-#---------------------------------------------------
-def kernel(Time_i, n_slice):
-    """
-    Kernel!
-    """
-    Kernel_il = np.zeros([len(Time_i), n_slice])
-    N_pix = hp.nside2npix(N_SIDE)
-    for ii in xrange(len(Time_i)):
-        position_theta, position_phi   = hp.pixelfunc.pix2ang(N_SIDE, np.arange(N_pix))
-        Weight_n = weight(Time_i[ii])
-        assigned_l = np.trunc(position_phi/(2.*np.pi/n_slice))
-        Count_l = np.zeros(n_slice)
[…]

### 2016-08-16 prior.py

@@ -184,7 +184,6 @@ def regularize_area_GP2( x_area_lk, regparam ):
     return term1 + term2
 
 
-
 #---------------------------------------------------
 def get_cov2( sigma, lambda_angular, l_dim, periodic=True):
 

### 2016-08-19 paper/main.tex
EPOXI geometry table is inserted

@@
 \begin{center}
-\begin{tabular}{cccccc} \hline \hline
-\multicolumn{2}{c}{Date} & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\
-\multicolumn{2}{c}{Phase} & & & & \\ \hline
-\multirow{2}{*}{initial sub-solar} & latitude & & & & \\
-& longitude  & & & & \\ \hline 
-\multirow{2}{*}{initial sub-observer} & latitude & & & & \\
-& longitude & & & & \\ \hline
+\begin{tabular}{lcccc} \hline \hline
+& Equator (equinox) & Equator (solstice) & North & South \\ \hline
+Date & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\ 
+Phase & $57.7^{\circ }$ & $76.6^{\circ }$ & $85.9^{\circ }$ & $86.4^{\circ }$ \\ 
+average sub-solar latitude & $-0.4^{\circ }$ & $22.6^{\circ }$ & $3.0^{\circ }$ & $-4.6^{\circ }$ \\
+average sub-observer latitude & $1.6^{\circ }$ & $0.3^{\circ }$ & $61.5^{\circ }$ & $-73.7^{\circ }$  \\
+initial sub-solar longitude & $267.6^{\circ }$ & $286.0^{\circ }$ & $296.7^{\circ }$ & $33.2^{\circ }$ \\
+initial sub-observer longitude & $210.1^{\circ }$ & $210.5^{\circ }$ & $210.1^{\circ }$ & $300.6^{\circ }$ \\ \hline
 \end{tabular}

### 2016-09-13 paper/main.tex
new mock data based on simplified Earth surface map

@@
 
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Test with idealized mock data}
+\label{s:mockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\# of Surface Types}
-\label{ss:regularization}
+\subsection{Creating Mock Data}
+\label{ss:createmockdata}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Testing with mock data}
-\label{s:mockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
+For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
+We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction.
+The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
+The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.
+
+We then compute the geometrically weighted area fraction of each surface type (``contribution factor'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature \memoYF{Describe in more detail.}; this is shown in the lower left panel of Figure \ref{fig:mockdata}.
+Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers.
+The effect of atmosphere is completely ignored.
+The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bpth]
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
+    \end{center}
+     \end{minipage}
+  \begin{minipage}{0.5\hsize}
+    \begin{center}
+    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
+    \end{center}
+\end{minipage}
+  \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
+    \end{center}
+ \end{minipage}
+   \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
+    \end{center}
+ \end{minipage}
+    \caption{Our mock data based on Earth surface. }
+\label{fig:mockdata}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Testing Rotational Unmixing with Mock Data}
+\label{ss:testmockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-10-04 main_map_EPOXI_mcmc.py
syncing with remote

@@ -139,6 +139,11 @@ def lnprob(Y_array, *args):
         print 'chi2/d.o.f.', chi2 / (len(Y_array)*1.-1.), len(Y_array)
 
     answer = - chi2 + ln_prior_albd + ln_prior_area + regterm_area
+
+    # Check for nans
+    if np.isnan(answer):
+        answer = -np.inf
+
     if flip :
         return -1. * answer
     else :

### 2016-10-04 mcmc_physical.py

@@ -163,6 +163,17 @@ def convolve_with_eye(wl, spectrum):
         colormodels.rgb_from_xyz (ciexyz.xyz_from_spectrum (spec)))
     return rgb_eye
 
+def plot_reg1(samples):
+    reg == 'Tikhonov'
+    par = 'sigma', samples[-1]
+    fig = plt.figure(figsize=(16,8))
+    gs = gridspec.GridSpec(1,2)
+    ax0 = plt.subplot(gs[0])
+    ax1 = plt.subplot(gs[1])
+    ax0.set_ylabel("Area Fraction")
+    ax0.set_xlabel("Slice #")
+    ax1.set_ylabel("Albedo")
+
 
 
 #===================================================

### 2016-10-04 prior.py

@@ -235,7 +235,7 @@ def regularize_area_tikhonov( x_area_lk, regparam ):
 #    return ln_prior
 
 
- 
+
 #---------------------------------------------------
 #def get_ln_prior_area_old( y_area_lj, x_area_lj ):
 #
@@ -271,4 +271,3 @@ def regularize_area_tikhonov( x_area_lk, regparam ):
 #
 #    ln_prior = np.log( dxdy_det )
 #    return ln_prior
- 

### 2016-10-05 mcmc_analysis.py
minor updates

@@ -25,6 +25,8 @@ DIR = "mcmc_output/"
 # Specify burn-in index for corner plot
 DEFAULT_BURN_INDEX = 0
 
+DEFAULT_WHICH = None
+
 def estimate_burnin1(samples):
     # Determine time of burn-in by calculating first time median is crossed
     # Algorithm by Eric Agol 2016
@@ -45,7 +47,7 @@ def estimate_burnin1(samples):
     # Now return the index of the last walker to cross its median
     return np.amax(first_median_crossing)
 
-def plot_trace(samples, directory="", X_names=None):
+def plot_trace(samples, directory="", X_names=None, which=None):
 
     print "Plotting Trace..."
 
@@ -58,6 +60,8 @@ def plot_trace(samples, directory="", X_names=None):
 
     # Loop over all parameters making trace plots
     for i in range(nparam):
+        if which is not None:
+            i = which
         print i
         if X_names is None:
             pname = ""
@@ -80,30 +84,37 @@ def plot_trace(samples, directory="", X_names=None):
         plt.setp(ax1.get_xticklabels(), fontsize=18, rotation=45)
         plt.setp(ax1.get_yticklabels(), fontsize=18, rotation=45)
         fig.subplots_adjust(wspace=0)
-        fig.savefig(directory+"trace"+str(i)+".png")
+        fig.savefig(directory+"trace"+str(i)+".png", bbox_inches="tight")
+        fig.clear()
+        plt.close()
+        if which is not None:
+            break
     return
 
 #===================================================
 if __name__ == "__main__":
 
     # Read command line args
-    myopts, args = getopt.getopt(sys.argv[1:],"d:b:")
+    myopts, args = getopt.getopt(sys.argv[1:],"d:b:n:")
     run = ""
+    iburn = DEFAULT_BURN_INDEX
+    which = DEFAULT_WHICH
     for o, a in myopts:
         # o == option
         # a == argument passed to the o
-        # Get MCMC directory timestamp name
         if o == '-d':
+            # Get MCMC directory timestamp name
             run=a
+        elif o == "-b":
+            # Get burn in index
+            iburn = int(a)
+        elif o == "-n":
+            # Get which index
+            which = int(a)
         else:
-            print("Please specify run directory using -d: \n e.g. >python mcmc_physical.py -d 2016-07-13--11-59")
-            sys.exit()
-        # Get burn in index
-        if o == "-b":
[…]

### 2016-10-05 paper/main.tex
mock data based on IGBP map
equations are detailed so that the following arguments can be made + text updates

@@
 However, interpretation of disk-integrated colors is not trivial. 
-This is particularly true for Earth-like planets which may harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possible biological surfaces, e.g.
+This is particularly true for Earth-like planets that harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possible biological surfaces, e.g.
 vegetation.
-Disentangling specific features from mixed disk-integrated color can be very challenging.
+Disentangling specific features from the mixed disk-integrated colors can be very challenging.
 
-A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to planetary spin rotation and orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
+A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to the planetary spin rotation and the orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
 \citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components (with a difference of 1) and that the variation pattern is indicative of the surface properties.
-\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, where they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
+\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
 Moreover, by coupling the time variation due to spin rotation and that due to orbital revolution, 2-dimensional information of the surface may be retrieved with sufficient quality of data \citep{Kawahara2010, Kawahara2011, Fujii2012}.
@@
 \citet{Cowan2013} took another approach to the same inverse problem. 
-Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters and letting them to fit the data.
+Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters and letting them fit the data.
 The result appeared successful to the extent that the obtained reflectance spectra roughly match the typical spectra of clouds, ocean, and continents. 
@@
 
-Assuming that the planetary surface is Lambertian scatterer everywhere, with a certain number $K$ of mutually distinct surface types, 
-the disk-integrated spectra can be written as a weighted summation of the reflectance spectra of different surface types, e.g., 
+Assuming that the planetary surface is Lambertian scatterer everywhere, with a certain number $K$ of spectrally distinct surface types, 
+the disk-integrated scattered light can be written as a weighted summation of the reflectance spectra of different surface types.
+
+For the moment, let us suppose that the planetary radius and the observational geometry (latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet) are fully known.
+(This will be relaxed in \S\ref{s:discussion}.)
+In this case, we can straightforwardly translate the observed planetary intensity to albedo (or reflectivity) using the stellar flux. 
+A useful normalization for albedo in exoplanet observations is {\it apparent albedo}, which is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will consistently use apparent albedo for our study unless otherwise noted.
+
+The observed apparent albedo, $d_{ij}$ (``$d$'' for data), can be written as \citep[see][]{Fujii2010}: 
 %%%
-\begin{equation}
-d_{ij} = R_p^2 \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
-\end{equation}
+\begin{eqnarray}
+d_{i} (\lambda_j) &=& \displaystyle \frac{ \int_{{\rm IV}_i} s_{\vec \Omega }(\lambda_j) \cdot \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
+&=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
+&\equiv & \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
+\end{eqnarray}
 %%%
-where $R_p$ is the planetary radius, $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively \citep[see][]{Fujii2010} . 
-The symbols represent as follows:
-$d_{ij}$ is the observed apparent albedo (``$d$'' for data) at $i$-th epoch and $j$-th band, 
-$f_{lk}^{\ast }$ is the contribution factor of the $k$-th surface type at $i$-th observational epoch, and 
+where $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
+In the last expression, $f_{lk}^{\ast }$ represents the contribution factor of the $k$-th surface type at $i$-th observational epoch, and 
 $s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
 The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
+
+By definition, that the area fraction $f$ and reflectance spectra $s$ are subject to the following conditions:
+%%%
+\begin{eqnarray}
+\begin{cases}
+\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
+\;\; 0 < f^{\ast }_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
+\;\; \sum_k f_{lk}^{\ast } = 1 & \mbox{for any $l$} 
+\end{cases}
+\label{eq:constraints_ast}
+\end{eqnarray}
+%%%
 
@@
 
-The contribution factor $f^{\ast }$ is the weighted summation of the area fraction of $k$-th surface type, i. e.,
+The time variability of the contribution factor $f^{\ast }$ due to spin rotation is related to the surface inhomogeneity along the equator.
+Approximately, $f^{\ast }_{ik}$ may be written as the weighted summation of the area fraction of $k$-th surface type in each of (the finite number $L$ of) longitudinal slices, i.e.,
 %%%
-\begin{equation}
-f^{\ast }_{ik} = \sum _{l} W_{il} f_{lk}
-\end{equation}
+\begin{eqnarray}
+f^{\ast }_{ik} &=& \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
+&=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
+&\sim & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
+&\equiv & \sum_l  W_{il} f_{lk}
+\end{eqnarray}
 %%%
-where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type at $l$-th longitudinal slice, and 
-$W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
-The maximum number of $l$ is denoted by $L$. 
+where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type in the $l$-th longitudinal slice. 
+The approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little in the $l$-th slice for all $k$ and $l$. 
+In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
 As a result,
@@
 %%%
-
-Because $f$ is area fraction and $s$ is reflectance spectra, they are subject to the following constraints:
+with the following condition similar to equation (\ref{eq:cond_f_ast}):
 %%%
@@
 %%%
+Now, the relevant problem is, given $d_{ij}$, estimate both $f_{lk}$ and $s_{kj}$ subject to the constraints of equation (\ref{eq:constraints})---this is where \citet{Cowan2013} stood.
 
-Now, in the case that the planetary radius and observational geometry (latitude and longitude of the sub-stellar point and the sub-observer point) is fully known, the relevant problem is, given $d_{ij}$, estimate both $f_{lk}$ and $s_{kj}$ subject to the constraints of equation (\ref{eq:constraints}).
----This is pioneered by trial by \citet{Cowan2013}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fit with $f$ or $f^{\ast}$?}
+\label{ss:degeneracy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!bpth]
+    \begin{center}
+\includegraphics[width=\hsize]{PCA_projected.pdf}
+    \end{center}
+    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
+\label{fig:shrinkwrap}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Since one of them includes lunar transit in front of the Earth and the interpretation is not straightforward, we just remove it from our data and consider only 4 series of observations, which were conducted on March 2008, June 2008, March 2009, and October 2009.
-The data are presented in Figure \ref{fig:EPOXIlc} in terms of {\it apparent albedo}, the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}.
+The data are presented in Figure \ref{fig:EPOXIlc} in terms of {\it apparent albedo}.
 

### 2016-10-05 map_utils.py
added hdf5 saving function

@@ -1,4 +1,61 @@
 import numpy as np
+import h5py
+
+#---------------------------------------------------
+def save2hdf5(f, dataset, name="dataset", dictionary=None, compression='lzf', close=True):
+    """
+    Saves a dataset (e.g. numpy array) to a new or existing hdf5 file with ability to save a
+    dictionary as attributes to that dataset.
+
+    Parameters
+    ----------
+    f : str OR h5py._hl.files.File
+        Name of new hdf5 file OR existing h5py file object
+    dataset : numpy array
+        Data to be saved
+    name : str
+        Name of new dataset to be saved
+    dictionary : dict
+        Dictionary of attributes for dataset
+    compression : str
+        h5py compression algorithm
+    close : bool
+        If False returns new h5py._hl.files.File
+    """
+
+    # Hack for interactive use with iPython notebook:
+    try:
+        f.close()
+    except (NameError, ValueError, AttributeError):
+        pass
+
+    # Create new hdf5 file
+    if type(f) is str:
+        filename = f
+        f = h5py.File(filename, 'w')
+    elif type(f) is h5py._hl.files.File:
+        pass
+    else:
+        print "Invalid type(f)"
+        return None
+
+    # Create dataset for mcmc chain samples
+    s = f.create_dataset('samples', data=samples, compression=compression)
+
+    # Save dictionary to attributes
+    if dictionary is not None:
+        # Loop through python dictionary, saving each item as an hdf5 attribute
+        # under the same name
+        for key, value in dictionary.iteritems(): s.attrs[key] = value
+
+    if close:
+        # Close the file stream
+        f.close()
+        return None
+    else:
+        # Return the file stream
+        return f
+#---------------------------------------------------
 
 #---------------------------------------------------
 def generate_tex_names(n_type, n_band, n_slice):
@@ -36,3 +93,4 @@ def generate_tex_names(n_type, n_band, n_slice):
     X_names = np.concatenate([np.array(Atmp), np.array(Ftmp)])
 
     return Y_names, X_names
+#---------------------------------------------------

### 2016-10-05 main_fitlc_mcmc_EPOXI_NEW.py
new hdf5 saving

@@ -15,7 +15,7 @@ from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVE
 
 import prior
 import reparameterize
-from map_utils import generate_tex_names
+from map_utils import generate_tex_names, save2hdf5
 
 NCPU = multiprocessing.cpu_count()
 
@@ -290,10 +290,33 @@ if __name__ == "__main__":
     # Run MCMC
     sampler.run_mcmc( p0, NUM_MCMC )
 
+    # Get emcee chain samples
     original_samples = sampler.chain
 
+    ############ Save HDF5 File ############
+
+    # Specify save file
+    hfile = run_dir + "samurai_out.hdf5"
+
+    # print
+    print "Saving:", hfile
+
+    # Add moderately small files to dictionary
+    dictionary = {
+        "data" : data,
+        "Y_names" : Y_names,
+        "X_names" : X_names,
+        "N_TYPE" : N_TYPE,
+        "N_SLICE" : n_slice,
+        "p0" : p0
+    }
+
+    # Save emcee samples with dictionary as metadata
+    save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary, compression='lzf')
+
+    """# Old saving
     print "Saving:", run_dir+"mcmc_samples.npz"
     np.savez(run_dir+"mcmc_samples.npz", data=data, samples=original_samples, \
              Y_names=Y_names, X_names=X_names, N_TYPE=N_TYPE, N_SLICE=n_slice, p0=p0)
-
+    """
     sys.exit()

### 2016-10-05 main_map_EPOXI_mcmc.py

@@ -14,7 +14,7 @@ import corner
 import geometry
 import prior
 from reparameterize import *
-from map_utils import generate_tex_names
+from map_utils import generate_tex_names, save2hdf5
 
 #--------------------------------------------------------------------
 # Parameters
@@ -281,9 +281,32 @@ if __name__ == "__main__":
     # Extract chain from sampler
     original_samples = sampler.chain
 
+    ############ Save HDF5 File ############
+
+    # Specify save file
+    hfile = run_dir + "samurai_out.hdf5"
+
+    # print
+    print "Saving:", hfile
+
+    # Add moderately small files to dictionary
+    dictionary = {
+        "data" : data,
+        "Y_names" : Y_names,
+        "X_names" : X_names,
+        "N_TYPE" : N_TYPE,
+        "N_SLICE" : n_slice,
+        "p0" : p0
+    }
+
+    # Save emcee samples with dictionary as metadata
+    save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary, compression='lzf')
+
+    """# Old saving
     # Save chains and other info
     print "Saving:", run_dir+"mcmc_samples.npz"
     np.savez(run_dir+"mcmc_samples.npz", data=data, samples=original_samples,\
              Y_names=Y_names, X_names=X_names, N_TYPE=N_TYPE, N_SLICE=N_SLICE, p0=p0)
+    """
 
     sys.exit()

### 2016-10-05 paper/main.tex
description added

@@
 
-By definition, that the area fraction $f$ and reflectance spectra $s$ are subject to the following conditions:
+By definition, the area fraction $f$ and reflectance spectra $s$ are subject to the following conditions:
 %%%
@@
 &=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
-&\sim & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
-&\equiv & \sum_l  W_{il} f_{lk}
+&\sim & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
+&\equiv & \sum_l  W_{il} f_{lk} \label{eq:Wf}
 \end{eqnarray}
@@
 %%%
-Now, the relevant problem is, given $d_{ij}$, estimate both $f_{lk}$ and $s_{kj}$ subject to the constraints of equation (\ref{eq:constraints})---this is where \citet{Cowan2013} stood.
+Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of equation (\ref{eq:constraints})---this is where \citet{Cowan2013} stood.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fit with $f$ or $f^{\ast}$?}
+\subsection{Fit with $f$ or with $f^{\ast}$?}
 \label{ss:degeneracy}
@@
 
-We argue that estimating $f$ and $s$ is no superior to estimating $f^*$ and $s$ subject to the following similar constraint:
-%%%
-\begin{eqnarray}
-\begin{cases}
-\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 < f^{\ast }_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \\
-\;\; \sum_k f_{lk}^{\ast } = 1 & \mbox{for any $l$} 
-\end{cases}
-\label{eq:constraints_ast}
-\end{eqnarray}
-%%%
-\memoYF{write here}.
+\memoYF{I am not 100\% sure if the following statement is right. Need to check.} 
+We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ f^{\ast }, s \}$. 
+One reason comes from the fact the approximation adopted in equation (\ref{eq:discretize}). This is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
+If this isn't the case, equation (\ref{eq:Wf}) is no longer a good discritization.
+
+If that condition is satisfied for $L=I$ slices, then in general cases there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$.
 

### 2016-10-06 map_utils.py
added hdf5 to mcmc_analysis; partially added to mcmc_physical

@@ -40,7 +40,7 @@ def save2hdf5(f, dataset, name="dataset", dictionary=None, compression='lzf', cl
         return None
 
     # Create dataset for mcmc chain samples
-    s = f.create_dataset('samples', data=samples, compression=compression)
+    s = f.create_dataset(name, data=dataset, compression=compression)
 
     # Save dictionary to attributes
     if dictionary is not None:

### 2016-10-06 mcmc_analysis.py

@@ -1,6 +1,4 @@
 import numpy as np
-import healpy as hp
-import emcee
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
@@ -14,7 +12,7 @@ import corner
 import datetime
 import multiprocessing
 import os
-import pdb
+import h5py
 
 
 # Specify directory of run to analyze
@@ -51,11 +49,12 @@ def plot_trace(samples, directory="", X_names=None, which=None):
 
     print "Plotting Trace..."
 
-    nwalkers = samples.shape[0]
-    nsteps = samples.shape[1]
-    nparam = samples.shape[2]
+    nwalkers = samples.attrs["nwalkers"]
+    nsteps = samples.attrs["nsteps"]
+    nparam = samples.attrs["nparam"]
 
     # Flatten chains for histogram
+    print "Flattening chains for histogram (slow)..."
     samples_flat = samples[:, :, :].reshape((-1, nparam))
 
     # Loop over all parameters making trace plots
@@ -118,6 +117,26 @@ if __name__ == "__main__":
 
     MCMC_DIR = DIR + run + "/"
 
+    # Load MCMC samples
+    try:
+        # Open the file stream
+        f = h5py.File(MCMC_DIR+"samurai_out.hdf5", 'r')
+    except IOError:
+        print "Run directory does not exist! Check -d argument."
+        sys.exit()
+
+    # Extract info from HDF5 file
+    samples=f["samples"]
+    data = samples.attrs["data"]
+    N_TYPE = samples.attrs["N_TYPE"]
+    p0 = samples.attrs["p0"]
+    X_names = samples.attrs["X_names"]
+    Y_names = samples.attrs["Y_names"]
+    nwalkers = samples.attrs[0]
+    nsteps = samples.attrs[1]
+    nparam = samples.attrs[2]
+
+    """
     # Load MCMC samples from numpy archive
     try:
         temp = np.load(MCMC_DIR+"mcmc_samples.npz")
@@ -136,9 +155,7 @@ if __name__ == "__main__":
     nwalkers = samples.shape[0]
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
-
-    # Flatten chains
-    samples_flat = samples[:,iburn:,:].reshape((-1, nparam))
+    """
 
     if "trace" in str(sys.argv):
 
@@ -154,8 +171,15 @@ if __name__ == "__main__":
         plot_trace(samples, X_names=Y_names, directory=trace_dir, which=which)
[…]

### 2016-10-06 mcmc_physical.py

@@ -1,14 +1,12 @@
 import numpy as np
 import healpy as hp
 import emcee
-import matplotlib.pyplot as pl
 from scipy.optimize import minimize
 import sys, getopt
 import corner
 import datetime
 import multiprocessing
 import os
-import pdb
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
@@ -18,6 +16,7 @@ import pdb
 from colorpy import colormodels, ciexyz
 
 from reparameterize import transform_Y2X
+from map_utils import save2hdf5
 
 mpl.rc('font', family='Times New Roman')
 mpl.rcParams['font.size'] = 25.0
@@ -214,6 +213,26 @@ if __name__ == "__main__":
 
     MCMC_DIR = DIR + run + "/"
 
+    # Load MCMC samples
+    try:
+        # Open the file stream
+        f = h5py.File(MCMC_DIR+"samurai_out.hdf5", 'r+')
+    except IOError:
+        print "Run directory does not exist! Check -d argument."
+        sys.exit()
+
+    # Extract info from HDF5 file
+    samples=f["samples"]
+    data = samples.attrs["data"]
+    N_TYPE = samples.attrs["N_TYPE"]
+    p0 = samples.attrs["p0"]
+    X_names = samples.attrs["X_names"]
+    Y_names = samples.attrs["Y_names"]
+    nwalkers = samples.attrs[0]
+    nsteps = samples.attrs[1]
+    nparam = samples.attrs[2]
+
+    """# old load
     # Load MCMC samples from numpy archive
     try:
         temp = np.load(MCMC_DIR+"mcmc_samples.npz")
@@ -234,6 +253,7 @@ if __name__ == "__main__":
     nwalkers = samples.shape[0]
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
+    """
 
     # Unpack Data
     Obs_ij = data[0]
@@ -245,12 +265,53 @@ if __name__ == "__main__":
     # Compute slice longitude
     #slice_longitude = np.array([-180. + (360. / n_slice) * (i + 0.5) for i in range(n_slice)])
 
-    try:
+    """
+    temp = np.load(MCMC_DIR+"mcmc_physical_samples.npz")
+    xsam = temp["xsam"]
+    """
+
+    NAME_YSAM = "samples"
+    NAME_XSAM = "physical_samples"
+
+    # If the xsamples are already in the hdf5 file
[…]

### 2016-10-06 paper/main.tex
minor updates

@@
 \;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 < f_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \\
+\;\; 0 < f_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f} \\
 \;\; \sum_k f_{lk} = 1 & \mbox{for any $l$} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fit with $f$ or with $f^{\ast}$?}
+\subsection{Fit data with $f$ or with $f^{\ast}$?}
 \label{ss:degeneracy}
@@
 \memoYF{I am not 100\% sure if the following statement is right. Need to check.}
+
 We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ f^{\ast }, s \}$. 
-One reason comes from the fact the approximation adopted in equation (\ref{eq:discretize}). This is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
-If this isn't the case, equation (\ref{eq:Wf}) is no longer a good discritization.
+%
+One reason comes from the fact the approximation adopted in equation (\ref{eq:discretize}) is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
+Otherwise, fitting data with $f$ by equation (\ref{eq:Wf}) includes some errors by design.
 
-If that condition is satisfied for $L=I$ slices, then in general cases there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$.
+%Suppose the above approximation is justified. 
+In essence, $f^{\ast }_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
+%
+If $L=I$, in general there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
+In this case, clearly, equations (\ref{eq:cond_f_ast}) and (\ref{eq:cond_f}) are equivalent given $W_{il}>0$ (for any $i$ and $j$), and $\sum _l W_{il} = 1$. 
+%
+If $L<I$, $W$ works as a low-pass filter, as discussed in \citet{Cowan2013}. 
+In this case, the inverse problem described by equation (\ref{eq:Wf}), $f^{\ast }=Wf$ is an overdetermined system, and one must to find the solution for $f$ by some means (e.g.
+least squares method), and the resultant $f$ may not automatically satisfy the condition listed by eqution (\ref{eq:cond_f}).
+However, this is because of the design of the problem and the assumed lowered resolution, and not because of the wrong estimation for $f$ (or $s$).
+
+Thus, although both $\{ f^{\ast }, s \}$ and $\{ f, s \}$ could be a fitting parameters to the light curves, the estimation for $s$ should not be affected by this conversion in fitting parameters. 
+In that sense, $\{ f, s \}$ is not likely to return a better solution than $\{ f^{\ast }, s \}$ does.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Degeneracy}
+\subsection{Strong Degeneracy}
 \label{ss:degeneracy}

### 2016-10-06 paper/main.tex
text updated, reference updated, results of mock data added

--- 2016-10-05 paper/main.tex
@@
    \hbox{$\sim$}}\raise 1.5pt\hbox{$<$}\;}
+%\def\fast{\;$f^{\ast }$\;}
+\def\fast{\tilde f}
 
@@
 
-\def\memoYF#1{\color{red}{\bf [#1]}\color{black}}
+\def\memoYF#1{\color{red}[NOTE: {\bf #1}]\color{black}}
 
@@
 A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to the planetary spin rotation and the orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
-\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components (with a difference of 1) and that the variation pattern is indicative of the surface properties.
+\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components; (\# of surface types) $\ge $ (\# of principal componentes) $+ 1$.
+%) and that the variation pattern is indicative of the surface properties.
 \citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
@@
 &=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
-&\equiv & \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
+&\equiv & \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:d_f_ast_s}
 \end{eqnarray}
@@
 where $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
-In the last expression, $f_{lk}^{\ast }$ represents the contribution factor of the $k$-th surface type at $i$-th observational epoch, and 
+In the last expression, $\fast_{lk}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
 $s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
@@
 \;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 < f^{\ast }_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
-\;\; \sum_k f_{lk}^{\ast } = 1 & \mbox{for any $l$} 
+\;\; 0 < \fast_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
+\;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
 \end{cases}
-\label{eq:constraints_ast}
 \end{eqnarray}
@@
 
-The time variability of the contribution factor $f^{\ast }$ due to spin rotation is related to the surface inhomogeneity along the equator.
-Approximately, $f^{\ast }_{ik}$ may be written as the weighted summation of the area fraction of $k$-th surface type in each of (the finite number $L$ of) longitudinal slices, i.e.,
+The time variability of the apparent covering fraction $\fast $ due to spin rotation is related to the surface inhomogeneity along the equator.
+Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of $k$-th surface type in each of (the finite number $L$ of) longitudinal slices, i.e.,
 %%%
 \begin{eqnarray}
-f^{\ast }_{ik} &=& \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
+\fast _{ik} &=& \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
 &=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
@@
 \begin{equation}
-d_{ij} = R_p^2 \sum _{l,k} W_{il} \, f_{lk} \, s_{kj}
+d_{ij} = R_p^2 \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
 \end{equation}
@@
 
+\citet{Cowan2013} suggested the specific procedure to find the solution for $\{f, s\}$. 
+Namely, 
+(1) perform PCA on the data to reduce the dimensionality as needed, 
+(2) perform simplex shrink-wrapping analysis to find the first guess for $s$, 
+and 
+(3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
+(In the last step, the initial value for $f$ is fixed at 1/(\# of surface types).)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fit with $f$ or with $f^{\ast}$?}
+\subsection{Fit data with $f$ or with $f^{\ast}$?}
 \label{ss:degeneracy}
@@
 
-\memoYF{I am not 100\% sure if the following statement is right. Need to check.} 
+\memoYF{I am not 100\% sure if the following statement is right. Need to check. The argument below probably makes sense for the noiseless case. What if the data are noisy?}
+
 We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ f^{\ast }, s \}$. 
-One reason comes from the fact the approximation adopted in equation (\ref{eq:discretize}). This is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
-If this isn't the case, equation (\ref{eq:Wf}) is no longer a good discritization.
+%
+One reason comes from the approximation adopted in equation (\ref{eq:discretize}) is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
+Otherwise, fitting data with $f$ by equation (\ref{eq:Wf}) produces some errors by design.
 
-If that condition is satisfied for $L=I$ slices, then in general cases there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$.
+%Suppose the above approximation is justified. 
+In essence, $f^{\ast }_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
+%
+If $L=I$, in general there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
+In this case, clearly, equations (\ref{eq:cond_f_ast}) and (\ref{eq:cond_f}) are equivalent, given $W_{il}>0$ (for any $i$ and $j$) and $\sum _l W_{il} = 1$. 
+%
+If $L<I$, the matrix $W$ works as a low-pass filter \citep{Cowan2013}. 
+In this case, the inverse problem described by equation (\ref{eq:Wf}), $f^{\ast }=Wf$, is an overdetermined system, and one must to find the solution for $f$ by some means (e.g.
+the least squares method), and the resultant $f$ may not automatically satisfy the condition listed by eqution (\ref{eq:cond_f}).
+However, this is because of the design of the problem and the assumed lowered resolution.
+
+Therefore, although either $\{ \fast, s \}$ or $\{ f, s \}$ could be fitting parameters to the data, the estimation for $s$ should not be affected by this conversion in fitting parameters. 
+In that sense, $\{ f, s \}$ is not likely to return a better solution than $\{ \fast, s \}$ does. 
+Rather, it could return less reasonable results because of the approximation adopted in equation (\ref{eq:discretize}).
+
+\memoYF{\citet{Cowan2013} found a more reasonable answer for $s$ when they fitted with $\{ f, s \}$, but I think this is a coincidence. }
 
@@
 
+\memoYF{The degeneracy in solving $\{ \fast ,\,s\} $ is already indicated in \citet{Cowan2013}, but might be worth clarifying here again. }
+
+One could try to find the solutions for $\{ \fast, s \}$ given $d$ using equation (\ref{eq:d_f_ast_s}), or the solutions for  $\{ f, s \}$ using equation (\ref{eq:d_f_s}), but we must keep in mind that
+these two formulations both embrace intrinsic degeneracies in the solutions if there is no other information about $\fast$ (or $f$) and $s$.
+
 %%%
-\begin{equation}
-\tilde d_{ij} = \sum _{i,k} f_{ik}^{\ast } \, s_{kj}
-\end{equation}
+%\begin{equation}
+%d_{ij} = \sum _{i,k} f^{\ast }_{ik} \, s_{kj} \tag{\ref{eq:d_f_ast_s}}
+%\end{equation}
 %%%
-where $\tilde d_{ij} = d_{ij}/R_p^2$. 
-Without any constraints on $f^{\ast }$ and $s$, it is trivial to notice the degeneracy in the solutions. 
-Using an arbitrary regular matrix $X$ with rank $K$, a particular set of solution $\{ f^{\ast },\,s\}$ implies another set of solution $\{ f^{\ast }X^{-1},\,Xs\}$.
+%When one tries to find solutions for both $\fast$ and $s$ given $d$, the results are strongly degenerate if there are not other information about $\fast$ and $s$.
 
-Now that they are subject to the constraints (equation (\ref{eq:constraints_ast})), the range of acceptable solution is limited. 
-However, the constraints cannot be sufficient to reduce them to a unique solution. 
-One can create a infinite number of candidates for $f_{ik}^{\ast }$ which satisfies both of the two constraints for $f$, then $s$ may be obtained by $s = f^{+} \tilde d$, where $f^+$ is the pseudo-inverse matrix (note that $K < I$ to be able to find the solution) and among these solutions there should be many that satisfy the constraint for $s$ as well.
-\memoYF{Need to brush up. Possibly need to consider SVD of $f$. }
+Without any constraints on $\fast$ (or $f$) and $s$, it is trivial to notice the degeneracy in the solutions. 
+Using an arbitrary regular matrix $X$ with rank $K$, a particular set of solution $\{ \fast ,\,s\}$ implies another set of solution $\{ \fast X^{-1},\,Xs\}$.
 
-To see this, we demonstrate the application to the mock data with known solution in Section \ref{s:mockdata}.
+Now that they are subject to the constraints (equation (\ref{eq:cond_f_ast}) or (\ref{eq:cond_f})), the range of the acceptable solution is limited.
+Nevertheless, the constraints cannot be sufficient to narrow them to a unique set of solution.
+%
+To see this, %let us consider equation (\ref{eq:d_f_ast_s}) for the moment.
+imagine a $J$-dimensional space.
+Suppose there are $K$ number of vertices in that space, $\vec x_1,\,\vec x_2,\,...,\,\vec x_K$, and that all of the coordinate of $\vec x_k$ in this $J$-dimensional space is between 0 and 1. 
+Mathematically, any points (say, $\vec y_1$, $\vec y_2$, ..., $\vec y_I$) that are {\it enclosed} in the hyperplane defined by these vertices may be represented by $\vec y_i=\sum _k^K p_{ik} \vec x_k $ where $\sum _k^K p_{ik} = 1$ for any $i$.
+%In the matrix form, $Y_{ij} = P_{ik} X_{kj}$. 
+This is essentially same as the situation described by equation (\ref{eq:d_f_ast_s}). 
+In other words, any set of vertices in $J$-dimensional space that can enclose the observed data, $\vec d_i$, if any, can be the solutions for equation (\ref{eq:d_f_ast_s}), as long as all of the element in $x_{kj}$ satisfy $0<x_{kj}<1$.
 
@@
 
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Creating Mock Data}
-\label{ss:createmockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
-For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
-We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction.
-The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
-The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.
-
-We then compute the geometrically weighted area fraction of each surface type (``contribution factor'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature \memoYF{Describe in more detail.}; this is shown in the lower left panel of Figure \ref{fig:mockdata}.
-Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers.
-The effect of atmosphere is completely ignored.
-The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bpth]
+\begin{figure*}[!hbt]
     \begin{minipage}{0.5\hsize}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Creating Mock Data}
+\label{ss:createmockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
+For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
+We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction.
+The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
+The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.
+
+We then compute the geometrically weighted area fraction of each surface type (``apparent covering fraction'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature, as is shown in the lower left panel of Figure \ref{fig:mockdata}.
+Specifically, we fix the sub-observer latitude at $0^{\circ }$, sub-observer at $0^{\circ }$, the sub-solar latitude at $0^{\circ }$, and sub-solar longitude at $90^{\circ }$. 
+Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers.
+The effect of atmosphere is completely ignored.
+The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{PCA and Shrink-Wrapping}
+\label{ss:shrinkwrap}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Now, we analyze the mock data created in the preceding section (Figure \ref{fig:mockdata}). 
+In this section, the result of PCA and shrink-wrapping are presented and discussed.
+
+PCA on the mock data indicated one dominant component (contribution: $\sim $98\%) and one minor component (contribution: $\sim $2\%).
+The residual is virtually zero, leaving 2 components in total, consistent with the assumption of 3 surface types.
+The corresponding principal components are shown in Figure \ref{fig:PCs}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Testing Rotational Unmixing with Mock Data}
-\label{ss:testmockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Then, we performed simplex shrink-wrapping analysis in the plane defined by these two principal components, based on the algorithm described in \citet{Fuhrmann1999}. 
+The result are presented in Figure \ref{fig:shrinkwrap}. 
+The black solid line indicates the trajectory of the light curves projected in this plane. 
+The minimum-volume triangle that encloses the data points are found at the orange line in the same figure. 
+For reference, the locations of the assumed three surface colors projected onto this plane are shown as points. 
+As can be seen, the light curves the minimum-volume enclosure does not match the colors of physical surfaces, except for ocean. 
+This is a natural consequence from the fact that the soil and vegetation are minor components and never dominate the surface in the illuminated and visible area, while the apparent covering fraction of ocean comes close to unity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bpth]
+    \begin{center}
+\includegraphics[width=\hsize]{xmed_std_time.pdf}
+\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
+    \end{center}
+    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
+\label{fig:shrinkwrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-10-07 fitlc_params.py
hdf5 fully implemented; removed param files from gitignore

@@ -1,0 +1,35 @@
+import numpy as np
+
+#--------------------------------------------------------------------
+# Parameters
+#--------------------------------------------------------------------
+
+NUM_MCMC = 10000
+NUM_MCMC_BURNIN = 0
+SEED_AMP = 0.5
+
+REGULARIZATION = None
+#REGULARIZATION = 'GP'
+#REGULARIZATION = 'GP2'
+#REGULARIZATION = 'Tikhonov'
+
+SIGMA_Y  = 3.0
+NOISELEVEL = 0.01
+
+FLAG_REG_AREA = False
+FLAG_REG_ALBD = False
+
+#n_slice = 4
+N_TYPE  = 3
+
+deg2rad = np.pi/180.
+
+N_SIDE   = 32
+#INFILE = "data/raddata_12_norm"
+INFILE = "data/raddata_2_norm"
+#INFILE = "mockdata/mock_simple_1_data"
+#INFILE = "mockdata/mock_simple_3types_1_data"
+# INFILE = 'mockdata/mock_simple_1_scattered0.01_data_with_noise'
+
+def calculate_walkers(n_dim):
+    return 10*n_dim

### 2016-10-07 main_fitlc_mcmc_EPOXI_NEW.py

@@ -301,18 +301,32 @@ if __name__ == "__main__":
     # print
     print "Saving:", hfile
 
-    # Add moderately small files to dictionary
+    # Add small files to dictionary
     dictionary = {
-        "data" : data,
         "Y_names" : Y_names,
         "X_names" : X_names,
         "N_TYPE" : N_TYPE,
         "N_SLICE" : n_slice,
-        "p0" : p0
+        "N_REGPARAM" : N_REGPARAM
+    }
+
+    # Create dict for additional datasets (larger arrays)
+    data_dict = {
+    "Obs_ij" : Obs_ij,
+    "Obsnoise_ij" : Obsnoise_ij,
+    "Kernel_il" : Kernel_il,
+    "p0" : p0
     }
 
     # Save emcee samples with dictionary as metadata
-    save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary, compression='lzf')
+    f = save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary,
+              compression='lzf', close=False)
+    # Save data to hdf5 file
+    for key, value in data_dict.iteritems():
+        f.create_dataset(key, data=value, compression='lzf')
+
+    # Close hdf5 file stream
+    f.close()
 
     """# Old saving
     print "Saving:", run_dir+"mcmc_samples.npz"

### 2016-10-07 main_map_EPOXI_mcmc.py

@@ -289,19 +289,32 @@ if __name__ == "__main__":
     # print
     print "Saving:", hfile
 
-    # Add moderately small files to dictionary
+    # Add small files to dictionary
     dictionary = {
-        "data" : data,
         "Y_names" : Y_names,
         "X_names" : X_names,
         "N_TYPE" : N_TYPE,
         "N_SLICE" : n_slice,
-        "p0" : p0
+        "N_REGPARAM" : N_REGPARAM
+    }
+
+    # Create dict for additional datasets (larger arrays)
+    data_dict = {
+    "Obs_ij" : Obs_ij,
+    "Obsnoise_ij" : Obsnoise_ij,
+    "Kernel_il" : Kernel_il,
+    "p0" : p0
     }
 
     # Save emcee samples with dictionary as metadata
-    save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary, compression='lzf')
+    f = save2hdf5(hfile, original_samples, name="samples", dictionary=dictionary,
+              compression='lzf', close=False)
+    # Save data to hdf5 file
+    for key, value in data_dict.iteritems():
+        f.create_dataset(key, data=value, compression='lzf')
 
+    # Close hdf5 file stream
+    f.close()
     """# Old saving
     # Save chains and other info
     print "Saving:", run_dir+"mcmc_samples.npz"

### 2016-10-07 map_EPOXI_params.py

@@ -1,0 +1,30 @@
+import numpy as np
+
+#--------------------------------------------------------------------
+# Parameters
+#--------------------------------------------------------------------
+
+REGULARIZATION = None
+#REGULARIZATION = 'GP'
+#REGULARIZATION = 'GP2'
+#REGULARIZATION = 'Tikhonov'
+
+N_TYPE  = 3
+N_SLICE = 13
+
+MONTH = 'June'
+
+NOISELEVEL = 0.01
+
+NUM_MCMC = 2000
+NUM_MCMC_BURNIN = 10000
+SEED_AMP = 0.1
+
+N_side_seed = 2
+N_SIDE  = 2*2**N_side_seed
+
+Pspin = 24.0
+OMEGA = ( 2. * np.pi / Pspin )
+
+def calculate_walkers(n_dim):
+    return 10*n_dim#**2

### 2016-10-07 mcmc_analysis.py

@@ -49,9 +49,9 @@ def plot_trace(samples, directory="", X_names=None, which=None):
 
     print "Plotting Trace..."
 
-    nwalkers = samples.attrs["nwalkers"]
-    nsteps = samples.attrs["nsteps"]
-    nparam = samples.attrs["nparam"]
+    nwalkers = samples.shape[0]
+    nsteps = samples.shape[1]
+    nparam = samples.shape[2]
 
     # Flatten chains for histogram
     print "Flattening chains for histogram (slow)..."
@@ -127,14 +127,13 @@ if __name__ == "__main__":
 
     # Extract info from HDF5 file
     samples=f["samples"]
-    data = samples.attrs["data"]
     N_TYPE = samples.attrs["N_TYPE"]
-    p0 = samples.attrs["p0"]
+    p0 = f["p0"]
     X_names = samples.attrs["X_names"]
     Y_names = samples.attrs["Y_names"]
-    nwalkers = samples.attrs[0]
-    nsteps = samples.attrs[1]
-    nparam = samples.attrs[2]
+    nwalkers = samples.shape[0]
+    nsteps = samples.shape[1]
+    nparam = samples.shape[2]
 
     """
     # Load MCMC samples from numpy archive

### 2016-10-07 mcmc_physical.py

@@ -11,6 +11,7 @@ import matplotlib as mpl
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
 from matplotlib import rc
+import h5py
 import pdb
 
 from colorpy import colormodels, ciexyz
@@ -223,52 +224,23 @@ if __name__ == "__main__":
 
     # Extract info from HDF5 file
     samples=f["samples"]
-    data = samples.attrs["data"]
+    assert iburn < samples.shape[1]
     N_TYPE = samples.attrs["N_TYPE"]
-    p0 = samples.attrs["p0"]
+    n_slice = samples.attrs["N_SLICE"]
+    p0 = f["p0"]
     X_names = samples.attrs["X_names"]
     Y_names = samples.attrs["Y_names"]
-    nwalkers = samples.attrs[0]
-    nsteps = samples.attrs[1]
-    nparam = samples.attrs[2]
-
-    """# old load
-    # Load MCMC samples from numpy archive
-    try:
-        temp = np.load(MCMC_DIR+"mcmc_samples.npz")
-    except IOError:
-        print "Run directory does not exist! Check -d argument."
-        sys.exit()
-
-    # Extract info from numpy archive
-    samples=temp["samples"]
-    data = temp["data"]
-    N_TYPE = temp["N_TYPE"]
-    p0 = temp["p0"]
-    X_names = temp["X_names"]
-    Y_names = temp["Y_names"]
-    n_slice = temp["N_SLICE"]
-
-    # MCMC dimensions
     nwalkers = samples.shape[0]
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
-    """
-
     # Unpack Data
-    Obs_ij = data[0]
+    Obs_ij = f["Obs_ij"]
     n_times = len(Obs_ij)
     n_band = len(Obs_ij[0])
-    N_REGPARAM = data[3]
-
+    N_REGPARAM = samples.attrs["N_REGPARAM"]
 
     # Compute slice longitude
     #slice_longitude = np.array([-180. + (360. / n_slice) * (i + 0.5) for i in range(n_slice)])
-
-    """
-    temp = np.load(MCMC_DIR+"mcmc_physical_samples.npz")
-    xsam = temp["xsam"]
-    """
 
     NAME_YSAM = "samples"
     NAME_XSAM = "physical_samples"
@@ -276,10 +248,10 @@ if __name__ == "__main__":
     # If the xsamples are already in the hdf5 file
     if NAME_XSAM in f.keys():
[…]

### 2016-10-07 fitlc_params.py
added hdf5 groups for more logical data storage; fixed tight_layout bug

@@ -4,7 +4,7 @@ import numpy as np
 # Parameters
 #--------------------------------------------------------------------
 
-NUM_MCMC = 10000
+NUM_MCMC = 100
 NUM_MCMC_BURNIN = 0
 SEED_AMP = 0.5
 

### 2016-10-07 main_fitlc_mcmc_EPOXI_NEW.py

@@ -9,6 +9,7 @@ import datetime
 import multiprocessing
 import os
 import pdb
+import h5py
 
 from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
     REGULARIZATION, N_TYPE, deg2rad, N_SIDE, INFILE, calculate_walkers
@@ -135,13 +136,29 @@ def run_initial_optimization(lnlike, data, guess, method="Nelder-Mead", run_dir=
     residuals = Obs_ij - np.dot( X_area_lk, X_albd_kj )
     print "residuals", residuals
 
+    # Create dictionaries of initial results to convert to hdf5
+    # datasets and attributes
+    init_dict_datasets = {
+        "best_fity" : best_fit,
+        "X_area_lk" : X_area_lk,
+        "X_albd_kj_T" : X_albd_kj_T,
+        "residuals" : residuals,
+        "best_fitx" : bestfit
+    }
+    init_dict_attrs = {
+        "best_lnprob" : lnprob_bestfit,
+        "best_BIC" : BIC
+    }
+
+    """
     # Save initialization run as npz
     print "Saving:", run_dir+"initial_minimize.npz"
     np.savez(run_dir+"initial_minimize.npz", data=data, best_fity=best_fit, \
         lnprob_bestfit=lnprob_bestfit, BIC=BIC, X_area_lk=X_area_lk, \
         X_albd_kj_T=X_albd_kj_T, residuals=residuals, best_fitx =bestfit)
+    """
 
-    return best_fit
+    return (init_dict_datasets, init_dict_attrs)#best_fit
 
 #---------------------------------------------------
 def run_emcee(lnlike, data, guess, N=500, run_dir="", seed_amp=0.01, *args):
@@ -243,7 +260,8 @@ if __name__ == "__main__":
 
     data = (Obs_ij, Obsnoise_ij, Kernel_il, N_REGPARAM, True, False)
 
-    best_fit = run_initial_optimization(lnprob, data, Y0_array, method="Nelder-Mead", run_dir=run_dir)
+    init_dict_datasets, init_dict_attrs = run_initial_optimization(lnprob, data, Y0_array, method="Nelder-Mead", run_dir=run_dir)
+    best_fit = init_dict_datasets["best_fity"]
 
     ########## Run MCMC ##########
 
@@ -295,35 +313,74 @@ if __name__ == "__main__":
 
[…]

### 2016-10-07 main_map_EPOXI_mcmc.py

@@ -10,6 +10,7 @@ import pdb
 import healpy as hp
 import emcee
 import corner
+import h5py
 
 import geometry
 import prior
@@ -235,10 +236,26 @@ if __name__ == "__main__":
             print 'overall_amp', best_fit[-2]
             print 'lambda _angular', best_fit[-1]* ( 180. / np.pi )
 
+    # Create dictionaries of initial results to convert to hdf5
+    # datasets and attributes
+    init_dict_datasets = {
+        "best_fity" : best_fit,
+        "X_area_lk" : X_area_lk,
+        "X_albd_kj_T" : X_albd_kj_T,
+        "residuals" : residuals,
+        "best_fitx" : bestfit
+    }
+    init_dict_attrs = {
+        "best_lnprob" : lnprob_bestfit,
+        "best_BIC" : BIC
+    }
+
+    """
     # Save initialization run as npz
     print "Saving:", run_dir+"initial_minimize.npz"
     np.savez(run_dir+"initial_minimize.npz", data=data, best_fity=best_fit, \
         lnprob_bestfit=lnprob_bestfit, X_area_lk=X_area_lk, X_albd_kj_T=X_albd_kj_T)
+    """
 
     ############ run MCMC ############
 
@@ -283,38 +300,78 @@ if __name__ == "__main__":
 
     ############ Save HDF5 File ############
 
-    # Specify save file
+    # Specify hdf5 save file and group names
     hfile = run_dir + "samurai_out.hdf5"
+    grp_init_name = "initial_optimization"
+    grp_mcmc_name = "mcmc"
+    grp_data_name = "data"
+    compression='lzf'
 
     # print
     print "Saving:", hfile
 
-    # Add small files to dictionary
-    dictionary = {
-        "Y_names" : Y_names,
-        "X_names" : X_names,
+    # dictionary for global run metadata
+    hfile_attrs = {
         "N_TYPE" : N_TYPE,
         "N_SLICE" : n_slice,
         "N_REGPARAM" : N_REGPARAM
     }
 
-    # Create dict for additional datasets (larger arrays)
-    data_dict = {
+    # Create dictionaries for mcmc data and metadata
+    mcmc_dict_datasets = {
+        "samples" : original_samples,
+        "p0" : p0
+    }
+    mcmc_dict_attrs = {
+        "Y_names" : Y_names,
+        "X_names" : X_names,
+    }
+
+    # Create dictionaries for observation data and metadata
+    data_dict_datasets = {
     "Obs_ij" : Obs_ij,
[…]

### 2016-10-07 mcmc_analysis.py

@@ -126,11 +126,11 @@ if __name__ == "__main__":
         sys.exit()
 
     # Extract info from HDF5 file
-    samples=f["samples"]
-    N_TYPE = samples.attrs["N_TYPE"]
-    p0 = f["p0"]
-    X_names = samples.attrs["X_names"]
-    Y_names = samples.attrs["Y_names"]
+    samples = f["mcmc/samples"]
+    N_TYPE = f.attrs["N_TYPE"]
+    p0 = f["mcmc/p0"]
+    X_names = f["mcmc"].attrs["X_names"]
+    Y_names = f["mcmc"].attrs["Y_names"]
     nwalkers = samples.shape[0]
     nsteps = samples.shape[1]
     nparam = samples.shape[2]

### 2016-10-07 mcmc_physical.py

@@ -88,9 +88,7 @@ def plot_median(med_alb, std_alb, med_area, std_area, directory=""):
     leg=ax0.legend(loc=0, fontsize=14)
     leg.get_frame().set_alpha(0.0)
 
-    fig.tight_layout()
-
-    fig.savefig(directory+"xmed_std.pdf")
+    fig.savefig(directory+"xmed_std.pdf", bbox_inches="tight")
 
 def plot_sampling(x, directory=""):
 
@@ -151,9 +149,7 @@ def plot_sampling(x, directory=""):
     leg=ax0.legend(loc=0, fontsize=16)
     leg.get_frame().set_alpha(0.0)
 
-    fig.tight_layout()
-
-    fig.savefig(directory+"xsamples.pdf")
+    fig.savefig(directory+"xsamples.pdf", bbox_inches="tight")
 
 def convolve_with_eye(wl, spectrum):
     # Construct 2d array for ColorPy
@@ -223,32 +219,31 @@ if __name__ == "__main__":
         sys.exit()
 
     # Extract info from HDF5 file
-    samples=f["samples"]
+    samples=f["mcmc/samples"]
     assert iburn < samples.shape[1]
-    N_TYPE = samples.attrs["N_TYPE"]
-    n_slice = samples.attrs["N_SLICE"]
-    p0 = f["p0"]
-    X_names = samples.attrs["X_names"]
-    Y_names = samples.attrs["Y_names"]
+    N_TYPE = f.attrs["N_TYPE"]
+    n_slice = f.attrs["N_SLICE"]
+    p0 = f["mcmc/p0"]
+    X_names = f["mcmc"].attrs["X_names"]
+    Y_names = f["mcmc"].attrs["Y_names"]
     nwalkers = samples.shape[0]
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
     # Unpack Data
-    Obs_ij = f["Obs_ij"]
+    Obs_ij = f["data/Obs_ij"]
     n_times = len(Obs_ij)
     n_band = len(Obs_ij[0])
-    N_REGPARAM = samples.attrs["N_REGPARAM"]
+    N_REGPARAM = f.attrs["N_REGPARAM"]
 
     # Compute slice longitude
     #slice_longitude = np.array([-180. + (360. / n_slice) * (i + 0.5) for i in range(n_slice)])
 
-    NAME_YSAM = "samples"
     NAME_XSAM = "physical_samples"
 
[…]

### 2016-10-07 mcmc_analysis.py
added physical posterior plotting with 1-sig percentiles

@@ -61,7 +61,8 @@ def plot_trace(samples, directory="", X_names=None, which=None):
     for i in range(nparam):
         if which is not None:
             i = which
-        print i
+        sys.stdout.write("\r{0}/{1}".format(i+1,nparam))
+        sys.stdout.flush()
         if X_names is None:
             pname = ""
         else:

### 2016-10-07 mcmc_physical.py

@@ -29,6 +29,8 @@ EPOXI = True
 # Specify burn-in index for corner plot
 DEFAULT_BURN_INDEX = 0
 
+DEFAULT_WHICH = None
+
 #---------------------------------------------------
 def decomposeX(x,n_band,n_slice,n_type):
     alb = x[0:n_band * n_type].reshape((n_type,n_band))
@@ -170,15 +172,67 @@ def plot_reg1(samples):
     ax0.set_xlabel("Slice #")
     ax1.set_ylabel("Albedo")
 
+def nsig_intervals(x, intvls=[0.16, 0.5, 0.84]):
+    # Compute median and n-sigma intervals
+    q_l, q_50, q_h = np.percentile(x, list(100.0 * np.array(intvls)))
+    q_m, q_p = q_50-q_l, q_h-q_50
+    return q_l, q_50, q_h, q_m, q_p
+
+def plot_posteriors(samples, directory="", X_names=None, which=None, nbins=50):
+
+    print "Plotting Posteriors..."
+
+    nsteps = samples.shape[0]
+    nparam = samples.shape[1]
+
+    # Loop over all parameters making posterior histograms
+    for i in range(nparam):
+        if which is not None:
+            i = which
+        sys.stdout.write("\r{0}/{1}".format(i+1,nparam))
+        sys.stdout.flush()
+        if X_names is None:
+            pname = ""
+        else:
+            pname = X_names[i]
+        fig = plt.figure(figsize=(10,8))
+        gs = gridspec.GridSpec(1,1)
+        ax0 = plt.subplot(gs[0])
+        ax0.set_xlabel(pname)
+        ax0.set_ylabel("Relative Probability")
+        bins = np.linspace(np.min(samples[:,i]), np.max(samples[:,i]), nbins, endpoint=True)
+        h = ax0.hist(samples[:,i], bins, color="k", alpha=0.5)
+        ax0.set_yticks([])
+        plt.setp(ax0.get_xticklabels(), fontsize=18, rotation=45)
+        plt.setp(ax0.get_yticklabels(), fontsize=18, rotation=45)
+        q_l, q_50, q_h, q_m, q_p = nsig_intervals(samples[:,i], intvls=[0.16, 0.5, 0.84])
+        # Format title
+        title_fmt = ".3f"
+        fmt = "{{0:{0}}}".format(title_fmt).format
+        title = r"${{{0}}}_{{-{1}}}^{{+{2}}}$"
[…]

### 2016-10-07 main_fitlc_mcmc_EPOXI_NEW.py
minor indentation fix

@@ -342,9 +342,9 @@ if __name__ == "__main__":
 
     # Create dictionaries for observation data and metadata
     data_dict_datasets = {
-    "Obs_ij" : Obs_ij,
-    "Obsnoise_ij" : Obsnoise_ij,
-    "Kernel_il" : Kernel_il,
+        "Obs_ij" : Obs_ij,
+        "Obsnoise_ij" : Obsnoise_ij,
+        "Kernel_il" : Kernel_il,
     }
     data_dict_attrs = {
         "datafile" : INFILE

### 2016-10-08 mcmc_physical.py
plotting quantiles now with 'area-alb' flag

@@ -92,6 +92,83 @@ def plot_median(med_alb, std_alb, med_area, std_area, directory=""):
 
     fig.savefig(directory+"xmed_std.pdf", bbox_inches="tight")
 
+def plot_area_alb(samples, directory="", savetxt=True, intvls=[0.16, 0.5, 0.84]):
+
+    print "Plotting Area & Albedo..."
+
+    nparam = samples.shape[1]
+
+    # Compute grid of quantiles
+    # q_l, q_50, q_h, q_m, q_p
+    quantiles = np.array([nsig_intervals(samples[:,i], intvls=intvls)
+        for i in range(nparam)])
+
+    # Construct 2d arrays from 1d array
+    alb_med, area_med = decomposeX(quantiles[:,1], n_band, n_slice, N_TYPE)
+    alb_m, area_m = decomposeX(quantiles[:,3], n_band, n_slice, N_TYPE)
+    alb_p, area_p = decomposeX(quantiles[:,4], n_band, n_slice, N_TYPE)
+
+    # Make plot
+    fig = plt.figure(figsize=(16,8))
+    gs = gridspec.GridSpec(1,2)
+    ax0 = plt.subplot(gs[0])
+    ax1 = plt.subplot(gs[1])
+    ax0.set_ylabel("Area Fraction")
+    ax0.set_xlabel("Slice #")
+    ax1.set_ylabel("Albedo")
+
+    xarea = np.arange(n_slice)
+    xalb = np.arange(n_band)
+
+    if n_slice == n_times:
+        ax0.set_xlabel("Time [hrs]")
+        ax0.set_xlim([np.min(xarea)-0.05, np.max(xarea)+0.05])
+    else:
+        ax0.set_xlabel("Slice Longitude [deg]")
+        xarea = np.array([-180. + (360. / n_slice) * (i + 0.5) for i in range(n_slice)])
+        ax0.set_xlim([-185, 185])
+        ax0.set_xticks([-180, -90, 0, 90, 180])
+
+    if EPOXI:
+        epoxi_bands = np.loadtxt("data/EPOXI_band")
+        wl = epoxi_bands[:,1]
+        xalb = wl
+        ax1.set_xlabel("Wavelength [nm]")
+        ax1.set_xlim([300,1000])
+    else:
+        ax1.set_xlabel("Band")
+        ax1.set_xlim([np.min(xalb)-0.05, np.max(xalb)+0.05])
+
+    if EYECOLORS:
+        epoxi_bands = np.loadtxt("data/EPOXI_band")
[…]

### 2016-10-08 mcmc_physical.py
added run* function so analysis can be called from other python scripts

@@ -24,7 +24,7 @@ mpl.rcParams['font.size'] = 25.0
 
 DIR = "mcmc_output/"
 EYECOLORS = False
-EPOXI = True
+DEFAULT_EPOXI = True
 
 # Specify burn-in index for corner plot
 DEFAULT_BURN_INDEX = 0
@@ -37,7 +37,8 @@ def decomposeX(x,n_band,n_slice,n_type):
     area = x[n_band * n_type:].reshape((n_slice , n_type))
     return alb, area
 
-def plot_median(med_alb, std_alb, med_area, std_area, directory=""):
+def plot_median(med_alb, std_alb, med_area, std_area, n_all, directory="",
+                epoxi=DEFAULT_EPOXI, eyecolors=False):
 
     print "Plotting Median, Std..."
 
@@ -49,19 +50,19 @@ def plot_median(med_alb, std_alb, med_area, std_area, directory=""):
     ax0.set_xlabel("Slice #")
     ax1.set_ylabel("Albedo")
 
-    xarea = np.arange(n_slice)
-    xalb = np.arange(n_band)
+    xarea = np.arange(n_all["nslice"])
+    xalb = np.arange(n_all["nband"])
 
-    if n_slice == n_times:
+    if n_all["nslice"] == n_all["ntimes"]:
         ax0.set_xlabel("Time [hrs]")
         ax0.set_xlim([np.min(xarea)-0.05, np.max(xarea)+0.05])
     else:
         ax0.set_xlabel("Slice Longitude [deg]")
-        xarea = np.array([-180. + (360. / n_slice) * (i + 0.5) for i in range(n_slice)])
+        xarea = np.array([-180. + (360. / n_all["nslice"]) * (i + 0.5) for i in range(n_all["nslice"])])
         ax0.set_xlim([-185, 185])
         ax0.set_xticks([-180, -90, 0, 90, 180])
 
-    if EPOXI:
+    if epoxi:
         epoxi_bands = np.loadtxt("data/EPOXI_band")
         wl = epoxi_bands[:,1]
         xalb = wl
@@ -71,14 +72,14 @@ def plot_median(med_alb, std_alb, med_area, std_area, directory=""):
         ax1.set_xlabel("Band")
         ax1.set_xlim([np.min(xalb)-0.05, np.max(xalb)+0.05])
 
-    if EYECOLORS:
+    if eyecolors:
[…]

### 2016-10-08 mcmc_analysis.py
added run* function to mcmc_analysis.py; changed 'which' keyword arg to '-w'

@@ -92,31 +92,13 @@ def plot_trace(samples, directory="", X_names=None, which=None):
     return
 
 #===================================================
-if __name__ == "__main__":
 
-    # Read command line args
-    myopts, args = getopt.getopt(sys.argv[1:],"d:b:n:")
-    run = ""
-    iburn = DEFAULT_BURN_INDEX
-    which = DEFAULT_WHICH
-    for o, a in myopts:
-        # o == option
-        # a == argument passed to the o
-        if o == '-d':
-            # Get MCMC directory timestamp name
-            run=a
-        elif o == "-b":
-            # Get burn in index
-            iburn = int(a)
-        elif o == "-n":
-            # Get which index
-            which = int(a)
-        else:
-            pass
+def run_mcmc_analysis(run, directory=DIR, iburn=DEFAULT_BURN_INDEX, which=DEFAULT_WHICH,
+                      run_trace=False, run_corner=False):
 
     print "Burn-in index:", iburn
 
-    MCMC_DIR = DIR + run + "/"
+    MCMC_DIR = directory + run + "/"
 
     # Load MCMC samples
     try:
@@ -136,28 +118,7 @@ if __name__ == "__main__":
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
 
-    """
-    # Load MCMC samples from numpy archive
-    try:
-        temp = np.load(MCMC_DIR+"mcmc_samples.npz")
-    except IOError:
-        print "Run directory does not exist! Check -d argument."
-        sys.exit()
-
-    # Extract info from numpy archive
-    samples=temp["samples"]
-    data = temp["data"]
-    N_TYPE = temp["N_TYPE"]
-    p0 = temp["p0"]
-    X_names = temp["X_names"]
-    Y_names = temp["Y_names"]
-
-    nwalkers = samples.shape[0]
-    nsteps = samples.shape[1]
-    nparam = samples.shape[2]
-    """
-
-    if "trace" in str(sys.argv):
+    if run_trace:
 
         # Create directory for trace plots
         trace_dir = MCMC_DIR+"trace_plots/"
@@ -170,7 +131,7 @@ if __name__ == "__main__":
         # Make trace plots
         plot_trace(samples, X_names=Y_names, directory=trace_dir, which=which)
 
-    if "corner" in str(sys.argv):
+    if run_corner:
 
         # Flatten chains
         print "Flattening chains..."
@@ -183,3 +144,42 @@ if __name__ == "__main__":
 
     # Close HDF5 file stream
     f.close()
+
[…]

### 2016-10-08 mcmc_physical.py

@@ -300,13 +300,13 @@ def plot_posteriors(samples, directory="", X_names=None, which=None, nbins=50):
 
 #===================================================
 
-def run_physical_mcmc_analysis(run, run_sample=False, run_median=False, run_corner=False,
+def run_physical_mcmc_analysis(run, directory=DIR, run_sample=False, run_median=False, run_corner=False,
                            run_posterior=False, run_area_alb=False, iburn=DEFAULT_BURN_INDEX,
                            which=DEFAULT_WHICH, eyecolors=False, epoxi=DEFAULT_EPOXI):
 
     print "Burn-in index:", iburn
 
-    MCMC_DIR = DIR + run + "/"
+    MCMC_DIR = directory + run + "/"
 
     # Load MCMC samples
     try:
@@ -499,7 +499,7 @@ def run_physical_mcmc_analysis(run, run_sample=False, run_median=False, run_corn
 if __name__ == "__main__":
 
     ###### Read command line args ######
-    myopts, args = getopt.getopt(sys.argv[1:],"d:b:n:")
+    myopts, args = getopt.getopt(sys.argv[1:],"d:b:w:")
     run = ""
     iburn = DEFAULT_BURN_INDEX
     which = DEFAULT_WHICH
@@ -512,7 +512,7 @@ if __name__ == "__main__":
         elif o == "-b":
             # Get burn in index
             iburn = int(a)
-        elif o == "-n":
+        elif o == "-w":
             # Get which index
             which = int(a)
         else:

### 2016-10-08 mcmc_physical.py
widened area-albedo figure size

@@ -111,7 +111,7 @@ def plot_area_alb(samples, n_all, directory="", savetxt=True, intvls=[0.16, 0.5,
     alb_p, area_p = decomposeX(quantiles[:,4], n_all["nband"], n_all["nslice"], n_all["ntype"])
 
     # Make plot
-    fig = plt.figure(figsize=(16,8))
+    fig = plt.figure(figsize=(18,8))
     gs = gridspec.GridSpec(1,2)
     ax0 = plt.subplot(gs[0])
     ax1 = plt.subplot(gs[1])

### 2016-10-09 mcmc_analysis.py
fig.subplots_adjust(wspace=0)

@@ -16,7 +16,7 @@ import h5py
 
 
 # Specify directory of run to analyze
-MCMC_DIR = "mcmc_output/2016-07-13--11-59/"
+MCMC_DIR = ""
 
 DIR = "mcmc_output/"
 
@@ -53,9 +53,10 @@ def plot_trace(samples, directory="", X_names=None, which=None):
     nsteps = samples.shape[1]
     nparam = samples.shape[2]
 
-    # Flatten chains for histogram
+    """# Flatten chains (for histogram)
     print "Flattening chains for histogram (slow)..."
     samples_flat = samples[:, :, :].reshape((-1, nparam))
+    """
 
     # Loop over all parameters making trace plots
     for i in range(nparam):
@@ -68,23 +69,25 @@ def plot_trace(samples, directory="", X_names=None, which=None):
         else:
             pname = X_names[i]
         fig = plt.figure(figsize=(13,5))
-        gs = gridspec.GridSpec(1,2, width_ratios=(1,.3))
+        gs = gridspec.GridSpec(1,1)
         ax0 = plt.subplot(gs[0])
-        ax0.plot(samples[:,:,i].T, lw=0.5)
+        ax0.plot(samples[:,:,i].T, lw=0.5, alpha=0.5)
         ax0.set_xlabel("Iteration")
         ax0.set_ylabel(pname+" Value")
+        """# Add histogram on right
         ax1 = plt.subplot(gs[1], sharey=ax0)
         bins = np.linspace(np.min(samples_flat[:,i]), np.max(samples_flat[:,i]), 25, endpoint=True)
         h = ax1.hist(samples_flat[:,i], bins, orientation='horizontal', color="k", alpha=0.5)
         ax1.set_xticks([])
         ax1.yaxis.tick_right()
         ax1.yaxis.set_label_position("right")
-        plt.setp(ax0.get_xticklabels(), fontsize=18, rotation=45)
-        plt.setp(ax0.get_yticklabels(), fontsize=18, rotation=45)
         plt.setp(ax1.get_xticklabels(), fontsize=18, rotation=45)
         plt.setp(ax1.get_yticklabels(), fontsize=18, rotation=45)
+        """
+        plt.setp(ax0.get_xticklabels(), fontsize=18, rotation=45)
+        plt.setp(ax0.get_yticklabels(), fontsize=18, rotation=45)
         fig.subplots_adjust(wspace=0)
[…]

### 2016-10-09 mcmc_physical.py

@@ -91,7 +91,7 @@ def plot_median(med_alb, std_alb, med_area, std_area, n_all, directory="",
     leg=ax0.legend(loc=0, fontsize=14)
     leg.get_frame().set_alpha(0.0)
 
-    fig.savefig(directory+"xmed_std.pdf", bbox_inches="tight")
+    fig.savefig(os.path.join(directory,"xmed_std.pdf"), bbox_inches="tight")
 
 def plot_area_alb(samples, n_all, directory="", savetxt=True, intvls=[0.16, 0.5, 0.84],
                   epoxi=DEFAULT_EPOXI, eyecolors=False):
@@ -161,7 +161,7 @@ def plot_area_alb(samples, n_all, directory="", savetxt=True, intvls=[0.16, 0.5,
     leg.get_frame().set_alpha(0.0)
 
     # Save the plot
-    fig.savefig(directory+"area-alb.pdf", bbox_inches="tight")
+    fig.savefig(os.path.join(directory, "area-alb.pdf"), bbox_inches="tight")
     print "Saved:", "area-alb.pdf"
 
     return quantiles
@@ -291,7 +291,7 @@ def plot_posteriors(samples, directory="", X_names=None, which=None, nbins=50):
         ax0.axvline(q_l, color="k", lw=2.0, ls="--")
         ax0.axvline(q_h, color="k", lw=2.0, ls="--")
         # Save
-        fig.savefig(directory+"posterior"+str(i)+".png", bbox_inches="tight")
+        fig.savefig(os.path.join(directory, "posterior"+str(i)+".png"), bbox_inches="tight")
         fig.clear()
         plt.close()
         if which is not None:
@@ -306,12 +306,13 @@ def run_physical_mcmc_analysis(run, directory=DIR, run_sample=False, run_median=
 
     print "Burn-in index:", iburn
 
-    MCMC_DIR = directory + run + "/"
+    MCMC_DIR = os.path.join(directory, run)
 
     # Load MCMC samples
     try:
         # Open the file stream
-        f = h5py.File(MCMC_DIR+"samurai_out.hdf5", 'r+')
+        hpath = os.path.join(MCMC_DIR, "samurai_out.hdf5")
+        f = h5py.File(hpath, 'r+')
     except IOError:
         print "Run directory does not exist! Check -d argument."
         sys.exit()
@@ -435,8 +436,8 @@ def run_physical_mcmc_analysis(run, directory=DIR, run_sample=False, run_median=
[…]

### 2016-10-09 main_fitlc_mcmc_EPOXI_NEW.py
added os.path.join where appropriate

@@ -12,7 +12,7 @@ import pdb
 import h5py
 
 from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
-    REGULARIZATION, N_TYPE, deg2rad, N_SIDE, INFILE, calculate_walkers
+    REGULARIZATION, N_TYPE, deg2rad, N_SIDE, INFILE, calculate_walkers, HDF5_COMPRESSION
 
 import prior
 import reparameterize
@@ -134,7 +134,7 @@ def run_initial_optimization(lnlike, data, guess, method="Nelder-Mead", run_dir=
 
     # Calculate residuals
     residuals = Obs_ij - np.dot( X_area_lk, X_albd_kj )
-    print "residuals", residuals
+    #print "residuals", residuals
 
     # Create dictionaries of initial results to convert to hdf5
     # datasets and attributes
@@ -142,7 +142,6 @@ def run_initial_optimization(lnlike, data, guess, method="Nelder-Mead", run_dir=
         "best_fity" : best_fit,
         "X_area_lk" : X_area_lk,
         "X_albd_kj_T" : X_albd_kj_T,
-        "residuals" : residuals,
         "best_fitx" : bestfit
     }
     init_dict_attrs = {
@@ -158,34 +157,7 @@ def run_initial_optimization(lnlike, data, guess, method="Nelder-Mead", run_dir=
         X_albd_kj_T=X_albd_kj_T, residuals=residuals, best_fitx =bestfit)
     """
 
-    return (init_dict_datasets, init_dict_attrs)#best_fit
-
-#---------------------------------------------------
-def run_emcee(lnlike, data, guess, N=500, run_dir="", seed_amp=0.01, *args):
-
-    print "MCMC until burn-in..."
-
-    # Number of dimensions is number of free parameters
-    n_dim = len(guess)
-    # Number of walkers
-    n_walkers = 2*n_dim**2
-
-    # Initialize emcee EnsembleSampler object
-    sampler = emcee.EnsembleSampler(n_walkers, n_dim, lnprob, args=data, threads=NCPU)
-
-    # Set starting guesses as gaussian noise ontop of intial optimized solution
-    # note: consider using emcee.utils.sample_ball(p0, std) (std: axis-aligned standard deviation.)
-    #       to produce a ball of walkers around an initial parameter value.
[…]

### 2016-10-09 main_map_EPOXI_mcmc.py

@@ -23,7 +23,7 @@ from map_utils import generate_tex_names, save2hdf5
 
 from map_EPOXI_params import N_TYPE, N_SLICE, MONTH, NOISELEVEL, \
     NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, N_SIDE, OMEGA, REGULARIZATION, \
-    calculate_walkers
+    calculate_walkers, HDF5_COMPRESSION
 
 NCPU = multiprocessing.cpu_count()
 
@@ -161,16 +161,16 @@ if __name__ == "__main__":
 
     # Create directory for this run
     startstr = now.strftime("%Y-%m-%d--%H-%M")
-    run_dir = "mcmc_output/" + startstr + "/"
+    run_dir = os.path.join("mcmc_output", startstr)
     os.mkdir(run_dir)
     print "Created directory:", run_dir
 
     # Save THIS file and the param file for reproducibility!
     thisfile = os.path.basename(__file__)
     paramfile = "map_EPOXI_params.py"
-    newfile = run_dir + thisfile
+    newfile = os.path.join(run_dir, thisfile)
     commandString1 = "cp " + thisfile + " " + newfile
-    commandString2 = "cp "+paramfile+" " + run_dir+paramfile
+    commandString2 = "cp "+paramfile+" " + os.path.join(run_dir,paramfile)
     os.system(commandString1)
     os.system(commandString2)
     print "Saved :", thisfile, " &", paramfile
@@ -236,13 +236,15 @@ if __name__ == "__main__":
             print 'overall_amp', best_fit[-2]
             print 'lambda _angular', best_fit[-1]* ( 180. / np.pi )
 
+    # Flatten best-fitting physical parameters
+    bestfit = np.r_[ X_albd_kj.flatten(), X_area_lk.T.flatten() ]
+
     # Create dictionaries of initial results to convert to hdf5
     # datasets and attributes
     init_dict_datasets = {
         "best_fity" : best_fit,
         "X_area_lk" : X_area_lk,
         "X_albd_kj_T" : X_albd_kj_T,
-        "residuals" : residuals,
         "best_fitx" : bestfit
     }
     init_dict_attrs = {
@@ -305,7 +307,7 @@ if __name__ == "__main__":
     grp_init_name = "initial_optimization"
     grp_mcmc_name = "mcmc"
     grp_data_name = "data"
-    compression='lzf'
+    compression = HDF5_COMPRESSION
 
     # print
     print "Saving:", hfile

### 2016-10-09 main_fitlc_mcmc_EPOXI_NEW.py
using emcee blobs to return and save model_ij evaluations

@@ -43,30 +43,32 @@ if REGULARIZATION is not None:
 else :
     N_REGPARAM = 0
 
-
 #---------------------------------------------------
 def lnprob(Y_array, *args):
     """
     Misfit-function to be minimized
     """
 
+    # Unpack args
     Obs_ij, Obsnoise_ij, Kernel_il, N_REGPARAM, flip, verbose  = args
     n_slice = len(Obs_ij)
     n_band = len(Obs_ij[0])
 
-    # parameter conversion
+    # Parameter conversion
     if (N_REGPARAM > 0):
         X_albd_kj, X_area_lk = reparameterize.transform_Y2X(Y_array[:-1*N_REGPARAM], N_TYPE, n_band, n_slice )
     else:
         X_albd_kj, X_area_lk = reparameterize.transform_Y2X(Y_array, N_TYPE, n_band, n_slice )
 
-    # making matrix...
+    # Model
     Model_ij = np.dot(Kernel_il, np.dot(X_area_lk, X_albd_kj))
+
+    # Chi-squared statistic
     Diff_ij = ( Obs_ij - Model_ij ) / Obsnoise_ij
     Chi2_i  = np.diag(np.dot( Diff_ij, Diff_ij.T ))
     chi2    = np.sum(Chi2_i)
 
-    # flat prior for albedo
+    # Flat prior for albedo
     Y_albd_kj = Y_array[0:N_TYPE*n_band].reshape([N_TYPE, n_band])
     ln_prior_albd = prior.get_ln_prior_albd( Y_albd_kj )
 
@@ -101,7 +103,7 @@ def lnprob(Y_array, *args):
     if flip :
         return -1. * answer
     else :
-         return answer
+         return answer, Model_ij
 
 #---------------------------------------------------
 def run_initial_optimization(lnlike, data, guess, method="Nelder-Mead", run_dir=""):
@@ -237,9 +239,6 @@ if __name__ == "__main__":
 
     ########## Run MCMC ##########
 
-    # Data tuple to pass to emcee
-    data = (Obs_ij, Obsnoise_ij, Kernel_il, N_REGPARAM, False, False)
-
     # Number of dimensions is number of free parameters
     n_dim = len(Y0_array)
     # Number of walkers
@@ -281,6 +280,11 @@ if __name__ == "__main__":
     # Get emcee chain samples
     original_samples = sampler.chain
 
+    # Get model evaluations
+    blobs = sampler.blobs
[…]

### 2016-10-09 main_map_EPOXI_mcmc.py

@@ -148,7 +148,7 @@ def lnprob(Y_array, *args):
     if flip :
         return -1. * answer
     else :
-         return answer
+         return answer, Model_ij
 
 
 
@@ -300,6 +300,11 @@ if __name__ == "__main__":
     # Extract chain from sampler
     original_samples = sampler.chain
 
+    # Get model evaluations
+    blobs = sampler.blobs
+    shape = (len(blobs), len(blobs[0]), len(blobs[0][0]), len(blobs[0][0][0]))
+    model_ij = np.reshape(blobs, shape)
+
     ############ Save HDF5 File ############
 
     # Specify hdf5 save file and group names
@@ -322,6 +327,7 @@ if __name__ == "__main__":
     # Create dictionaries for mcmc data and metadata
     mcmc_dict_datasets = {
         "samples" : original_samples,
+        "model_ij" : model_ij,
         "p0" : p0
     }
     mcmc_dict_attrs = {

### 2016-10-12 fitlc_params.py
prepared longitudinal n_slice mapping code for simple IGBP tests; fixed ylabel on area-alb plot when using each modeling approach

@@ -9,9 +9,9 @@ NUM_MCMC_BURNIN = 0
 SEED_AMP = 0.5
 
 #REGULARIZATION = None
-#REGULARIZATION = 'GP'
+REGULARIZATION = 'GP'
 #REGULARIZATION = 'GP2'
-REGULARIZATION = 'Tikhonov'
+#REGULARIZATION = 'Tikhonov'
 
 SIGMA_Y  = 3.0
 NOISELEVEL = 0.01
@@ -24,7 +24,7 @@ N_TYPE  = 3
 
 deg2rad = np.pi/180.
 
-N_SIDE   = 32
+N_SIDE   = 128
 #INFILE = "data/raddata_12_norm"
 ##INFILE = "data/raddata_2_norm"
 #INFILE = "mockdata/mock_simple_1_data"

### 2016-10-12 main_map_EPOXI_mcmc.py

@@ -69,6 +69,14 @@ elif ( MONTH == 'test' ):
     INFILE = "mockdata/mock_simple_3types_JuneKernel_scattered0.01_data_with_noise"
     Time_i = np.arange(25)*1.
 
+elif ( MONTH == 'simpleIGBP' ):
+    LON_S = 90.0
+    LAT_S = 0.0
+    LON_O = 0.0
+    LAT_O = 0.0
+    INFILE = 'mockdata/simpleIGBP_quadrature_lc'
+    Time_i = np.arange(7)/7.*24.
+
 else :
     print 'ERROR: Invalid MONTH'
     sys.exit()

### 2016-10-12 map_EPOXI_params.py

@@ -10,15 +10,15 @@ REGULARIZATION = None
 #REGULARIZATION = 'Tikhonov'
 
 N_TYPE  = 3
-N_SLICE = 13
+N_SLICE = 7
 
 MONTH = 'June'
 
 NOISELEVEL = 0.01
 
-NUM_MCMC = 100
+NUM_MCMC = 10000
 NUM_MCMC_BURNIN = 0
-SEED_AMP = 0.1
+SEED_AMP = 0.5
 
 N_side_seed = 2
 N_SIDE  = 2*2**N_side_seed

### 2016-10-12 mcmc_physical.py

@@ -151,7 +151,6 @@ def plot_area_alb(samples, n_all, directory="", savetxt=True, intvls=[0.16, 0.5,
     gs = gridspec.GridSpec(1,2)
     ax0 = plt.subplot(gs[0])
     ax1 = plt.subplot(gs[1])
-    ax0.set_ylabel("Area Fraction")
     ax0.set_xlabel("Slice #")
     ax1.set_ylabel("Albedo")
 
@@ -160,9 +159,11 @@ def plot_area_alb(samples, n_all, directory="", savetxt=True, intvls=[0.16, 0.5,
 
     if n_all["nslice"] == n_all["ntimes"]:
         ax0.set_xlabel("Time [hrs]")
+        ax0.set_ylabel("Contribution Factor")
         ax0.set_xlim([np.min(xarea)-0.05, np.max(xarea)+0.05])
     else:
         ax0.set_xlabel("Slice Longitude [deg]")
+        ax0.set_ylabel("Area Fraction")
         xarea = np.array([-180. + (360. / n_all["nslice"]) * (i + 0.5) for i in range(n_all["nslice"])])
         ax0.set_xlim([-185, 185])
         ax0.set_xticks([-180, -90, 0, 90, 180])

### 2016-10-13 map_EPOXI_params.py
minor update from laptop runs

@@ -4,15 +4,15 @@ import numpy as np
 # Parameters
 #--------------------------------------------------------------------
 
-REGULARIZATION = None
-#REGULARIZATION = 'GP'
+#REGULARIZATION = None
+REGULARIZATION = 'GP'
 #REGULARIZATION = 'GP2'
 #REGULARIZATION = 'Tikhonov'
 
 N_TYPE  = 3
-N_SLICE = 7
+N_SLICE = 9
 
-MONTH = 'June'
+MONTH = 'simpleIGBP'
 
 NOISELEVEL = 0.01
 
@@ -20,7 +20,7 @@ NUM_MCMC = 10000
 NUM_MCMC_BURNIN = 0
 SEED_AMP = 0.5
 
-N_side_seed = 2
+N_side_seed = 4
 N_SIDE  = 2*2**N_side_seed
 
 Pspin = 24.0

### 2016-10-14 map_EPOXI_params.py
params

@@ -10,7 +10,7 @@ REGULARIZATION = 'GP'
 #REGULARIZATION = 'Tikhonov'
 
 N_TYPE  = 3
-N_SLICE = 9
+N_SLICE = 13
 
 MONTH = 'simpleIGBP'
 
@@ -20,7 +20,7 @@ NUM_MCMC = 10000
 NUM_MCMC_BURNIN = 0
 SEED_AMP = 0.5
 
-N_side_seed = 4
+N_side_seed = 5
 N_SIDE  = 2*2**N_side_seed
 
 Pspin = 24.0

### 2016-10-14 paper/main.tex
add a figure for PCs
figure of the principal component plane is updated

@@
 This is essentially same as the situation described by equation (\ref{eq:d_f_ast_s}).
-In other words, any set of vertices in $J$-dimensional space that can enclose the observed data, $\vec d_i$, if any, can be the solutions for equation (\ref{eq:d_f_ast_s}), as long as all of the element in $x_{kj}$ satisfy $0<x_{kj}<1$.
+
+In other words, any set of vertices in $J$-dimensional space that can enclose all of the observed data, $\vec d_i$ can be the solutions for equation (\ref{eq:d_f_ast_s}), as long as all of the element in $x_{kj}$ satisfy $0<x_{kj}<1$.
+The condition $0<x_{kj}<1$ generally constrains the outer boundary of the possible locations for the vertices. 
+Therefore, the ``answer'' vertices allowed by the observations are somewhere outside the polygon that tightly encloses the observed data and inside the outer boundary defined by the condition $0<x_{kj}<1$ (see \S\ref{ss:shrinkwrap} below).
+
+Note that in an exceptional case where the apparent covering fractions of all of the surface type come close to unity to different epochs, the allowed region for the vertices would be narrow, i.e., better estimation can be expected.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Prior: Gaussian Processes}
+\label{ss:gp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{This is just a quick draft and will need to be updated significantly.}
+
+As seen above, the solution is highly degenerate, and in general we cannot reduce to a unique solution. 
+Therefore, we may want to give a prior in estimating the area fractions. 
+What kind of assumptions can we make?
+
+In general, the large time/longitude variations in apparent area fractions corresponds to spectrally similar surface types, because such solution correspond to the proximity of the inner boundary in the $J$-dimensional space discussed above.
+On the contrary, the spectrally separated surface types correspond to the small time/longitude variations in the apparent area fractions. 
+In the real world, we might expect that the latter is more likely, i.e., covering area fraction of any surface type would not change significantly along the longitude (or in time). 
+This would be a reasonable assumption for the estimation of $\{s, \fast \}$, since the illuminated and visible area is usually broad and tend to change the averaged area fraction of each surface type only gently.
+Although there is no physical proof for this assumption...
+
+The assumption of the smoothness and the small variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}.
+
+Essentially, the probability of the
 
@@
 Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$ and $f$ always satisfy our constraints.
+
+\newpage
 
@@
     \begin{center}
-\includegraphics[width=\hsize]{PCA_projected.pdf}
+\includegraphics[width=\hsize]{PCA_V_jn.pdf}
+    \end{center}
+    \caption{Principal Components. }
+\label{fig:PCs}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bpth]
+    \begin{center}
+%\includegraphics[width=\hsize]{PCA_projected.pdf}
+\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
     \end{center}
@@
 \label{fig:shrinkwrap}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-17 paper/main.tex
figure size reduced
text reorganized, figure added

@@
 \usepackage{url}
+\usepackage{here}
 \usepackage{hyperref}
@@
 \def\memoYF#1{\color{red}[NOTE: {\bf #1}]\color{black}}
+
+%%% http://www.oceanwave.jp/index.php?float%B4%C4%B6%AD(figure%2Ftable)%A4%CE%BD%D0%CE%CF%B0%CC%C3%D6%A4%F2%A5%B3%A5%F3%A5%C8%A5%ED%A1%BC%A5%EB
 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-By definition, the area fraction $f$ and reflectance spectra $s$ are subject to the following conditions:
+By definition, the area fraction $\fast $ and reflectance spectra $s$ are subject to the following conditions:
 %%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[bh]
+\begin{table}[tbh]
 \caption{Indexes}
@@
 where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type in the $l$-th longitudinal slice. 
-The approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little in the $l$-th slice for all $k$ and $l$. 
+Strictly speaking, the approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little across the $l$-th slice for all $k$ and $l$. 
 In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fit data with $f$ or with $f^{\ast}$?}
+\subsection{Fit data with $\fast $ or with $f$ ?}
 \label{ss:degeneracy}
@@
 
-We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ f^{\ast }, s \}$. 
+We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ \fast, s \}$. 
 %
@@
 %
-If $L=I$, in general there is a one-to-one relationship between $f^{\ast}_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
+If $L=I$, in general there is a one-to-one relationship between $\fast_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
 In this case, clearly, equations (\ref{eq:cond_f_ast}) and (\ref{eq:cond_f}) are equivalent, given $W_{il}>0$ (for any $i$ and $j$) and $\sum _l W_{il} = 1$. 
@@
 If $L<I$, the matrix $W$ works as a low-pass filter \citep{Cowan2013}. 
-In this case, the inverse problem described by equation (\ref{eq:Wf}), $f^{\ast }=Wf$, is an overdetermined system, and one must to find the solution for $f$ by some means (e.g.
-the least squares method), and the resultant $f$ may not automatically satisfy the condition listed by eqution (\ref{eq:cond_f}).
+In this case, the inverse problem described by equation (\ref{eq:Wf}), $\fast=Wf$, is an overdetermined system, and one must to find the solution for $f$ by some means (e.g.
+the least squares method), and the resultant $f$ may not automatically satisfy the condition listed by equation (\ref{eq:cond_f}).
+
 However, this is because of the design of the problem and the assumed lowered resolution.
@@
 \memoYF{\citet{Cowan2013} found a more reasonable answer for $s$ when they fitted with $\{ f, s \}$, but I think this is a coincidence. }
+
+\newpage
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Prior: Gaussian Processes}
-\label{ss:gp}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{This is just a quick draft and will need to be updated significantly.}
-
-As seen above, the solution is highly degenerate, and in general we cannot reduce to a unique solution. 
-Therefore, we may want to give a prior in estimating the area fractions. 
-What kind of assumptions can we make?
-
-In general, the large time/longitude variations in apparent area fractions corresponds to spectrally similar surface types, because such solution correspond to the proximity of the inner boundary in the $J$-dimensional space discussed above.
-On the contrary, the spectrally separated surface types correspond to the small time/longitude variations in the apparent area fractions. 
-In the real world, we might expect that the latter is more likely, i.e., covering area fraction of any surface type would not change significantly along the longitude (or in time). 
-This would be a reasonable assumption for the estimation of $\{s, \fast \}$, since the illuminated and visible area is usually broad and tend to change the averaged area fraction of each surface type only gently.
-Although there is no physical proof for this assumption...
-
-The assumption of the smoothness and the small variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}.
-
-Essentially, the probability of the
+\newpage
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bayesian Formulation}
+\subsection{Bayesian Formulation ?}
 \label{ss:regularization}
@@
 
+Assuming the observational noise is distributed as Gaussian, 
 %%%
 \begin{eqnarray}
-Posterior = \prod\limits_{i,j} \frac{1}{\sqrt{2\pi }\sigma_{ij}} &&  \exp \left[ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right] \notag \\
-&& \times \; \mathcal{P} (\{f_{l,k}\}) \cdot \mathcal{P}(\{s_{l,k}\}) 
+&&Posterior 
+\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
+&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
 \end{eqnarray}
@@
 t_{kj} = \displaystyle \ln \left[ \frac{ s_{kj} }{1 - s_{kj} } \right]  \;\;\; & \mbox{for any $k$, $j$} \\
-g_{lk} = \displaystyle \ln \left[ \frac{ f_{lk} }{1 - \sum _{m=0}^{k} f_{lm} } \right] \;\;\; & \mbox{for $k=1, ..., K-1$, any $j$} 
+g_{lk} = \displaystyle \ln \left[ \frac{ f_{lk} }{1 - \sum _{m=0}^{k} f_{lm} } \right] \;\;\; & \mbox{for $k=1, ..., K-1$} %, any $j$} 
 \end{cases}
@@
 %%%
-Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$ and $f$ always satisfy our constraints.
+Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$.
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Prior: Gaussian Processes}
+\label{ss:gp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{This is just a quick draft and will need to be updated significantly.}
+
+As seen in Section \ref{ss:degeneracy}, the solution is highly degenerate, and in general we cannot reduce to a unique solution. 
+Therefore, we may want to give a prior in estimating the area fractions. 
+What kind of assumptions can we make?
+
+In general, the large time/longitude variations in apparent area fractions corresponds to spectrally similar surface types, because such solution correspond to the proximity of the inner boundary in the $J$-dimensional space discussed above.
+On the contrary, spectrally well-separated surface types correspond to small time/longitude variations in the apparent area fractions. 
+In the real world, we might expect that the latter is more likely, i.e., covering area fraction of any surface type would not change significantly along the longitude (or in time). 
+This would be a reasonable assumption for the estimation of $\{s, \fast \}$, since the illuminated and visible area is usually broad and tend to change the averaged area fraction of each surface type only gently.
+Although there is no physical proof for this assumption...
+
+The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
+We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
+Such assumption can be represented by the prior of 
+%%%
+\begin{equation}
+\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
+\end{equation}
+%%%
+or
+%%%
+\begin{equation}
+\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
+\end{equation}
+%%%
+where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
+In this paper, we assume squared exponential covariance function, i.e., 
+%%%
+\begin{equation}
+\tilde \Sigma _{ii'} = \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
+\end{equation}
+%%%
+where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
+%%%
+\begin{equation}
+\Sigma _{ll'} = \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
+\end{equation}
+%%%
+where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Creating Mock Data}
+\label{ss:createmockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!hbt]
+\begin{figure*}[hb!]
     \begin{minipage}{0.5\hsize}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Creating Mock Data}
-\label{ss:createmockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
@@
 The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.
+
+\clearpage
 
@@
 %\includegraphics[width=\hsize]{PCA_projected.pdf}
-\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
+\includegraphics[width=\hsize]{mockdata_quadrature_PCplane_reduced.pdf}
     \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bpth]
+\begin{figure*}[!htbp]
     \begin{center}
@@
 
-\newpage
+\clearpage
 

### 2016-10-18 paper/main.tex
text updated, figure trimmed
text and figures updated
merged
forgot to commit

@@
 %
-Nicolas Cowan ?\altaffilmark{4} 
+Nicolas Cowan\altaffilmark{4} 
 %
@@
 
-\memoYF{\citet{Cowan2013} found a more reasonable answer for $s$ when they fitted with $\{ f, s \}$, but I think this is a coincidence. }
-
 \newpage
@@
 \begin{equation}
-\tilde \Sigma _{ii'} = \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
+\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
 \end{equation}
@@
 \begin{equation}
-\Sigma _{ll'} = \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
+\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hb!]
+\begin{figure*}[bth!]
     \begin{minipage}{0.5\hsize}
@@
 
-\clearpage
+\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!bpth]
+\begin{figure}[th]
     \begin{center}
-\includegraphics[width=\hsize]{PCA_V_jn.pdf}
+\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
     \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bpth]
+\begin{figure*}[b]
     \begin{center}
 %\includegraphics[width=\hsize]{PCA_projected.pdf}
-\includegraphics[width=\hsize]{mockdata_quadrature_PCplane_reduced.pdf}
+\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
     \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
 
@@
     \begin{center}
-\includegraphics[width=\hsize]{xmed_std_time.pdf}
-\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
+\includegraphics[width=\hsize]{xmed_std_regtime_l1e-2.pdf}
     \end{center}
-    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
+    \caption{Result of estimation for $\{ \fast,\,s\}$ with $\lambda = 0.01$. \memoYF{MC chains do not fully converge in 5000 steps. The evolution of the chains are very weird.}}
     \label{fig:shrinkwrap}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!htbp]
+    \begin{center}
+\includegraphics[width=\hsize]{xmed_std_regtime_l1e-4.pdf}
+    \end{center}
+    \caption{Result of estimation for $\{ \fast,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
+\label{fig:shrinkwrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!htbp]
+    \begin{center}
+\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
+    \end{center}
+    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.01$. \memoYF{MC chains do not fully converge in 5000 steps, and it is not a single peak!!}}
+\label{fig:xmed_std_reglong_l1e-2}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!htbp]
+    \begin{center}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
+    \end{center}
+    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
+\label{fig:shrinkwrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[!htbp]
+%    \begin{center}
+%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
+%    \end{center}
+%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
+%\label{fig:shrinkwrap}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[!htbp]
+%    \begin{center}
+%\includegraphics[width=\hsize]{xmed_std_time.pdf}
+%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
+%    \end{center}
+%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
+%\label{fig:shrinkwrap}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
+
+\acknowledgments
+
+\bibliography{ref}
+
+\newpage
+
+\appendix
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!tb]
+\begin{figure*}[b!]
     \begin{center}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Retrieval using equation (\ref{eq:}) }
-\label{ss:retrieval}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-First, each series of data is analyzed separately. 
-Without regularization and with regularization
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{s:discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Uncertainty in Radius}
-\label{ss:radius}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sensitivity to Initial Condition}
-\label{ss:initialcondition}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}
-\label{s:summary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\acknowledgments
-
-\bibliography{ref}
-
 \end{document}

### 2016-10-31 paper/main.tex
incorporating Nick's feedback

--- 2016-10-17 paper/main.tex
@@
 
-Future direct imaging observations of terrestrial exoplanets is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
-A substantial number of work have seeked detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
-It has been pointed out that not only some of atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but also surface reflectance spectra affect the continuum of the spectra, which could be measured through low-resolution spectra, or multi-band photometry (color) \citep[e.g.,][]{Ford2001}.
+Future direct imaging of terrestrial exoplanets is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
+Substantial work has gone into prediciting detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
+Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry \citep[e.g.,][]{Ford2001}.
 
-However, interpretation of disk-integrated colors is not trivial. 
-This is particularly true for Earth-like planets that harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possible biological surfaces, e.g.
-vegetation.
-Disentangling specific features from the mixed disk-integrated colors can be very challenging.
+However, interpreting of disk-integrated colors is not trivial. 
+This is particularly true for Earth-like planets that harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possibly vegetation. 
+Disentangling specific features from the disk-integrated colors can be very challenging.
 
-A key here is to use time variation of the spectra; because the surface area that contributes to the scattered light changes due to the planetary spin rotation and the orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
-\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of the Earth, and found that number of surface types can be inferred from the number of dominant principle components; (\# of surface types) $\ge $ (\# of principal componentes) $+ 1$.
+A key here is to leverage the time variation of the spectrum: the regions that contributes to the scattered light change due to the planetary rotation and  orbital revolution, the time variability can in principle be translated to the heterogeneity of the surface environment.
+\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of Earth.
+They found that number of surface types can be inferred from the number of dominant principle components; (\# of surface types) $\ge $ (\# of principal components) $+ 1$.
 %) and that the variation pattern is indicative of the surface properties.
-\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are reasonably recovered.
-Moreover, by coupling the time variation due to spin rotation and that due to orbital revolution, 2-dimensional information of the surface may be retrieved with sufficient quality of data \citep{Kawahara2010, Kawahara2011, Fujii2012}.
+\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered.
+Moreover, by coupling the time variation due to rotation and orbital revolution, a 2-dimensional information of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
 
 \citet{Cowan2013} took another approach to the same inverse problem. 
-Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters and letting them fit the data.
-The result appeared successful to the extent that the obtained reflectance spectra roughly match the typical spectra of clouds, ocean, and continents. 
+Their strategy is to try to estimate the physically meaningful reflectance spectra and their distribution across the globe simultaneously, by making all of them fitting parameters. 
+The result appeared successful to the extent that the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents. 
 However, the longitudinal map of these components do not match the reality sufficiently well.
 
-We were motivated by this unsatisfactory result and decided to revisit their analysis with some updates. 
+We were motivated by this unsatisfactory result to revisit their analysis. 
 Specifically, the updates include:
@@
 
-For the moment, let us suppose that the planetary radius and the observational geometry (latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet) are fully known.
-(This will be relaxed in \S\ref{s:discussion}.)
-In this case, we can straightforwardly translate the observed planetary intensity to albedo (or reflectivity) using the stellar flux. 
-A useful normalization for albedo in exoplanet observations is {\it apparent albedo}, which is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will consistently use apparent albedo for our study unless otherwise noted.
+For the moment, let us suppose that the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet (This will be relaxed in \S\ref{s:discussion}.)
+In this case, we can straightforwardly translate the observed planetary intensity to apparent albedo. 
+{\it Apparent albedo} is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted.
 
-The observed apparent albedo, $d_{ij}$ (``$d$'' for data), can be written as \citep[see][]{Fujii2010}: 
+The observed apparent albedo, $d_{ij}$ (``$d$'' for data), can be written using the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$, (both defined at each surface point) as follows \citep[see][]{Fujii2010}:
 %%%
@@
 &=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
-&\equiv & \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:d_f_ast_s}
+&=& \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:d_f_ast_s}
 \end{eqnarray}
 %%%
-where $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
+where
+%%%
+\begin{eqnarray}
+s _{kj} &\equiv & s_k (\lambda _j) \\
+\tilde f_{ik} &\equiv & \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }
+\end{eqnarray}
+%%%
+and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
 In the last expression, $\fast_{lk}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
@@
 \begin{cases}
-\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 < \fast_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
+\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
+\;\; 0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
 \;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
@@
 &=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
-&\sim & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
-&\equiv & \sum_l  W_{il} f_{lk} \label{eq:Wf}
+&\approx & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
+&\equiv & \sum_l  W_{il} f_{lk} \label{eq:Wf}, 
 \end{eqnarray}
@@
 \begin{equation}
-d_{ij} = R_p^2 \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
+d_{ij} = \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
 \end{equation}
@@
 \begin{cases}
-\;\; 0 < s_{kj} < 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 < f_{lk} < 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f} \\
+\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
+\;\; 0 \leq f_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f} \\
 \;\; \sum_k f_{lk} = 1 & \mbox{for any $l$} 
@@
 
-\citet{Cowan2013} suggested the specific procedure to find the solution for $\{f, s\}$. 
+\citet{Cowan2013} proposed the specific procedure to find the solution for $\{f, s\}$. 
 Namely, 
@@
 (3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
-(In the last step, the initial value for $f$ is fixed at 1/(\# of surface types).)
+(The initial value for $f$ is fixed at 1/(\# of surface types).)
 
@@
 %Suppose the above approximation is justified. 
-In essence, $f^{\ast }_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
+In essence, $\fast_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
 %
@@
 Rather, it could return less reasonable results because of the approximation adopted in equation (\ref{eq:discretize}).
-
-\memoYF{\citet{Cowan2013} found a more reasonable answer for $s$ when they fitted with $\{ f, s \}$, but I think this is a coincidence. }
 
@@
 
-\clearpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!bpth]
+\begin{figure}[t]
     \begin{center}
-\includegraphics[width=\hsize]{PCA_V_jn.pdf}
+\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
     \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bpth]
+\begin{figure*}[bt]
     \begin{center}
 %\includegraphics[width=\hsize]{PCA_projected.pdf}
-\includegraphics[width=\hsize]{mockdata_quadrature_PCplane_reduced.pdf}
+\includegraphics[width=0.9\hsize]{mockdata_quadrature_PCplane.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{xmed_std_time.pdf}
-\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
+%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-2.pdf}
+%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-4.pdf}
+\includegraphics[width=\hsize]{xmed_std_regtime_l1e-2.pdf}
+\includegraphics[width=\hsize]{xmed_std_regtime_l1e-4.pdf}
     \end{center}
-    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
+    \caption{Regularization in terms of time. Upper: $\lambda = 0.01$. Lower: $\lambda = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
+\label{fig:shrinkwrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!bpth]
+    \begin{center}
+\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
+%\includegraphics[width=\hsize]{xmed_std_reglong_l1e-4.pdf}
+    \end{center}
+    \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
+
 \label{fig:shrinkwrap}
@@
 \clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{s:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Uncertainty in Radius}
+\label{ss:radius}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
+\label{s:summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\acknowledgments
+
+\bibliography{ref}
+
+\appendix
 

### 2016-11-09 main_fitlc_mcmc.py
adding shrinkwrap code etc... (sorry I forgot to do so earlier)

@@ -5,6 +5,24 @@ import matplotlib.pyplot as pl
 from scipy.optimize import minimize
 import sys
 import corner
+import datetime
+import multiprocessing
+import os
+import pdb
+
+from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
+    REGULARIZATION, deg2rad, N_SIDE, INFILE, calculate_walkers, KNOWN_ANSWER, \
+    ALBDFILE, AREAFILE, SLICE_TYPE, N_SLICE_LONGITUDE, GEOM
+
+import prior
+import reparameterize
+
+import PCA
+import shrinkwrap
+
+import geometry
+
+NCPU = multiprocessing.cpu_count()
 
 # March 2008
 #LAT_S = -0.5857506  # sub-solar latitude
@@ -12,147 +30,25 @@ import corner
 #LAT_O = 1.6808370  # sub-observer longitude
 #LON_O = 210.1242232 # sub-observer longitude
 
-NUM_MCMC = 100
-NUM_MCMC_BURNIN = 100
-
-SIGMA_Y  = 3.0
-NOISELEVEL = 0.1
-
-FLAG_REG_AREA = False
-FLAG_REG_ALBD = False
-
-N_SLICE = 4
-N_TYPE  = 2
-
-deg2rad = np.pi/180.
-
-N_SIDE   = 32
-# INFILE = "/Users/yuka/data/EPOXI/Earth/raddata_2_norm"
-#INFILE = "mockdata/mock_simple_1_data"
-INFILE = 'mockdata/mock_simple_1_scattered0.01_data_with_noise'
 
 #===================================================
 # basic functions
-#===================================================
+#=============================================== ====
 
-#---------------------------------------------------
-def latlon2cart(lat, lon):
-    x = np.sin((90.-lat)*deg2rad)*np.cos(lon*deg2rad)
-    y = np.sin((90.-lat)*deg2rad)*np.sin(lon*deg2rad)
-    z = np.cos((90.-lat)*deg2rad)
-    return np.array([x,y,z])
-
-
-#---------------------------------------------------
-def weight(time):
-    """
-    Weight of pixel at (lat_r, lon_r) assuming Lambertian surface
-    """
-    EO_vec = latlon2cart(LAT_O, LON_O-OMEGA*time/deg2rad)
-    ES_vec = latlon2cart(LAT_S, LON_S-OMEGA*time/deg2rad)
[…]

### 2016-11-09 main_plot_PCplane2D.py

@@ -1,0 +1,178 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+from matplotlib import gridspec
+import sys, getopt
+
+# Specify directory of run to analyze
+MCMC_DIR = "mcmc_output/2016-07-13--11-59/"
+DIR = "mcmc_output/"
+
+# RESOLUTION=1000
+RESOLUTION=500
+
+#--------------------------------------------------
+def allowed_region( mcmc_dir ):
+
+    # read PCs
+    V_nj = np.loadtxt( mcmc_dir+'PCA_V_jn' ).T
+    PC1 = V_nj[0]
+    PC2 = V_nj[1]
+    n_band = len( PC1 )
+    band_ticks = np.arange( n_band )
+
+    ave_j = np.loadtxt( mcmc_dir+'AVE_j' )
+
+    print '# ave_j ', ave_j
+
+    x_ticks = np.linspace(-0.4,0.2,RESOLUTION)
+    y_ticks = np.linspace(-0.2,0.4,RESOLUTION)
+    x_mesh, y_mesh, band_mesh = np.meshgrid( x_ticks, y_ticks, band_ticks, indexing='ij' )
+    vec_mesh = x_mesh * PC1[ band_mesh ] + y_mesh * PC2[ band_mesh ] + ave_j[ band_mesh ]
+
+    x_grid, y_grid = np.meshgrid( x_ticks, y_ticks, indexing='ij' )
+    prohibited_grid = np.zeros_like( x_grid )
+
+    for ii in xrange( len( x_ticks ) ) :
+        for jj in xrange( len( y_ticks ) ) :
+
+            if np.any( vec_mesh[ii][jj] < 0. ) :
+                prohibited_grid[ii][jj] = 1
+                if np.any( vec_mesh[ii][jj] > 1. ) :
+                    prohibited_grid[ii][jj] = 3
+            elif np.any( vec_mesh[ii][jj] > 1. ) :
+                prohibited_grid[ii][jj] = 2
+            else :
+                prohibited_grid[ii][jj] = 0
+
+    return x_grid, y_grid, prohibited_grid
+
+
+
+def generate_cmap(colors):
+    """
+    copied from) http://qiita.com/kenmatsu4/items/fe8a2f1c34c8d5676df8
+    """
+    values = range(len(colors))
+    vmax = np.ceil(np.max(values))
+    color_list = []
[…]

### 2016-11-09 preprocess.py

@@ -1,0 +1,25 @@
+import numpy as np
+import sys
+import PCA
+import shrinkwrap
+
+INFILE = 'data/raddata_2_norm'
+
+#===================================================
+def do ( Obs_ij, run_dir ) :
+
+    # PCA
+    N_PCs, V_nj, U_in = PCA.do_PCA( Obs_ij, run_dir ) 
+
+    print '# ---------------------------------------------------'
+    print '# U_in'
+    # print samples
+    for ii in xrange( len( U_in ) ):
+        for nn in xrange( len( U_in.T ) ):
+            print U_in[ii][nn],
+        print ''
+    print ''
+
+    # shrink wrap
+    A_mn = shrinkwrap.do_shrinkwrap ( U_in, N_PCs, run_dir )
+    

### 2016-11-09 shrinkwrap.py

@@ -1,0 +1,125 @@
+import numpy as np
+import math
+import sys
+from scipy.optimize import minimize
+
+ALPHA_INI = 1.e-4
+DIFF_LIM  = 1e-1
+
+
+
+#---------------------------------------------------
+def init_A_nm( n_PC ) :
+
+    # N ( = n_PC ): number of principle components
+    # M ( = n_PC + 1 ) : number of vertices
+    # dimension of A_nm     : N x M
+    # dimension of A_mn_tmp : M x N just for personal convenience
+
+    A_mn_tmp = np.array( [-1., 1.] ) # each side has length '2'
+    for nn in xrange( 1, n_PC ) :
+
+        # new dimension for the previous point(s)
+        A_mn_tmp = np.c_[ A_mn_tmp,  [0.]*len( A_mn_tmp ) ]
+        # the new dimension for the new point
+        distance = np.sqrt( 2.**2 - np.sum( A_mn_tmp[0]**2 ) )
+        A_mn_tmp = np.vstack( [ A_mn_tmp, [0.]*( len( A_mn_tmp ) -1 )+[ distance ]  ] )
+        # balance point
+        balance_n = np.sum( A_mn_tmp, axis=0 ) / len( A_mn_tmp )
+        A_mn_tmp  = A_mn_tmp - balance_n
+
+    return A_mn_tmp.T
+
+
+#---------------------------------------------------
+def get_volume ( A_nm, n_PC ) :
+
+    AA_nn = np.delete( A_nm, (0), axis=1 )
+    dAA_nn = AA_nn - np.tile( A_nm.T[0] , [ len( AA_nn ), 1 ] ).T
+    vol = 1. / math.factorial( n_PC ) * np.absolute( np.linalg.det( dAA_nn ) )
+    return vol
+
+
+#---------------------------------------------------
+def get_penalty ( UU_qi, AA_qm ) :
+
+    P_mi = np.dot( np.linalg.inv( AA_qm ) , UU_qi )
+    if ( np.all( P_mi > 0. ) and np.all( P_mi < 1. ) ) :
+        pnlty = np.sum( 1. / P_mi )
+    else :
+        pnlty = 1e10
+    return pnlty
+
+
+#---------------------------------------------------
+def func_to_minimize ( A_nm_flat, *args ) :
+
+    UU_qi, n_PC, alpha = args
+    A_nm = A_nm_flat.reshape( [ n_PC , n_PC+1 ] )
+
+    A_mn = A_nm.T
[…]

### 2016-11-09 PCA.py
adding more files

@@ -1,0 +1,42 @@
+import numpy as np
+from sklearn.decomposition import PCA
+
+from fitlc_params import ALBDFILE
+
+#---------------------------------------------------
+def do_PCA ( Dij, run_dir, E_cutoff=5e-2 ):
+
+    # number of principle components
+    decomposer = PCA(n_components=len(Dij.T))
+
+    # execute
+    # YFYFYF    decomposer.fit(data.T)
+    U = decomposer.fit_transform( Dij )
+
+    M = decomposer.mean_
+
+    # PCs
+    V = decomposer.components_
+
+    # eigen values
+    E = decomposer.explained_variance_ratio_
+
+    N_PCs = np.sum( E > E_cutoff )
+
+    print "   cut-off below", E_cutoff, "..."
+    print "   # of PCs: ", N_PCs
+
+    np.savetxt( run_dir+'PCA_V_jn', V.T, header='Principal Components ( dimension: band x index )' ) 
+    np.savetxt( run_dir+'PCA_E_n', E, header='Contribution factor ( dimension: index )' ) 
+    np.savetxt( run_dir+'PCA_U_in', U, header='Conefficient ( dimension: time x index )' ) 
+    np.savetxt( run_dir+'AVE_j', M, header='Time Average ( dimension: band )' ) 
+
+    # projection of 'answer' onto PC plane
+    albd_kj  = np.loadtxt( ALBDFILE ).T
+    dalbd_kj = albd_kj - M
+#    coeff_kn = np.dot( dalbd_kj, np.linalg.inv( V ) )
+    coeff_kn = np.dot( dalbd_kj, V.T )
+    np.savetxt( run_dir+'PCA_answer_projected', coeff_kn )
+
+    return N_PCs, V[:N_PCs][:], U[:,:N_PCs], M
+

### 2016-11-12 main_IGBP_time.py
code to simulate lightcurves with simplified IGBP map

@@ -1,0 +1,234 @@
+import netCDF4
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import cm
+from matplotlib import font_manager
+from copy import deepcopy
+import sys
+import healpy as hp
+from scipy import constants
+import geometry
+import operator
+
+#-----------------------------------------------------------------------------
+target_indx_list = [[ 17 ], # ocean
+                    [ 7, 11, 13, 15, 16 ], # soil
+                    [ 1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14 ]] # vegetation
+
+#-----------------------------------------------------------------------------
+
+# MODE = 'March'
+# MODE = 'June'
+MODE= 'specify'
+TAG='45deg'
+# vegetation
+# target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
+ #target_indx = [1, 2, 3, 4, 5, 6, 10, 14]
+
+# soil
+#target_indx = [7,8,9,11,12,13,16]
+
+# ocean
+target_indx = [17]
+
+# all
+# target_indx = range(1,18)
+
+
+cldoptd_crit = 5.
+
+TIME_END = 24.0
+TSTEP = 1.0
+Pspin = 24.0
+OMEGA = ( 2. * np.pi / Pspin )
+
+# HealPix
+N_side_seed = 2
+N_SIDE  = 2*2**N_side_seed
+
+N_pixel = 12*N_SIDE**2
+
+print '# N_pixel', N_pixel
+
+
+#--------------------------------------------------------------------
+# set-up
+#--------------------------------------------------------------------
+
+if ( MODE == 'March' ):
+# based on spectroscopic data
+#         Sub-Sun Lon/Lat =      97.091       -0.581 /     W longitude, degrees 
+#         Sub-SC  Lon/Lat =     154.577        1.678 /     W longitude, degrees
+    LAT_S = -0.581  # sub-solar latitude
+    LON_S = 262.909  # sub-solar longitude
+    LAT_O = 1.678  # sub-observer latitude
+    LON_O = 205.423 # sub-observer longitude
+    INFILE = "data/raddata_1_norm"
+    Time_i = np.arange(25)*1.
+    cldfile_frac = "data/cldfrac_EPOXI_March_6.dat"
[…]

### 2016-11-12 main_IGBP_time_scat.py

@@ -1,0 +1,238 @@
+import netCDF4
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import cm
+from matplotlib import font_manager
+from copy import deepcopy
+import sys
+import healpy as hp
+from scipy import constants
+import geometry
+import operator
+
+#-----------------------------------------------------------------------------
+target_indx_list = [[ 17 ], # ocean
+                    [ 7, 11, 13, 15, 16 ], # soil
+                    [ 1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14 ]] # vegetation
+
+#-----------------------------------------------------------------------------
+
+# MODE = 'March'
+# MODE = 'June'
+MODE= 'specify'
+TAG='90deg'
+SIGMA=0.01
+# vegetation
+# target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
+ #target_indx = [1, 2, 3, 4, 5, 6, 10, 14]
+
+# soil
+#target_indx = [7,8,9,11,12,13,16]
+
+# ocean
+target_indx = [17]
+
+# all
+# target_indx = range(1,18)
+
+
+cldoptd_crit = 5.
+
+TIME_END = 24.0
+TSTEP = 1.0
+Pspin = 24.0
+OMEGA = ( 2. * np.pi / Pspin )
+
+# HealPix
+N_side_seed = 2
+N_SIDE  = 2*2**N_side_seed
+
+N_pixel = 12*N_SIDE**2
+
+print '# N_pixel', N_pixel
+
+
+#--------------------------------------------------------------------
+# set-up
+#--------------------------------------------------------------------
+
+if ( MODE == 'March' ):
+# based on spectroscopic data
+#         Sub-Sun Lon/Lat =      97.091       -0.581 /     W longitude, degrees 
+#         Sub-SC  Lon/Lat =     154.577        1.678 /     W longitude, degrees
+    LAT_S = -0.581  # sub-solar latitude
+    LON_S = 262.909  # sub-solar longitude
+    LAT_O = 1.678  # sub-observer latitude
+    LON_O = 205.423 # sub-observer longitude
+    INFILE = "data/raddata_1_norm"
+    Time_i = np.arange(25)*1.
+    cldfile_frac = "data/cldfrac_EPOXI_March_6.dat"
[…]

### 2016-11-12 fitlc_params.py
ocean albedo

@@ -4,38 +4,44 @@ import numpy as np
 # Parameters
 #--------------------------------------------------------------------
 
-NUM_MCMC = 10000
+NUM_MCMC = 5000
 NUM_MCMC_BURNIN = 0
-SEED_AMP = 0.5
+SEED_AMP = 0.1
 
-#REGULARIZATION = None
-REGULARIZATION = 'GP'
-#REGULARIZATION = 'GP2'
-#REGULARIZATION = 'Tikhonov'
-
-SIGMA_Y  = 3.0
+SIGMA_Y  = 100.0
 NOISELEVEL = 0.01
 
-FLAG_REG_AREA = False
-FLAG_REG_ALBD = False
+#REGULARIZATION = 'GP'
+#REGULARIZATION = 'GP2'
+REGULARIZATION = 'GP4'
+#REGULARIZATION = 'Tikhonov'
+#REGULARIZATION = None
 
-#n_slice = 4
-N_TYPE  = 3
+SLICE_TYPE = 'time'
+# SLICE_TYPE = 'longitude'
+N_SLICE_LONGITUDE = 5
+
+# lat_o, lon_o, lat_s, lon_s, omega
+GEOM = ( 0., 0., 0.,  90., 2.*np.pi )
 
 deg2rad = np.pi/180.
 
-N_SIDE   = 128
+N_SIDE   = 32
+# INFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/mockdata_quadrature_lc'
+# INFILE = 'data/raddata_1_norm'
+# INFILE = 'simpleIGBP_quadrature_lc'
+INFILE = 'mockdata_90deg_lcscat'
 
+KNOWN_ANSWER=False
+ALBDFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/simpleIGBP_quadrature_bandsp'
+AREAFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/simpleIGBP_quadrature_factor'
 #INFILE = "data/raddata_12_norm"
-##INFILE = "data/raddata_2_norm"
+#INFILE = "data/raddata_2_norm"
+#INFILE = "data/raddata_2_norm"
 #INFILE = "mockdata/mock_simple_1_data"
 #INFILE = "mockdata/mock_simple_3types_1_data"
 # INFILE = 'mockdata/mock_simple_1_scattered0.01_data_with_noise'
[…]

### 2016-11-12 main_IGBP_time_scat.py

@@ -20,7 +20,7 @@ target_indx_list = [[ 17 ], # ocean
 # MODE = 'March'
 # MODE = 'June'
 MODE= 'specify'
-TAG='90deg'
+TAG='90deg_13time'
 SIGMA=0.01
 # vegetation
 # target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
@@ -38,9 +38,8 @@ target_indx = [17]
 
 cldoptd_crit = 5.
 
-TIME_END = 24.0
 TSTEP = 1.0
-Pspin = 24.0
+Pspin = 1.0
 OMEGA = ( 2. * np.pi / Pspin )
 
 # HealPix
@@ -49,8 +48,7 @@ N_SIDE  = 2*2**N_side_seed
 
 N_pixel = 12*N_SIDE**2
 
-print '# N_pixel', N_pixel
-
+SEED_in  = 11943
 
 #--------------------------------------------------------------------
 # set-up
@@ -65,7 +63,7 @@ if ( MODE == 'March' ):
     LAT_O = 1.678  # sub-observer latitude
     LON_O = 205.423 # sub-observer longitude
     INFILE = "data/raddata_1_norm"
-    Time_i = np.arange(25)*1.
+    Time_i = np.arange(25)*1./24.
     cldfile_frac = "data/cldfrac_EPOXI_March_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_March_6.dat"
 elif ( MODE == 'June' ):
@@ -83,7 +81,7 @@ elif ( MODE == 'June' ):
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
     INFILE = "data/raddata_2_norm"
-    Time_i = np.arange(25)*1.
+    Time_i = np.arange(25)*1./24.
 
 elif ( MODE == 'specify' ):
     LON_S = 90.
@@ -96,7 +94,8 @@ elif ( MODE == 'specify' ):
 #    LAT_S = 21.6159766
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
-    Time_i = np.arange(7)*1./7.*24.
+    N_TIME = 13
+    Time_i = np.arange( N_TIME + 1 ) / ( N_TIME*1. )
 else:
     print 'ERROR: Invalid MODE'
[…]

### 2016-11-12 prior.py

@@ -11,7 +11,7 @@ def get_ln_prior_albd( y_albd_kj ):
 
 
 #---------------------------------------------------
-def get_ln_prior_area_new( y_area_lk, x_area_lk ):
+def get_ln_prior_area_new( y_area_lk ):
 
 #    x_area_lk is a dummy
     prior_lk = np.exp( y_area_lk ) / ( 1 + np.exp( y_area_lk ) )**2

### 2016-11-12 fitlc_params.py
spider graph

@@ -29,8 +29,9 @@ deg2rad = np.pi/180.
 N_SIDE   = 32
 # INFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/mockdata_quadrature_lc'
 # INFILE = 'data/raddata_1_norm'
-# INFILE = 'simpleIGBP_quadrature_lc'
-INFILE = 'mockdata_90deg_lcscat'
+INFILE = 'mockdata/simpleIGBP_quadrature_lc'
+# INFILE = 'mockdata_90deg_13time_lcscat'
+# INFILE = 'mockdata_90deg_lc'
 
 KNOWN_ANSWER=False
 ALBDFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/simpleIGBP_quadrature_bandsp'

### 2016-11-12 geometry.py

@@ -27,6 +27,20 @@ def weight(time, n_side, param_geometry):
 
 
 #---------------------------------------------------
+def weight_2(time, n_side, param_geometry):
+    """
+    Weight of pixel at (lat_r, lon_r) assuming Lambertian surface
+    """
+    lat_o, lon_o, lat_s, lon_s, omega = param_geometry
+    EO_vec = latlon2cart(lat_o, lon_o-omega*time/deg2rad)[0]
+    ES_vec = latlon2cart(lat_s, lon_s-omega*time/deg2rad)[0]
+    ER_vec_array = np.array(hp.pix2vec(n_side, np.arange(hp.nside2npix(n_side))))
+    cosTH0_array = np.dot(ES_vec, ER_vec_array)
+    cosTH1_array = np.dot(EO_vec, ER_vec_array)
+    return np.clip(cosTH0_array, 0., 1.)*np.clip(cosTH1_array, 0., 1.)
+
+
+#---------------------------------------------------
 #def weight(time, n_side, nn, param_geometry):
 #    """
 #    Weight of pixel at (lat_r, lon_r) assuming Lambertian surface

### 2016-11-12 main_IGBP_time_scat.py

@@ -95,7 +95,7 @@ elif ( MODE == 'specify' ):
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
     N_TIME = 13
-    Time_i = np.arange( N_TIME + 1 ) / ( N_TIME*1. )
+    Time_i = np.arange( N_TIME ) / ( N_TIME*1. )
 else:
     print 'ERROR: Invalid MODE'
     sys.exit()
@@ -208,7 +208,7 @@ contribution_factor = np.zeros( [ len(Time_i),  len( target_indx_list ) ] )
 for ii in xrange( len(Time_i) ) :
 
     time = Time_i[ii]
-    weight_array0 = geometry.weight( time, N_SIDE, param_geometry )
+    weight_array0 = geometry.weight_2( time, N_SIDE, param_geometry )
     norm = np.sum( weight_array0 )
 
     for kk in xrange( len( target_indx_list ) ):

### 2016-11-12 main_plot_PCplane2D_terms.py

@@ -1,0 +1,330 @@
+import numpy as np
+import sys
+import corner
+import datetime
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from matplotlib.colors import LinearSegmentedColormap
+
+from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
+    REGULARIZATION, deg2rad, N_SIDE, INFILE, calculate_walkers, \
+    ALBDFILE, AREAFILE, SLICE_TYPE, N_SLICE_LONGITUDE, GEOM
+
+import prior
+import reparameterize
+
+import PCA
+import shrinkwrap
+
+import geometry
+
+LOOP_MAX  = 10000
+COUNT_MAX = 100
+SEED_in  = 2013
+
+SIGMA_Y = 100.
+WL_AMP  = 0.
+LAMBDA_CORR_DEG = 120
+LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
+
+RESOLUTION=1000
+# RESOLUTION=100
+
+# March 2008
+#LAT_S = -0.5857506  # sub-solar latitude
+#LON_S = 267.6066184  # sub-solar longitude
+#LAT_O = 1.6808370  # sub-observer longitude
+#LON_O = 210.1242232 # sub-observer longitude
+
+
+#===================================================
+# basic functions
+#=============================================== ====
+
+np.random.seed(SEED_in)
+
+
+#---------------------------------------------------
+def regularize_area_GP( x_area_lk, regparam ):
+
+    sigma, wn_rel_amp_seed, lambda_angular = regparam
+
+    wn_rel_amp = np.exp( wn_rel_amp_seed ) / ( 1. + np.exp( wn_rel_amp_seed ) )
+#    print 'wn_rel_amp', wn_rel_amp
+#    print 'lambda_angular', lambda_angular
+    l_dim = len( x_area_lk )
+    cov = prior.get_cov( sigma, wn_rel_amp, lambda_angular, l_dim )
+
+#    print 'cov', cov
+    inv_cov = np.linalg.inv( cov )
+    det_cov = np.linalg.det( cov )
+    if ( det_cov == 0. ):
+        print 'det_cov', det_cov
+        print 'cov', cov
+
+#    print 'inv_cov', inv_cov
[…]

### 2016-11-12 PCA.py
output in PCA routine is now optional

@@ -4,7 +4,7 @@ from sklearn.decomposition import PCA
 from fitlc_params import ALBDFILE
 
 #---------------------------------------------------
-def do_PCA ( Dij, run_dir, E_cutoff=5e-2 ):
+def do_PCA ( Dij, E_cutoff=5e-2, output=True, run_dir='' ):
 
     # number of principle components
     decomposer = PCA(n_components=len(Dij.T))
@@ -26,17 +26,17 @@ def do_PCA ( Dij, run_dir, E_cutoff=5e-2 ):
     print "   cut-off below", E_cutoff, "..."
     print "   # of PCs: ", N_PCs
 
-    np.savetxt( run_dir+'PCA_V_jn', V.T, header='Principal Components ( dimension: band x index )' ) 
-    np.savetxt( run_dir+'PCA_E_n', E, header='Contribution factor ( dimension: index )' ) 
-    np.savetxt( run_dir+'PCA_U_in', U, header='Conefficient ( dimension: time x index )' ) 
-    np.savetxt( run_dir+'AVE_j', M, header='Time Average ( dimension: band )' ) 
-
-    # projection of 'answer' onto PC plane
-    albd_kj  = np.loadtxt( ALBDFILE ).T
-    dalbd_kj = albd_kj - M
-#    coeff_kn = np.dot( dalbd_kj, np.linalg.inv( V ) )
-    coeff_kn = np.dot( dalbd_kj, V.T )
-    np.savetxt( run_dir+'PCA_answer_projected', coeff_kn )
+    if output :
+        np.savetxt( run_dir+'PCA_V_jn', V.T, header='Principal Components ( dimension: band x index )' ) 
+        np.savetxt( run_dir+'PCA_E_n', E, header='Contribution factor ( dimension: index )' ) 
+        np.savetxt( run_dir+'PCA_U_in', U, header='Conefficient ( dimension: time x index )' ) 
+        np.savetxt( run_dir+'AVE_j', M, header='Time Average ( dimension: band )' ) 
+        # projection of 'answer' onto PC plane
+        albd_kj  = np.loadtxt( ALBDFILE ).T
+        dalbd_kj = albd_kj - M
+    #    coeff_kn = np.dot( dalbd_kj, np.linalg.inv( V ) )
+        coeff_kn = np.dot( dalbd_kj, V.T )
+        np.savetxt( run_dir+'PCA_answer_projected', coeff_kn )
 
     return N_PCs, V[:N_PCs][:], U[:,:N_PCs], M
 

### 2016-11-12 main_fitlc_mcmc.py

@@ -255,7 +255,7 @@ if __name__ == "__main__":
 
         # PCA
         print 'Performing PCA...'
-        n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, run_dir, E_cutoff=1e-2 )
+        n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, run_dir=run_dir )
         n_type = n_pc + 1
 
         # shrinkwrap

### 2016-11-12 main_plot_PCplane2D_terms.py

@@ -29,14 +29,15 @@ WL_AMP  = 0.
 LAMBDA_CORR_DEG = 120
 LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
 
-RESOLUTION=1000
-# RESOLUTION=100
+# RESOLUTION=1000
+RESOLUTION=100
 
 # March 2008
 #LAT_S = -0.5857506  # sub-solar latitude
 #LON_S = 267.6066184  # sub-solar longitude
 #LAT_O = 1.6808370  # sub-observer longitude
 #LON_O = 210.1242232 # sub-observer longitude
+
 
 
 #===================================================
@@ -195,7 +196,7 @@ if __name__ == "__main__":
 
     # PCA
     print 'Performing PCA...'
-    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, run_dir, E_cutoff=1e-2 )
+    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, output=False )
     n_type = n_pc + 1
     if n_type != 3 :
         print 'ERROR: This code is only applicable for 3 surface types!'
@@ -293,12 +294,17 @@ if __name__ == "__main__":
 
     # loop end
 
+
+
     # spider graph (?)
     ax1 = plt.subplot(adjustable='box', aspect=1.0)
     ax1.set_xlim([-0.4,0.2])
     ax1.set_ylim([-0.2,0.4])
     ax1.set_xticks([ -0.4, -0.2, 0.0, 0.2 ])
     ax1.set_yticks([ -0.2, 0.0, 0.2, 0.4 ])
+
+    plt.xlabel('PC 1')
+    plt.ylabel('PC 2')
 
     print 'np.array( regterm1_list )', np.array( regterm1_list )
     print 'np.array( regterm2_list )', np.array( regterm2_list )
@@ -316,6 +322,21 @@ if __name__ == "__main__":
         points_kn = np.vstack( [ points_kn, points_kn[0] ] )
         plt.plot( points_kn.T[0], points_kn.T[1], color=cm.hot(colorlevel_sorted[ii]) )
 
+    # data
+    plt.plot( U_in.T[0], U_in.T[1], 'k' )
+    plt.plot( U_in.T[0], U_in.T[1], marker='.', c="black", label='data' )
+
+    # answer
+    # projection of 'answer' onto PC plane
[…]

### 2016-11-13 paper/main.tex
spider graph
add plots showing bestfit with regularization term

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Questions}
+
+\begin{itemize}
+\item Is this a right usage of Gaussian Process?
+\item
+\end{itemize}
+
 \newpage
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[th]
     \begin{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bt]
+\begin{figure*}[bht]
     \begin{center}
 %\includegraphics[width=\hsize]{PCA_projected.pdf}
-\includegraphics[width=0.9\hsize]{mockdata_quadrature_PCplane.pdf}
+\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
     \end{center}
@@
 This is a natural consequence from the fact that the soil and vegetation are minor components and never dominate the surface in the illuminated and visible area, while the apparent covering fraction of ocean comes close to unity.
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{[NEW] Effect of Regularization Term}
+\label{ss:shrinkwrap}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%
+\begin{eqnarray}
+\mathcal{P}_{\fast} &=& \prod _k \left[ \frac{1}{(\sqrt{ 2 \pi })^{I} \sqrt{| \tilde \Sigma |} } \right. \\
+&& \left. \times \exp \left\{ - \sum _{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k} \right\} \right] \\
+\tilde \Sigma _{ii'} (\lambda,  \Delta_t ) &=& \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_t^2} \right)
+\end{eqnarray}
+%%%
+
+%%%
+\begin{eqnarray}
+- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; f) \\
+\mathcal{F}(\lambda, \Delta_t; f)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
+\end{eqnarray}
+%%%
+
+...I think $\fast $ here should be zero mean for each $k$. 
+%%%
+\begin{equation}
+\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
+\end{equation}
+%%%
+In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast } (\Delta_t; f) = \lambda ^2 \mathcal{F}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}    
+    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{Solution with smallest regularization term. }
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
@@
     \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
+\label{fig:xmed_std_reglong_l1e-2}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!htbp]
+    \begin{center}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
+\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
+    \end{center}
+    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
 \label{fig:shrinkwrap}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[!htbp]
+%    \begin{center}
+%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
+%    \end{center}
+%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
+%\label{fig:shrinkwrap}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[!htbp]
+%    \begin{center}
+%\includegraphics[width=\hsize]{xmed_std_time.pdf}
+%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
+%    \end{center}
+%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
+%\label{fig:shrinkwrap}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
+
+\acknowledgments
+
+\bibliography{ref}
+
+\newpage
+
+\appendix
 

### 2016-11-14 fitlc_params.py
adding missed figures

@@ -34,8 +34,8 @@ INFILE = 'mockdata/simpleIGBP_quadrature_lc'
 # INFILE = 'mockdata_90deg_lc'
 
 KNOWN_ANSWER=False
-ALBDFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/simpleIGBP_quadrature_bandsp'
-AREAFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/simpleIGBP_quadrature_factor'
+ALBDFILE = 'mockdata/simpleIGBP_quadrature_bandsp'
+AREAFILE = 'mockdata/simpleIGBP_quadrature_factor'
 #INFILE = "data/raddata_12_norm"
 #INFILE = "data/raddata_2_norm"
 #INFILE = "data/raddata_2_norm"

### 2016-11-14 main_fitlc_mcmc.py

@@ -262,7 +262,7 @@ if __name__ == "__main__":
         print 'Perfoming shrink-wrapping...'
         # N ( = n_PC ): number of principle components
         # M ( = n_PC + 1 ) : number of vertices
-        A_mn, P_im   = shrinkwrap.do_shrinkwrap( U_in, n_pc, run_dir )
+        A_mn, P_im   = shrinkwrap.do_shrinkwrap( U_in, n_pc, run_dir=run_dir )
         X0_albd_kj   = np.dot( A_mn, V_nj )
         X0_albd_kj   = X0_albd_kj + M_j
         if ( SLICE_TYPE=='time' ) :

### 2016-11-14 main_plot_PCplane2D_terms.py

@@ -6,10 +6,11 @@ import os
 
 import matplotlib.pyplot as plt
 import matplotlib.cm as cm
+from mpl_toolkits.axes_grid1 import make_axes_locatable
 from matplotlib.colors import LinearSegmentedColormap
 
-from fitlc_params import NUM_MCMC, NUM_MCMC_BURNIN, SEED_AMP, SIGMA_Y, NOISELEVEL, \
-    REGULARIZATION, deg2rad, N_SIDE, INFILE, calculate_walkers, \
+from PCplane2D_params import NOISELEVEL, \
+    deg2rad, N_SIDE, INFILE_DIR, INFILE, OUTFILE_DIR, \
     ALBDFILE, AREAFILE, SLICE_TYPE, N_SLICE_LONGITUDE, GEOM
 
 import prior
@@ -46,7 +47,6 @@ RESOLUTION=100
 
 np.random.seed(SEED_in)
 
-
 #---------------------------------------------------
 def regularize_area_GP( x_area_lk, regparam ):
 
@@ -58,7 +58,6 @@ def regularize_area_GP( x_area_lk, regparam ):
     l_dim = len( x_area_lk )
     cov = prior.get_cov( sigma, wn_rel_amp, lambda_angular, l_dim )
 
-#    print 'cov', cov
     inv_cov = np.linalg.inv( cov )
     det_cov = np.linalg.det( cov )
     if ( det_cov == 0. ):
@@ -78,7 +77,7 @@ def regularize_area_GP( x_area_lk, regparam ):
     return term1, term2, prior_wn_rel_amp
 
 #---------------------------------------------------
-def regularize_area_GP_new( x_area_lk, regparam ):
+def regularize_area_GP_2( x_area_lk, regparam ):
 
     sigma, wn_rel_amp, lambda_angular = regparam
 
@@ -87,7 +86,6 @@ def regularize_area_GP_new( x_area_lk, regparam ):
     l_dim = len( x_area_lk )
     cov = prior.get_cov( sigma, wn_rel_amp, lambda_angular, l_dim )
 
-#    print 'cov', cov
     inv_cov = np.linalg.inv( cov )
     det_cov = np.linalg.det( cov )
     if ( det_cov == 0. ):
@@ -95,9 +93,38 @@ def regularize_area_GP_new( x_area_lk, regparam ):
         print 'cov', cov
 
 #    print 'inv_cov', inv_cov
[…]

### 2016-11-14 prior.py

@@ -140,8 +140,8 @@ def get_cov( sigma, wn_rel_amp, lambda_angular, l_dim, periodic=True):
     else :
         dif_lon_ll = abs( dif_lon_ll )
 
-#    Sigma_ll = np.exp( - 0.5 * dif_lon_ll**2 / ( lambda_angular**2 ) )
-    Sigma_ll = np.exp( - dif_lon_ll / ( lambda_angular**2 ) )
+    Sigma_ll = np.exp( - 0.5 * dif_lon_ll**2 / ( lambda_angular**2 ) )
+#    Sigma_ll = np.exp( - dif_lon_ll / ( lambda_angular**2 ) )
 
     cov = Sigma_ll * ( 1 - wn_rel_amp )
     cov[np.diag_indices(l_dim)] += wn_rel_amp

### 2016-11-14 shrinkwrap.py

@@ -71,7 +71,7 @@ def func_to_minimize ( A_nm_flat, *args ) :
 
 
 #---------------------------------------------------
-def do_shrinkwrap ( U_in, n_PC, run_dir ) :
+def do_shrinkwrap ( U_in, n_PC, output=True, run_dir='' ) :
 
     # N ( = n_PC ): number of principle components
     # M ( = n_PC + 1 ) : number of vertices
@@ -91,7 +91,36 @@ def do_shrinkwrap ( U_in, n_PC, run_dir ) :
 
     diff = 1.
 
-    with open ( run_dir+'shrinkwrap_log', 'w' ) as f :
+    if output :
+
+        with open ( run_dir+'shrinkwrap_log', 'w' ) as f :
+
+            while ( diff > DIFF_LIM ) : 
+                
+                alpha = alpha / 10.
+                f.write( '# ------------------------------------\n' )
+                f.write( '# best fit with alpha='+str(alpha)+'\n' )
+                params = ( UU_qi , n_PC, alpha )
+                A_nm_bestfit_flat = minimize( func_to_minimize, A_nm_ini_flat, args=params, method='L-BFGS-B' )['x']
+                A_nm_bestfit      = A_nm_bestfit_flat.reshape( [ n_PC , n_PC+1 ] )
+
+                for mm in xrange( len( A_nm_bestfit.T ) ):
+                    for nn in xrange( len( A_nm_bestfit ) ):
+                        f.write( str( A_nm_bestfit[nn][mm] )+'\t' ) 
+                    f.write( '\n' )
+                for nn in xrange( len( A_nm_bestfit ) ):
+                    f.write( str( A_nm_bestfit[nn][0] )+'\t' ) 
+                f.write( '\n' )
+                vol  = get_volume ( A_nm_bestfit, n_PC )
+                diff = ( vol_old - vol ) / vol_old # fractional volume change
+                f.write( '# vol_old, vol, diff\t' + str(vol_old) + '\t' + str(vol) + '\t' + str(diff) + '\n\n\n' )
+                vol_old = vol
+                A_nm_ini_flat = A_nm_bestfit_flat
+            f.write( '#------------------------------------\n' )
+
+        np.savetxt( run_dir+'shrinkwrap_final', A_nm_bestfit.T )
+
+    else :
 
[…]

### 2016-11-21 paper/main.tex
adding missed figures
edits in a code to compute mock lightcurves

@@
 
+\subsubsection{Fitting with $\fast$}
+
 %%%
@@
 \begin{eqnarray}
-- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; f) \\
-\mathcal{F}(\lambda, \Delta_t; f)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
+- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; \fast) \\
+\mathcal{\tilde F}(\lambda, \Delta_t; \fast)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
 \end{eqnarray}
@@
 %%%
-In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast } (\Delta_t; f) = \lambda ^2 \mathcal{F}$.
+In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast } (\Delta_t; \fast) = \lambda ^2 \mathcal{\tilde F}$.
+
+\subsubsection{Concerns}
+
+%%%
+\begin{itemize}
+\item $\fast_{lk}$'s or $f_{lk}$'s are not mutually independent. (Sum is unity.) 
+\item Same regularization 
+\end{itemize}
+%%%
 
@@
     \end{minipage}    
-    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$.The difference between the three panels is just the seed for \url{np.randam.uniform}}
 \label{fig:regterm}
@@
     \end{minipage}
-    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$.
+The difference between the three panels is just the seed for \url{np.randam.uniform}}
 \label{fig:regterm}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_albd_jk_best.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_area_ik_best.pdf}
     \end{center}
     \end{minipage}
-    \caption{Solution with smallest regularization term. }
+    \caption{Solution with smallest regularization term when $\Delta_t=1.75$ ($\Delta \phi = 90^{\circ }$).}
 \label{fig:regterm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[b]
+%    \begin{minipage}{0.5\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
+%    \end{center}
+%    \end{minipage}
+%    \begin{minipage}{0.5\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
+%    \end{center}
+%    \end{minipage}
+%    \caption{Solution with smallest regularization term. }
+%\label{fig:regterm}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+
+\subsubsection{Fitting with $f$}
+
+What if $f$ is used instead of $\fast$ in fitting?
+
+From equation (\ref{eq:d_f_s}), the solution for $f_{lk} s_{kj}$ that is found through the least-square method is
+%%%
+\begin{equation}
+\sum_i (W^{+})_{li} d_{ij} = \sum_k f_{lk} s_{kj}
+\end{equation}
+%%%
+So, with an analogy to equation (\ref{eq:d_f_ast_s}), we could make similar plots of the principal components plane (with the principal components found from $\sum_i (W^{+})_{li} d_{ij}$ instead of $d_{ij}$).
+
+Then, the regularization term would be $\mathcal{F}^{\ast } (\Delta_{\phi }; f) = \lambda ^2 \mathcal{F}$ will be used where
+%%%
+\begin{equation}
+\mathcal{F}(\lambda, \Delta_{\phi }; f)\equiv  \sum _k \sum_{i,\,i'} (f^{T})_{ki} \Sigma_{ii'} ^{-1} f_{i'k}. 
+\end{equation}
+%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[h]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast }$ with $\Delta_t\sim 1.25$.
+The difference between the three panels is just the seed for \url{np.randam.uniform}.}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[h]
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_albd_jk_best.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_area_ik_best.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{Solution with smallest regularization term when $\Delta \phi = 90^{\circ }$. }
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{document}
 

### 2016-11-21 fitlc_params.py

@@ -29,8 +29,8 @@ deg2rad = np.pi/180.
 N_SIDE   = 32
 # INFILE = '/Users/yuka/Dropbox/Project/11_RotationalUnmixing/mockdata_quadrature_lc'
 # INFILE = 'data/raddata_1_norm'
-INFILE = 'mockdata/simpleIGBP_quadrature_lc'
-# INFILE = 'mockdata_90deg_13time_lcscat'
+# INFILE = 'mockdata/simpleIGBP_quadrature_lc'
+INFILE = 'mockdata_90deg_13time_lcscat'
 # INFILE = 'mockdata_90deg_lc'
 
 KNOWN_ANSWER=False

### 2016-11-21 main_IGBP_time.py

@@ -20,7 +20,7 @@ target_indx_list = [[ 17 ], # ocean
 # MODE = 'March'
 # MODE = 'June'
 MODE= 'specify'
-TAG='45deg'
+TAG='90deg_time9'
 # vegetation
 # target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
  #target_indx = [1, 2, 3, 4, 5, 6, 10, 14]
@@ -29,7 +29,7 @@ TAG='45deg'
 #target_indx = [7,8,9,11,12,13,16]
 
 # ocean
-target_indx = [17]
+# target_indx = [17]
 
 # all
 # target_indx = range(1,18)
@@ -37,9 +37,7 @@ target_indx = [17]
 
 cldoptd_crit = 5.
 
-TIME_END = 24.0
-TSTEP = 1.0
-Pspin = 24.0
+Pspin = 1.0
 OMEGA = ( 2. * np.pi / Pspin )
 
 # HealPix
@@ -65,6 +63,7 @@ if ( MODE == 'March' ):
     LON_O = 205.423 # sub-observer longitude
     INFILE = "data/raddata_1_norm"
     Time_i = np.arange(25)*1.
+    Time_i = np.arange(25)/24.
     cldfile_frac = "data/cldfrac_EPOXI_March_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_March_6.dat"
 elif ( MODE == 'June' ):
@@ -82,10 +81,10 @@ elif ( MODE == 'June' ):
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
     INFILE = "data/raddata_2_norm"
-    Time_i = np.arange(25)*1.
+    Time_i = np.arange(25)*24.
 
 elif ( MODE == 'specify' ):
-    LON_S = 45.
+    LON_S = 90.
     LAT_S = 0.
     LON_O = 0.
     LAT_O = 0.
@@ -95,7 +94,7 @@ elif ( MODE == 'specify' ):
 #    LAT_S = 21.6159766
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
-    Time_i = np.arange(7)*1./7.*24.
+    Time_i = np.arange(9)/9.
 else:
     print 'ERROR: Invalid MODE'
     sys.exit()
[…]

### 2016-11-21 main_plot_PCplane2D_terms.py

@@ -27,7 +27,7 @@ SEED_in  = 2013
 
 SIGMA_Y = 100.
 WL_AMP  = 0.
-LAMBDA_CORR_DEG = 120
+LAMBDA_CORR_DEG = 90
 LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
 
 # RESOLUTION=1000

### 2016-11-21 main_IGBP_time.py
further edit

@@ -20,7 +20,7 @@ target_indx_list = [[ 17 ], # ocean
 # MODE = 'March'
 # MODE = 'June'
 MODE= 'specify'
-TAG='90deg_time9'
+TAG='90deg_time19'
 # vegetation
 # target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
  #target_indx = [1, 2, 3, 4, 5, 6, 10, 14]
@@ -62,7 +62,7 @@ if ( MODE == 'March' ):
     LAT_O = 1.678  # sub-observer latitude
     LON_O = 205.423 # sub-observer longitude
     INFILE = "data/raddata_1_norm"
-    Time_i = np.arange(25)*1.
+#    Time_i = np.arange(25)*1.
     Time_i = np.arange(25)/24.
     cldfile_frac = "data/cldfrac_EPOXI_March_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_March_6.dat"
@@ -81,7 +81,7 @@ elif ( MODE == 'June' ):
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
     INFILE = "data/raddata_2_norm"
-    Time_i = np.arange(25)*24.
+    Time_i = np.arange(25)/24.
 
 elif ( MODE == 'specify' ):
     LON_S = 90.
@@ -94,7 +94,7 @@ elif ( MODE == 'specify' ):
 #    LAT_S = 21.6159766
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
-    Time_i = np.arange(9)/9.
+    Time_i = np.arange(19)/19.
 else:
     print 'ERROR: Invalid MODE'
     sys.exit()
@@ -229,5 +229,5 @@ for ii in xrange( len(Time_i) ) :
 #    print 'contribution_factor', contribution_factor
 sp = np.dot( contribution_factor, band_sp )
 
-np.savetxt( 'mockdata.'+TAG+'_factor', contribution_factor )
-np.savetxt( 'mockdata.'+TAG+'_lc', sp )
+np.savetxt( 'mockdata_'+TAG+'_factor', contribution_factor )
+np.savetxt( 'mockdata_'+TAG+'_lc', sp )

### 2016-11-21 main_plot_PCplane2D_terms_fitmap.py
a code to plot triangles in the principal component plane

@@ -1,0 +1,411 @@
+import numpy as np
+import sys
+import corner
+import datetime
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from matplotlib.colors import LinearSegmentedColormap
+
+from PCplane2D_params import NOISELEVEL, \
+    deg2rad, N_SIDE, INFILE_DIR, INFILE, OUTFILE_DIR, \
+    ALBDFILE, AREAFILE, SLICE_TYPE, N_SLICE_LONGITUDE, GEOM
+
+import prior
+import reparameterize
+
+import PCA
+import shrinkwrap
+
+import geometry
+
+LOOP_MAX  = 10000
+COUNT_MAX = 100
+SEED_in  = 2019
+
+SIGMA_Y = 100.
+WL_AMP  = 0.
+LAMBDA_CORR_DEG = 90
+LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
+
+# RESOLUTION=1000
+RESOLUTION=100
+
+# March 2008
+#LAT_S = -0.5857506  # sub-solar latitude
+#LON_S = 267.6066184  # sub-solar longitude
+#LAT_O = 1.6808370  # sub-observer longitude
+#LON_O = 210.1242232 # sub-observer longitude
+
+
+
+#===================================================
+# basic functions
+#=============================================== ====
+
+np.random.seed(SEED_in)
+
+#---------------------------------------------------
+def regularize_area_GP( x_area_lk, regparam ):
+
+    sigma, wn_rel_amp_seed, lambda_angular = regparam
+
+    wn_rel_amp = np.exp( wn_rel_amp_seed ) / ( 1. + np.exp( wn_rel_amp_seed ) )
+#    print 'wn_rel_amp', wn_rel_amp
+#    print 'lambda_angular', lambda_angular
+    l_dim = len( x_area_lk )
+    cov = prior.get_cov( sigma, wn_rel_amp, lambda_angular, l_dim )
+
+    inv_cov = np.linalg.inv( cov )
+    det_cov = np.linalg.det( cov )
+    if ( det_cov == 0. ):
+        print 'det_cov', det_cov
+        print 'cov', cov
+
+#    print 'inv_cov', inv_cov
+    x_area_ave = 1./len(x_area_lk.T)
[…]

### 2016-11-21 tmp.py

@@ -1,112 +1,0 @@
-
-#===================================================
-if __name__ == "__main__":
-
-    # print start time
-    now = datetime.datetime.now()
-    print now.strftime("%Y-%m-%d %H:%M:%S")
-
-    # Create directory for this run
-    startstr = now.strftime("%Y-%m-%d--%H-%M")
-    run_dir = "mcmc_output/" + startstr + "/"
-    os.mkdir(run_dir)
-    print "Created directory:", run_dir
-
-    # input data
-    Obs_ij = np.loadtxt(INFILE)
-    n_slice = len(Obs_ij)
-
-    n_band = len(Obs_ij[0])
-    Time_i = np.arange( n_slice )
-
-    Obsnoise_ij = ( NOISELEVEL * Obs_ij )
-
-    # set kernel
-#    Kernel_il = kernel(Time_i, n_slice)
-    Kernel_il = np.identity( n_slice )
-#    Sigma_ll = np.identity(n_slice)
-
-#    print 1/0
-#    set initial condition
-#    Y0_array = np.ones(N_TYPE*n_band+n_slice*(N_TYPE-1))
-    X0_albd_kj = 0.3+np.zeros([N_TYPE, n_band])
-    X0_area_lk = 0.1+np.zeros([n_slice, N_TYPE-1])
-
-## albedo ( band x surface type )
-#    X0_albd_kj = np.array( [[1.000000000000000056e-01, 9.000000000000000222e-01],
-#                            [2.999999999999999889e-01, 5.000000000000000000e-01],
-#                            [3.499999999999999778e-01, 5.999999999999999778e-01]]).T
-#
-#
-## area fraction ( longitude slice x suface type )
-#    X0_area_lk = np.array([[2.000000000000000111e-01, 8.000000000000000444e-01],
-#                           [5.500000000000000444e-01, 4.499999999999999556e-01],
-#                           [5.999999999999999778e-01, 4.000000000000000222e-01],
-#                           [9.000000000000000222e-01, 9.999999999999997780e-02]])
-
-#    X0_array = np.r_[ X0_albd_kj.flatten(), X0_area_lk.T[0].flatten() ]
-
[…]

### 2016-11-21 paper/main.tex
trying different regularization terms

@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2013.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2017.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2019.pdf}
     \end{center}
     \end{minipage}    
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$.The difference between the three panels is just the seed for \url{np.randam.uniform}}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 11 times in one rotation.
+\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}}
 \label{fig:regterm}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2013.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2017.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2019.pdf}
     \end{center}
     \end{minipage}
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$.
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$ \color{red} when the lightcurves are sampled 11 times in one rotation.
+\color{black}.
 The difference between the three panels is just the seed for \url{np.randam.uniform}}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 11 times in one rotation.
+\color{black} The difference between the three panels is just the seed for \url{np.randam.uniform}}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 15 times in one rotation.
+\color{black}.
+The difference between the three panels is just the seed for \url{np.randam.uniform}}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}    
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation.
+\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}.
+In the regularization term, not $f_{lk}$ but $(f_{lk}-f_{k}^{\rm (ave)})/f_{k}^{\rm (ave)}$ are used where $f_{k}^{\rm (ave)} = (\sum_l f_{lk})/L$.
+}
+\label{fig:regterm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[b]
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2013.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2017.pdf}
+    \end{center}
+    \end{minipage}
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2019.pdf}
+    \end{center}
+    \end{minipage}    
+    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation.
+\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}.
+In the regularization term, not $f_{lk}$ but $g_{lk}$ are used.
+}
 \label{fig:regterm}

### 2016-11-21 main_plot_PCplane2D_terms.py

@@ -6,12 +6,8 @@ import os
 
 import matplotlib.pyplot as plt
 import matplotlib.cm as cm
-from mpl_toolkits.axes_grid1 import make_axes_locatable
 from matplotlib.colors import LinearSegmentedColormap
-
-from PCplane2D_params import NOISELEVEL, \
-    deg2rad, N_SIDE, INFILE_DIR, INFILE, OUTFILE_DIR, \
-    ALBDFILE, AREAFILE, SLICE_TYPE, N_SLICE_LONGITUDE, GEOM
+from mpl_toolkits.axes_grid1 import make_axes_locatable
 
 import prior
 import reparameterize
@@ -23,23 +19,26 @@ import geometry
 
 LOOP_MAX  = 10000
 COUNT_MAX = 100
+# COUNT_MAX = 10
 SEED_in  = 2013
 
-SIGMA_Y = 100.
-WL_AMP  = 0.
 LAMBDA_CORR_DEG = 90
 LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
 
-# RESOLUTION=1000
 RESOLUTION=100
 
-# March 2008
-#LAT_S = -0.5857506  # sub-solar latitude
-#LON_S = 267.6066184  # sub-solar longitude
-#LAT_O = 1.6808370  # sub-observer longitude
-#LON_O = 210.1242232 # sub-observer longitude
+# GEOM = ( lat_o, lon_o, lat_s, lon_s, omega )
+GEOM = ( 0., 0., 0.,  90., 2.*np.pi )
 
+N_SIDE   = 32
+INFILE_DIR = 'mockdata/'
+INFILE = 'mockdata_90deg_time7_lc'
+OUTFILE_DIR = 'PCplane/'
 
+ALBDFILE = 'mockdata/simpleIGBP_quadrature_bandsp'
+AREAFILE = 'mockdata/simpleIGBP_quadrature_factor'
+
+deg2rad = np.pi/180.
 
 #===================================================
 # basic functions
@@ -47,44 +46,16 @@ RESOLUTION=100
 
 np.random.seed(SEED_in)
 
+
 #---------------------------------------------------
 def regularize_area_GP( x_area_lk, regparam ):
 
-    sigma, wn_rel_amp_seed, lambda_angular = regparam
-
-    wn_rel_amp = np.exp( wn_rel_amp_seed ) / ( 1. + np.exp( wn_rel_amp_seed ) )
[…]

### 2016-11-21 prior.py

@@ -136,9 +136,36 @@ def get_cov( sigma, wn_rel_amp, lambda_angular, l_dim, periodic=True):
     lon_l = 2.0 * np.pi * np.arange( l_dim ) / ( l_dim * 1. )
     dif_lon_ll = lon_l[:,np.newaxis] - lon_l[np.newaxis,:]
     if periodic :
+        dif_lon_ll = np.minimum( abs( dif_lon_ll ), 2. * np.pi - abs( dif_lon_ll ) )
+    else :
+        dif_lon_ll = abs( dif_lon_ll )
+
+    Sigma_ll = np.exp( - 0.5 * dif_lon_ll**2 / ( lambda_angular**2 ) )
+#    Sigma_ll = np.exp( - dif_lon_ll / ( lambda_angular**2 ) )
+
+    cov = Sigma_ll * ( 1 - wn_rel_amp )
+    cov[np.diag_indices(l_dim)] += wn_rel_amp
+    cov /= (1.0 +  wn_rel_amp)
+    cov = cov * sigma
+
+    return cov
+
+
+#---------------------------------------------------
+def get_cov_old( sigma, wn_rel_amp, lambda_angular, l_dim, periodic=True):
+
+#    kappa0 = np.log(output["x"][-1]) - np.log(360.0 - output["x"][-1])
+    Sigma_ll = np.zeros([l_dim, l_dim])
+    lon_l = 2.0 * np.pi * np.arange( l_dim ) / ( l_dim * 1. )
+    print 'lon_l', lon_l
+    dif_lon_ll = lon_l[:,np.newaxis] - lon_l[np.newaxis,:]
+    print 'dif_lon_ll', dif_lon_ll
+    if periodic :
+        print 'periodic'
         dif_lon_ll = np.minimum( abs( dif_lon_ll ), abs( 2. * np.pi - dif_lon_ll ) )
     else :
         dif_lon_ll = abs( dif_lon_ll )
+    print 'dif_lon_ll', dif_lon_ll
 
     Sigma_ll = np.exp( - 0.5 * dif_lon_ll**2 / ( lambda_angular**2 ) )
 #    Sigma_ll = np.exp( - dif_lon_ll / ( lambda_angular**2 ) )

### 2016-11-23 main_plot_PCplane2D_terms.py
gnuplot script

@@ -251,7 +251,7 @@ if __name__ == "__main__":
 
     # PCA
     print 'Performing PCA...'
-    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, output=False )
+    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, output=True )
     n_type = n_pc + 1
     if n_type != 3 :
         print 'ERROR: This code is only applicable for 3 surface types!'

### 2016-11-23 main_IGBP_time.py
adding more light curves

@@ -20,7 +20,7 @@ target_indx_list = [[ 17 ], # ocean
 # MODE = 'March'
 # MODE = 'June'
 MODE= 'specify'
-TAG='90deg_time19'
+TAG='90deg_time23'
 # vegetation
 # target_indx = [1, 2, 3, 4, 5, 6, 8, 9, 10, 12, 14]
  #target_indx = [1, 2, 3, 4, 5, 6, 10, 14]
@@ -94,7 +94,7 @@ elif ( MODE == 'specify' ):
 #    LAT_S = 21.6159766
     cldfile_frac = "data/cldfrac_EPOXI_June_6.dat"
     cldfile_optd = "data/clddpth_EPOXI_June_6.dat"
-    Time_i = np.arange(19)/19.
+    Time_i = np.arange(23)/23.
 else:
     print 'ERROR: Invalid MODE'
     sys.exit()

### 2017-02-08 samurai/samurai_class.py
minor comment

@@ -829,7 +829,8 @@ class Mapper(object):
             # Initialize ensemble sampler
             ensemble = emcee3.Ensemble(model, p0)
 
-            # Initialize sampler with Moves
+            # Initialize sampler with Moves: Linear combo of samplers -- essential
+            # for multi-modal posteriors
             sampler = emcee3.Sampler([
                 (emcee3.moves.DEMove(0.01), 0.5),
                 (emcee3.moves.DESnookerMove(), 0.1),

### 2017-02-08 fitlc_params.py
Updates for PCplane

@@ -4,11 +4,7 @@ import numpy as np
 # Parameters
 #--------------------------------------------------------------------
 
-<<<<<<< HEAD
-NUM_MCMC = 20000
-=======
 NUM_MCMC = 5000
->>>>>>> upstream/master
 NUM_MCMC_BURNIN = 0
 SEED_AMP = 0.1
 
@@ -41,28 +37,11 @@ KNOWN_ANSWER=False
 ALBDFILE = 'mockdata/simpleIGBP_quadrature_bandsp'
 AREAFILE = 'mockdata/simpleIGBP_quadrature_factor'
 #INFILE = "data/raddata_12_norm"
-<<<<<<< HEAD
-##INFILE = "data/raddata_2_norm"
-INFILE = "data/raddata_1_norm"
-#INFILE = "mockdata/mock_simple_1_data"
-#INFILE = "mockdata/mock_simple_3types_1_data"
-# INFILE = 'mockdata/mock_simple_1_scattered0.01_data_with_noise'
-#INFILE = 'mockdata/simpleIGBP_quadrature_lc'
-
-#WAVEBAND_CENTERS = np.array([550., 650., 750., 850.])
-#WAVEBAND_WIDTHS = np.array([100., 100., 100., 100.])
-WAVEBAND_CENTERS = np.array([350., 450., 550., 650., 750., 850., 950.])
-WAVEBAND_WIDTHS = np.array([100., 100., 100., 100., 100., 100., 100.])
-
-HDF5_COMPRESSION = 'lzf'
-=======
 #INFILE = "data/raddata_2_norm"
 #INFILE = "data/raddata_2_norm"
 #INFILE = "mockdata/mock_simple_1_data"
 #INFILE = "mockdata/mock_simple_3types_1_data"
 # INFILE = 'mockdata/mock_simple_1_scattered0.01_data_with_noise'
->>>>>>> upstream/master
 
 def calculate_walkers(n_dim):
     return 2*n_dim**2
- 

### 2017-02-08 PCA.py
bring PCA back

@@ -27,10 +27,10 @@ def do_PCA ( Dij, E_cutoff=5e-2, output=True, run_dir='' ):
     print "   # of PCs: ", N_PCs
 
     if output :
-        np.savetxt( run_dir+'PCA_V_jn', V.T, header='Principal Components ( dimension: band x index )' ) 
-        np.savetxt( run_dir+'PCA_E_n', E, header='Contribution factor ( dimension: index )' ) 
-        np.savetxt( run_dir+'PCA_U_in', U, header='Conefficient ( dimension: time x index )' ) 
-        np.savetxt( run_dir+'AVE_j', M, header='Time Average ( dimension: band )' ) 
+        np.savetxt( run_dir+'PCA_V_jn', V.T, header='Principal Components ( dimension: band x index )' )
+        np.savetxt( run_dir+'PCA_E_n', E, header='Contribution factor ( dimension: index )' )
+        np.savetxt( run_dir+'PCA_U_in', U, header='Conefficient ( dimension: time x index )' )
+        np.savetxt( run_dir+'AVE_j', M, header='Time Average ( dimension: band )' )
         # projection of 'answer' onto PC plane
         albd_kj  = np.loadtxt( ALBDFILE ).T
         dalbd_kj = albd_kj - M
@@ -39,4 +39,3 @@ def do_PCA ( Dij, E_cutoff=5e-2, output=True, run_dir='' ):
         np.savetxt( run_dir+'PCA_answer_projected', coeff_kn )
 
     return N_PCs, V[:N_PCs][:], U[:,:N_PCs], M
-

### 2017-02-08 main_plot_PCplane2D_terms_fitlc.py

@@ -157,7 +157,7 @@ if __name__ == "__main__":
 
     # PCA
     print 'Performing PCA...'
-    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, output=True )
+    n_pc, V_nj, U_in, M_j = PCA.do_PCA( Obs_ij, E_cutoff=1e-2, output=True, run_dir=OUTFILE_DIR )
     V_nj[0] = -1. * V_nj[0]
     U_in.T[0] = -1. * U_in.T[0]
     V_nj[1] = -1. * V_nj[1]
@@ -261,7 +261,7 @@ if __name__ == "__main__":
 
     #--------------------------------------------------------------------------
     # set up for a figure
-    fig = plt.figure(figsize=(3,3)) 
+    fig = plt.figure(figsize=(3,3))
     ax1 = plt.subplot(adjustable='box', aspect=1.0)
     ax1.set_xlim([-0.4,0.2])
     ax1.set_ylim([-0.2,0.4])
@@ -340,7 +340,7 @@ if __name__ == "__main__":
     # best
 
     points_kn_best = points_kn_array[ np.argmin( colorterm ) ][:-1,:]
-    
+
     print 'points_kn_best', points_kn_best
     # reconstruct albedo
     X_albd_kj_best = np.dot( points_kn_best, V_nj ) + M_j
@@ -350,5 +350,3 @@ if __name__ == "__main__":
 
     np.savetxt( OUTFILE_DIR+INFILE+'_l' + str(LAMBDA_CORR_DEG[0]) + 'deg_ratio_' + str(SEED_in) + '_X_albd_jk_best', X_albd_kj_best.T )
     np.savetxt( OUTFILE_DIR+INFILE+'_l' + str(LAMBDA_CORR_DEG[0]) + 'deg_ratio_' + str(SEED_in) + '_X_area_ik_best', X_area_ik_best )
-
-

### 2017-02-09 main_plot_PCplane2D_contour_gridsearch_noreg.py
plot of 2D plane with something like color contour

@@ -1,0 +1,302 @@
+import numpy as np
+import sys
+import corner
+import datetime
+import os
+
+import emcee
+
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from matplotlib.colors import LinearSegmentedColormap
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+
+from scipy.interpolate import griddata
+
+import prior
+import reparameterize
+
+import PCA
+import shrinkwrap
+
+import geometry
+
+
+import multiprocessing
+import functools
+
+
+LOOP_MAX  = 10000
+COUNT_MAX = 100
+
+SEED_in  = 2015
+
+deg2rad = np.pi/180.
+
+LAMBDA_CORR_DEG = 30.
+LAMBDA_CORR = LAMBDA_CORR_DEG * deg2rad
+
+
+
+# GEOM = ( lat_o, lon_o, lat_s, lon_s, omega )
+# GEOM = ( 0., 0., 0.,  90., 2.*np.pi )
+
+N_SIDE   = 32
+INFILE_DIR = 'mockdata/'
+# INFILE = 'mockdata_45deg_time23_l`xreplc'
+INFILE = 'mockdata_135deg_3types_redAmerica_t12_lc'
+OUTFILE_DIR = 'PCplane/'
+
+ALBDFILE = 'mockdata/mockdata_135deg_3types_redAmerica_t12_band_sp'
+AREAFILE = 'mockdata/mockdata_135deg_3types_redAmerica_t12_factor'
+
+VARAMP = 0.01
+
+N_TYPE = 3
+N_CPU  = 1
+N_MCMC = 100
+
+X_MIN = -0.2
+X_MAX = 0.4
+# X_NUM = 27
+X_NUM = 15
+Y_MIN = -0.2
+Y_MAX = 0.8
+Y_NUM = 25
+
+#===================================================
+# basic functions
+#=============================================== ====
+
+np.random.seed(SEED_in)
+
+
+#---------------------------------------------------
+def function( points_kn, params ):
+
+#    print 'working on ', indx
+    inv_cov, det_cov, M_j, U_iq = params
+
+    # construct area fraction
+    points_kq = np.c_[ points_kn, np.ones( len( points_kn ) ) ]
+    
+
+    # if the points do not form a triangle
+    if np.linalg.det( points_kq ) == 0. :
+        
+        term = 0.
+
+    else :
+
+        # construct albedo
+        X_albd_kj = np.dot( points_kn, V_nj ) + M_j
+
[…]

### 2017-02-09 main_plot_PCplane2D_contour_lc_EPOXI.py

@@ -1,0 +1,233 @@
+import numpy as np
+import sys
+import corner
+import datetime
+import os
+
+import emcee
+
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from matplotlib.colors import LinearSegmentedColormap
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+
+from scipy.interpolate import griddata
+
+import prior
+import reparameterize
+
+import PCA
+import shrinkwrap
+
+import geometry
+
+
+import multiprocessing
+import functools
+
+
+LOOP_MAX  = 10000
+COUNT_MAX = 100
+
+SEED_in  = 2015
+
+deg2rad = np.pi/180.
+
+LAMBDA_CORR_DEG = 30.
+LAMBDA_CORR = LAMBDA_CORR_DEG * deg2rad
+
+
+
+# GEOM = ( lat_o, lon_o, lat_s, lon_s, omega )
+# GEOM = ( 0., 0., 0.,  90., 2.*np.pi )
+
+N_SIDE   = 32
+
+
+INFILE_DIR = 'data/'
+INFILE = 'raddata_2_norm'
+OUTFILE_DIR = 'PCplane/'
+
+#INFILE_DIR = 'mockdata/'
+#INFILE = 'mockdata_135deg_3types_t12_lc'
+#OUTFILE_DIR = 'PCplane/'
+
+ALBDFILE = 'mockdata/mockdata_135deg_3types_t12_band_sp'
+AREAFILE = 'mockdata/mockdata_135deg_3types_t12_factor'
+
+VARAMP = 0.01
+
+N_TYPE = 3
+N_CPU  = 4
+N_MCMC = 100
+
+X_MIN = -1
+X_MAX = 1
+X_NUM = 30
+Y_MIN = -1
+Y_MAX = 1
+Y_NUM = 30
+
+#===================================================
+# basic functions
+#=============================================== ====
+
+np.random.seed(SEED_in)
+
+
+#---------------------------------------------------
+def function( points_kn, params ):
+
+#    print 'working on ', indx
+    inv_cov, det_cov, M_j, U_iq = params
+
+    # construct area fraction
+    points_kq = np.c_[ points_kn, np.ones( len( points_kn ) ) ]
+    
+
+    # if the points do not form a triangle
+    if np.linalg.det( points_kq ) == 0. :
+        
+        term = 0.
+
+    else :
+
+        # construct albedo
+        X_albd_kj = np.dot( points_kn, V_nj ) + M_j
+
[…]

### 2017-02-09 main_plot_PCplane2D_terms_fitmap.py

@@ -201,7 +201,6 @@ if __name__ == "__main__":
 
     # Load input data
     Obs_ij = np.loadtxt( INFILE_DIR + INFILE )
-    Obsnoise_ij = ( NOISELEVEL * Obs_ij )
     Time_i  = np.arange( len( Obs_ij ) ) / ( 1.0 * len( Obs_ij ) )
     n_band = len( Obs_ij.T )
 

### 2017-02-13 paper/main.tex
restructuring the manuscript...

@@
 \usepackage{epsfig}
-\usepackage{amsmath}
+%\usepackage{amsmath}
+\usepackage{amsmath,amsthm,amssymb,cases}
 \usepackage{rotating}
@@
 
-\keywords{planets and satellites: Jupiter --- Sun: evolution ---
-  planetary systems --- stars: evolution ---
-  stars: AGB and post-AGB --- radio continuum: planetary systems}
+\keywords{planets and satellites: surfaces --- planets and satellites: terrestrial planets}
 
@@
 
-\newpage
+%\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+    \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
+    \end{center}
+     \end{minipage}
+  \begin{minipage}{0.5\hsize}
+    \begin{center}
+    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
+    \end{center}
+\end{minipage}
+  \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
+    \end{center}
+ \end{minipage}
+   \begin{minipage}{0.5\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
+    \end{center}
+ \end{minipage}
+    \caption{Our mock data based on IGBP classification map of the Earth. }
+\label{fig:mockdata}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Framing the problem}
+\section{Preparing Mock Datasets}
+\label{s:mockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
+In order to facilitate the discussions about the procedures in the following sections, in this section we shall introduce a dataset to be used for demonstrations.
+
+We consider a simplified Earth map as shown in the upper left panel of Figure \ref{fig:mockdata}. 
+This map is based on the land classification by the International Geosphere-Biosphere Programme (IGBP)\footnote{\url{https://climatedataguide.ucar.edu/climate-data/ceres-igbp-land-classification}}. 
+Although the original classification assumes 16 land surface types plus ocean, in this paper we assume 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``soil'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.
+
+We consider an observation of diurnal light curves in 4 photometric bands. 
+The assumed albedo spectra of these surface types are shown in the upper right panel of Figure \ref{fig:mockdata}. 
+Here, the data for ocean are based on \citet{Mclinden1997}, 
+and the data for soil and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
+Specifically, we adopt  ``Brown to dark brown sand'' for ``soil'', and ``Grass'' for the ``vegetation''}. 
+These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise needed.
+The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering.
+
+The multi-band light curves are synthesized given the relative configuration of the star, planet, and the observer.  
+For the sake of simplicity in explaining the geometry, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $.
+However, the discussion in the following is generic and does not depend on these assumptions.
+
+The bottom panel of Figure \ref{fig:mockdata} displays the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
+Apparent albedo is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted.
+The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet.
+(We will discuss the effect of this assumptions later in Section ??.)
+
+The problem throughout this paper is, from this kind of multi-band diurnal light curves, how and how well we can retrieve the albedo spectra of different surface types as well as the longitudinal distribution of these surface types.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Inverse problem}
 \label{s:frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in Section \ref{s:mockdata}.
 
@@
 
-Assuming that the planetary surface is Lambertian scatterer everywhere, with a certain number $K$ of spectrally distinct surface types, 
-the disk-integrated scattered light can be written as a weighted summation of the reflectance spectra of different surface types.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[b]
+\caption{Indexes}
+\begin{center}
+\begin{tabular}{lcc} \hline \hline
+Name & Symbol & Maximum \\ \hline
+Observation Time & $i$ & I \\
+Band & $j$ & J  \\
+Surface Type & $k$ & K  \\
+Longitudinal Slice  & $l$ & L \\ \hline
+\end{tabular}
+\end{center}
+\label{tab:index}
+\end{table}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-For the moment, let us suppose that the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet (This will be relaxed in \S\ref{s:discussion}.)
-In this case, we can straightforwardly translate the observed planetary intensity to apparent albedo. 
-{\it Apparent albedo} is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted.
-
-The observed apparent albedo, $d_{ij}$ (``$d$'' for data), can be written using the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$, (both defined at each surface point) as follows \citep[see][]{Fujii2010}:
+On the assumption that the planetary surface is Lambertian scatterer everywhere, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types.
+Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
+the apparent albedo of the planet, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
 %%%
@@
 d_{i} (\lambda_j) &=& \displaystyle \frac{ \int_{{\rm IV}_i} s_{\vec \Omega }(\lambda_j) \cdot \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
-&=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
-&=& \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:d_f_ast_s}
+&=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \notag \\
+&=& \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:tilde_d_f_ast_s}
 \end{eqnarray}
@@
 %%%
-\begin{eqnarray}
-\begin{cases}
-\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
-\;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
-\end{cases}
-\end{eqnarray}
+\begin{subnumcases}
+{}
+0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:tilde_f_range} \\
+\sum_k \fast_{lk} = 1 & \mbox{for any $l$} \label{eq:tilde_f_sum} \\
+0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \label{eq:tilde_s_range} 
+\end{subnumcases}
 %%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[tbh]
-\caption{Indexes}
-\begin{center}
-\begin{tabular}{ccc} \hline \hline
-Name & Symbol & Maximum \\ \hline
-Observation Time & $i$ & I \\
-Band & $j$ & J  \\
-Surface Type & $k$ & K  \\
-Longitudinal Slice  & $l$ & L \\ \hline
-\end{tabular}
-\end{center}
-\label{tab:index}
-\end{table}%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%
+%\begin{eqnarray}
+%\begin{cases}
+%\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
+%\;\; 0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
+%\;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
+%\end{cases}
+%\end{eqnarray}
+%%%
+
+%\subsection{Estimating the Composition\\of Longitudinal Slices}
 
@@
 %%%
-with the following condition similar to equation (\ref{eq:cond_f_ast}):
+with the following condition similar to Equations (\ref{eq:tilde_s_range})-(\ref{eq:tilde_f_sum}):
 %%%
-\begin{eqnarray}
-\begin{cases}
-\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
-\;\; 0 \leq f_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f} \\
-\;\; \sum_k f_{lk} = 1 & \mbox{for any $l$} 
-\end{cases}
-\label{eq:constraints}
-\end{eqnarray}
+\begin{subnumcases}
+{}
+0 \leq f_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:f_range} \\
+\sum_k f_{lk} = 1 & \mbox{for any $l$} \label{eq:f_sum} \\
+0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \label{eq:s_range}
+\end{subnumcases}
 %%%
-Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of equation (\ref{eq:constraints})---this is where \citet{Cowan2013} stood.
+Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of Equations (\ref{eq:s_range})-(\ref{eq:f_sum})---this is where \citet{Cowan2013} stood.
 
-\citet{Cowan2013} proposed the specific procedure to find the solution for $\{f, s\}$. 
-Namely, 
-(1) perform PCA on the data to reduce the dimensionality as needed, 
-(2) perform simplex shrink-wrapping analysis to find the first guess for $s$, 
-and 
-(3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
-(The initial value for $f$ is fixed at 1/(\# of surface types).)
+%\citet{Cowan2013} proposed the specific procedure to find the solution for $\{f, s\}$. 
+%Namely, 
+%(1) perform PCA on the data to reduce the dimensionality as needed, 
+%(2) perform simplex shrink-wrapping analysis to find the first guess for $s$, 
+%and 
+%(3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
+%(The initial value for $f$ is fixed at 1/(\# of surface types).)
 
-\newpage
+%\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Degeneracy}
+\label{ss:degeneracy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.
+
+Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J-$th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$.
+\memoYF{How is it called in one word in mathematics?}\
+Conversely, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), and the associated matrix, $\fast _{ik}$, can always be found.
+Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the range where $\{ {\bf s}_k \}$ can exist, but in general this is not sufficient to result in a unique solution. 
+Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
+
+A formally equivalent degeneracy is found in Equation (\ref{eq:d_f_s}) coupled with the conditions (\ref{eq:f_range})-(\ref{eq:s_range}). 
+Essentially, the term $\sum _k f_{lk} s_{kj}$ represents the average albedo spectra of $l$-th slice and $W_{il}$ is the matrix that convolve them into the light curves. 
+But again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Constraining the Surface Types}
+\label{ss:constraining}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{ref}
+
+\end{document}
 
@@
 
+\bibliography{ref}
+
 \end{document}

### 2017-02-13 paper/main.tex
further updating...(but halfway)

@@
 
-In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in Section \ref{s:mockdata}.
+In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
+Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of the previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.
+We, however, choose to include these discussions as a baseline to establish the later arguments. 
+\memoYF{Too many overlaps??}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Principal Component (Hyper-)Plane\\and Graphical Conception}
+\label{ss:PCplane}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.
+
+Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$.
+\memoYF{How is it called in one word in mathematics?}\
+We show this graphically using the mock datasets shown in Section \ref{s:mockdata}.
+
+The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-th dimensional space is inconvenient for visualization. 
+We thus reduce the dimensionality using principal component analysis (PCA). 
+Unsurprisingly we extract two dominant principal components (PCs) through PCA (other components have vertually zero contribution), which are presented in Figure \ref{fig:PCs}.
+
+We subtract the 4-band light curves by the time averages of the respective bands, and its trajectory in the PC plane is shown in Figure \ref{fig:trajectory}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+\includegraphics[width=\hsize]{PCA_V_jn.pdf}
+    \end{center}
+    \caption{Principal components.}
+\label{fig:PCs}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
+    \end{center}
+    \caption{Trajectory on the principal component plane.}
+    \label{fig:trajectory}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
+    \end{center}
+    \caption{Trajectory on the principal component plane.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Degeneracy}
@@
 
-A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.
-
-Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J-$th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$.
-\memoYF{How is it called in one word in mathematics?}\
 Conversely, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), and the associated matrix, $\fast _{ik}$, can always be found.

### 2017-02-17 paper/main.tex
text and figure updated

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
-    \end{center}
-     \end{minipage}
-  \begin{minipage}{0.5\hsize}
-    \begin{center}
-    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
-    \end{center}
-\end{minipage}
-  \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
-    \end{center}
- \end{minipage}
-   \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
-    \end{center}
- \end{minipage}
-    \caption{Our mock data based on IGBP classification map of the Earth. }
+\begin{figure}[t]
+    \begin{center}
+	\includegraphics[width=\hsize]{mockdata_3types_map.pdf}
+    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
+	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc.pdf}
+    \end{center}
+    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green). }
 \label{fig:mockdata}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Principal Component (Hyper-)Plane\\and Graphical Conception}
+\subsection{Graphical Conception on PC (Hyper-)Plane\\and Formal Degeneracy}
 \label{ss:PCplane}
@@
 \memoYF{How is it called in one word in mathematics?}\
-We show this graphically using the mock datasets shown in Section \ref{s:mockdata}.
-
-The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-th dimensional space is inconvenient for visualization. 
+We show this graphically below, using the mock datasets shown in Section \ref{s:mockdata}.
+
+The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
 We thus reduce the dimensionality using principal component analysis (PCA). 
-Unsurprisingly we extract two dominant principal components (PCs) through PCA (other components have vertually zero contribution), which are presented in Figure \ref{fig:PCs}.
-
-We subtract the 4-band light curves by the time averages of the respective bands, and its trajectory in the PC plane is shown in Figure \ref{fig:trajectory}.
+As mentioned in \citet{Cowan2011}, the number of the spectrally distinct surface types is number of PCs plus 1 in theory. 
+Reasonably, we extract two dominant principal components (PCs) through PCA (other components have virtually zero contribution) from the mock light curves. 
+The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
+Note that, although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition).
+Thus, in the following, we adopt these two PCs as the axes of the PC plane.
+
+Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle. 
+The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases when larger surface area are averaged. 
+The points in the figure indicate the input albedo spectra of the three surface types. 
+Because the apparent albedo at any time of the observations is a linear combination of input surface colors (Equation \ref{eq:tilde_d_f_ast_s}) under the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), the trajectories should always be inside the triangle defined by these points.
 
@@
     \end{center}
-    \caption{Principal components.}
+    \caption{Principal components of the light curves shown in the bottom of Figure \ref{fig:mockdata}. }
 \label{fig:PCs}
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
-    \end{center}
-    \caption{Trajectory on the principal component plane.}
+\includegraphics[width=\hsize]{mockdata_3types_t360_lc_PCplane.pdf}
+    \end{center}
+    \caption{Lines: trajectory of the 4-band light curves projected on the PC plane, in the case of $\alpha = 135^{\circ }$ (thick indigo), $\alpha = 90^{\circ }$ (olive), and $\alpha = 45^{\circ }$ (gold).
+Points: The input albedo spectra of ocean (blue), soil (red), and vegetation (green), projected on the PC plane.
+The surface albedo spectra cannot be located in the ray region, because it violates the condition (\ref{eq:tilde_s_range}).
+}
     \label{fig:trajectory}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
-    \end{center}
-    \caption{Trajectory on the principal component plane.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Degeneracy}
-\label{ss:degeneracy}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Conversely, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), and the associated matrix, $\fast _{ik}$, can always be found.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Degeneracy}
+%\label{ss:degeneracy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+When it comes to the point where we must estimate the points given the trajectory/-ies, however, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
+The associated matrix, $\fast _{ik}$, can always be found. 
 Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the range where $\{ {\bf s}_k \}$ can exist, but in general this is not sufficient to result in a unique solution. 
@@
 \label{ss:constraining}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Given that any combinations that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
+% Thus, we need to be careful about the implicit assumptions that are made  
+With no assumptions or information on the spectral albedo of the surface types, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
+While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
+This is because of the relative configuration of the trajectory and the permitted region. 
+For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the left bottom corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
+
+In order to see this more quantitatively, we made a grid on the PC plane  with an interval of ?? (shown in Figure \ref{fig:gridsearch}) and considered all combinations of three grid points. 
+Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and find the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
+%
+As expected, we find a relatively definite peak near the point of ocean. 
+On the other hand, the peak that corresponds to soil is blurred.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Constraining the Surface Types}
+%\label{ss:constraining}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-21 paper/main.tex
figure added

@@
 
-In order to see this more quantitatively, we made a grid on the PC plane  with an interval of ?? (shown in Figure \ref{fig:gridsearch}) and considered all combinations of three grid points. 
-Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and find the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
+In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
+Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
 %
 As expected, we find a relatively definite peak near the point of ocean. 
-On the other hand, the peak that corresponds to soil is blurred.
+On the other hand, the peak that corresponds to soil is a blur.
 

### 2017-02-21 paper/main.tex
figure added
mock lightcurves are added

@@
     \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
-	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc.pdf}
+	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
     \end{center}
@@
 As expected, we find a relatively definite peak near the point of ocean. 
-On the other hand, the peak that corresponds to soil is a blur.
+On the other hand, the peak that corresponds to soil is a blur, and it is almost not constrained.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg.pdf}
+    \end{center}
+    \caption{correlation length $30^{\circ }$. }
+\label{fig:noreg}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Additional Constraints}
+\label{ss:regularization}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-02-21 paper/main.tex
minor text edits

@@
 
-We consider a simplified Earth map as shown in the upper left panel of Figure \ref{fig:mockdata}. 
+We consider diurnal light curves of a toy model of the Earth, in 4 photometric bands. 
+We use a simplified surface map as shown in the upper left panel of Figure \ref{fig:mockdata}. 
 This map is based on the land classification by the International Geosphere-Biosphere Programme (IGBP)\footnote{\url{https://climatedataguide.ucar.edu/climate-data/ceres-igbp-land-classification}}. 
@@
 
-We consider an observation of diurnal light curves in 4 photometric bands. 
-The assumed albedo spectra of these surface types are shown in the upper right panel of Figure \ref{fig:mockdata}. 
-Here, the data for ocean are based on \citet{Mclinden1997}, 
+The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
+These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise needed.
+The albedo spectra for ocean are based on \citet{Mclinden1997}, 
 and the data for soil and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
 Specifically, we adopt  ``Brown to dark brown sand'' for ``soil'', and ``Grass'' for the ``vegetation''}. 
-These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise needed.
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering.
 
-The multi-band light curves are synthesized given the relative configuration of the star, planet, and the observer.  
+The light curves are synthesized given the relative configuration of the star, planet, and the observer.  
 For the sake of simplicity in explaining the geometry, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $.
@@
 
-The bottom panel of Figure \ref{fig:mockdata} displays the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
+The bottom panels of Figure \ref{fig:mockdata} displays the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
 Apparent albedo is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted.
@@
 We thus reduce the dimensionality using principal component analysis (PCA). 
-As mentioned in \citet{Cowan2011}, the number of the spectrally distinct surface types is number of PCs plus 1 in theory. 
-Reasonably, we extract two dominant principal components (PCs) through PCA (other components have virtually zero contribution) from the mock light curves. 
+As mentioned in \citet{Cowan2011}, the number of the spectrally distinct major surface types is number of dominant PCs plus 1 in theory. 
+Reasonably, we extract two dominant principal components (PCs) through PCA (other components have virtually zero contribution) from the mock light curves prepared in Section \ref{s:mockdata}. 
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
-Note that, although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition).
+Although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition).
 Thus, in the following, we adopt these two PCs as the axes of the PC plane.
 
-Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle. 
-The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases when larger surface area are averaged. 
+Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
+The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area are averaged. 
 The points in the figure indicate the input albedo spectra of the three surface types. 
@@
     \caption{Lines: trajectory of the 4-band light curves projected on the PC plane, in the case of $\alpha = 135^{\circ }$ (thick indigo), $\alpha = 90^{\circ }$ (olive), and $\alpha = 45^{\circ }$ (gold).
-Points: The input albedo spectra of ocean (blue), soil (red), and vegetation (green), projected on the PC plane.
+Points: The input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle), projected on the PC plane.
 The surface albedo spectra cannot be located in the ray region, because it violates the condition (\ref{eq:tilde_s_range}).
@@
 
-When it comes to the point where we must estimate the points given the trajectory/-ies, however, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
-The associated matrix, $\fast _{ik}$, can always be found. 
-Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the range where $\{ {\bf s}_k \}$ can exist, but in general this is not sufficient to result in a unique solution. 
+On the other hand, when it comes to the point where we must estimate the points given the trajectory/-ies, however, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
+Note that the associated matrix, $\fast _{ik}$, can always be found. 
+Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the region where $\{ {\bf s}_k \}$ can exist. 
+However, in general this is not sufficient to result in a unique solution. 
 Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
@@
 In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
-Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
+Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha =90^{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
 %

### 2017-02-22 paper/main.tex
adding a draft of regularization term
missing figures are added

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[bth!]
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+    \end{center}
+    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?). }
+\label{fig:noreg}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
+    \end{center}
+    \caption{Upper panel: on the assumption of gaussian process with correlation length $30^{\circ }$. Lower panel: correlation length $40^{\circ }$. }
+\label{fig:noreg}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Given that any combinations that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Additional Constraints}
+\label{ss:regularization}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Constraining the Surface Types}
+%\label{ss:constraining}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Prior: Gaussian Processes}
+%\label{ss:gp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{This is just a quick draft and will need to be updated significantly.}
+
+A more constraining condition we might impose is the correlation length of the light curves.
+
+%%%
+\begin{eqnarray}
+&&Posterior 
+\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
+&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
+\end{eqnarray}
+%%%
+where $\mathcal{P} (X) $ is a prior for $X$.
+
+The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
+We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
+Such assumption can be represented by the prior of 
+%%%
+\begin{equation}
+\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
+\end{equation}
+%%%
+or
+%%%
+\begin{equation}
+\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
+\end{equation}
+%%%
+where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
+In this paper, we assume squared exponential covariance function, i.e., 
+%%%
+\begin{equation}
+\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
+\end{equation}
+%%%
+where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
+%%%
+\begin{equation}
+\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
+\end{equation}
+%%%
+where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg.pdf}
-    \end{center}
-    \caption{correlation length $30^{\circ }$. }
+%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
+\includegraphics[width=\hsize]{IGBP_lon_reg_l30deg.pdf}
+    \end{center}
+    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without (upper) and with (lower) regularization term.
+The regularization term for the lower panel assumes correlation length $30^{\circ }$.
+}
 \label{fig:noreg}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Additional Constraints}
-\label{ss:regularization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Constraining the Surface Types}
-%\label{ss:constraining}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-02-22 main_plot_PCplane2D_contour_gridsearch_reg.py
codes with better allowed region

@@ -34,6 +34,7 @@ SEED_in  = 2015
 
 deg2rad = np.pi/180.
 
+# LAMBDA_CORR_DEG = 40.
 LAMBDA_CORR_DEG = 30.
 LAMBDA_CORR = LAMBDA_CORR_DEG * deg2rad
 
@@ -44,7 +45,7 @@ LAMBDA_CORR = LAMBDA_CORR_DEG * deg2rad
 
 N_SIDE   = 32
 INFILE_DIR = 'mockdata/'
-# INFILE = 'mockdata_45deg_time23_l`xreplc'
+# INFILE = 'mockdata_135deg_3types_t12_lc'
 INFILE = 'mockdata_90deg_3types_t12_lc'
 OUTFILE_DIR = 'PCplane/'
 
@@ -99,8 +100,15 @@ def function( points_kn, params ):
             term = 0.
             
         else :
+
+            x_area_ave = np.average( x_area_ik, axis=0 )        
+            x_area_std = np.std( x_area_ik, axis=0 )
+            dx_area_ik = ( x_area_ik - x_area_ave )/x_area_std
+            term1 = -0.5 * np.sum( np.diag( np.dot( np.dot( dx_area_ik.T, inv_cov ), dx_area_ik ) ) )
+            term2 = -0.5 * np.log( det_cov )
+            term  = np.exp( term1 + term2 )
             
-            term = 1.
+#            term = 1.
 
     return term
 
@@ -159,6 +167,9 @@ def call_multicore( list_index, args ):
 if __name__ == "__main__":
 
 
+
+
+
     # Load input data
     Obs_ij = np.loadtxt( INFILE_DIR + INFILE )
     Time_i  = np.arange( len( Obs_ij ) ) / ( 1.0 * len( Obs_ij ) )
@@ -172,13 +183,14 @@ if __name__ == "__main__":
         print 'ERROR: This code is only applicable for 3 surface types!'
         sys.exit()
 
+
     # flipping
     V_nj[0] = -1. * V_nj[0]
     U_in.T[0] = -1. * U_in.T[0]
 #    V_nj[1] = -1. * V_nj[1]
 #    U_in.T[1] = -1. * U_in.T[1]
 
-    # longitudinal slices
+
     #--------------------------------------------------------------------------
     # longitudinal colors
     albd_answer_kj  = np.loadtxt( ALBDFILE ).T
@@ -186,9 +198,11 @@ if __name__ == "__main__":
     type_lk        = type_kl.T
[…]

### 2017-02-22 main_plot_PCplane2D_terms_fitlc_JLY.py
Earth Model compare

@@ -1,0 +1,360 @@
+import numpy as np
+import sys
+import corner
+import datetime
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from matplotlib.colors import LinearSegmentedColormap
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+import prior
+import reparameterize
+
+import PCA
+
+LOOP_MAX  = 10000
+COUNT_MAX = 100
+
+SEED_in  = 2015
+
+LAMBDA_CORR_DEG = np.array( [ 30., 30., 30. ] )
+LIST_LAMBDA_CORR = LAMBDA_CORR_DEG * ( np.pi/180. )
+
+RESOLUTION=100
+XMIN = -1.0
+XMAX = 2.0
+YMIN = -1.0
+YMAX = 1.0
+
+N_SIDE   = 32
+INFILE_DIR = 'mockdata/'
+# INFILE = 'mockdata_45deg_time23_l`xreplc'
+INFILE = 'lc_test2.txt'
+OUTFILE_DIR = 'PCplane/'
+
+#ALBDFILE = 'mockdata/mockdata_135deg_3types_redAmerica_t12_band_sp'
+#AREAFILE = 'mockdata/mockdata_135deg_3types_redAmerica_t12_factor'
+
+deg2rad = np.pi/180.
+
+#===================================================
+# basic functions
+#=============================================== ====
+
+np.random.seed(SEED_in)
+
+#---------------------------------------------------
+def regularize_area_GP_order( x_area_lk, points_kn, type='squared-exponential', ans=False ):
+
+    sum_term  = 0.
+    sum_term1 = 0.
+    sum_term2 = 0.
+
+    x_area_ave = np.average( x_area_lk, axis=0 )
+
+    x_area_std = np.std( x_area_lk, axis=0 )
+    dx_area_lk = ( x_area_lk - x_area_ave )/x_area_std
+
+    list_arg = np.argsort( x_area_ave )
+
+    print 'x_area_ave', x_area_ave
+    print 'x_area_std', x_area_std
+
+    for kk in xrange( len( points_kn ) ):
+#    for kk in [list_arg[-1]] :
+
+        print 'kk', kk
+        print'point ', points_kn[kk]
+
+        if ans :
+            lambda_angular = LIST_LAMBDA_CORR[kk]
+        else :
+            if points_kn[kk][1] == np.max( points_kn.T[1] ) :
[…]
